### 2021-10-07 01_data/newsarticle/counting-countries2.Rmd
r codes for counting countries mentioned
Now we can do separate years! Oh even more convenient!

---
title: "Preprocessing: counting countries Xinhua 2000"
author: "Lucie Lu"
date: "10/6/2021"
output: html_document
---

```{r}
test <- read.csv("Xinhua_2000.csv")
#head(test)
library(tidyverse)
#https://hbctraining.github.io/Intro-to-R/lessons/08_intro_tidyverse.html
test <- test %>% 
  rownames_to_column() %>% 
  as_tibble()
```

```{r}
df <- test %>% 
  pull(	
country) %>% 
  str_split("[|]")

max(lengths(df))

names(df) <- test$rowname
#df_2 <- data.frame(matrix(unlist(df), nrow=max(lengths(df)), byrow=TRUE),stringsAsFactors=FALSE)

library (plyr)
df_2 <- ldply (df, data.frame)
df_2 <- tibble(df_2)
colnames(df_2)[2] <- "country_mentioned"

df_2$countries_mentioned <- as.factor(df_2$country_mentioned)
```

```{r}
library(dplyr)
df_2 %>% 
  group_by(country_mentioned) %>%
  dplyr::summarise(n = n()) %>%
  arrange(desc(n))

#duplicated name summarise in both packages
#https://statisticsglobe.com/r-error-must-only-be-used-inside-dplyr-verbs
```

### 2021-10-14 02_clean_and_merge/05_clean_newarticles_counts_frequencies.Rmd

---
title: "Preprocessing: counting countries Xinhua 2000-2014"
author: "Lucie Lu"
date: "10/6/2021"
output: html_document
---

```{r}

list.files("Xinhua_news_articles_2000-2014/")

Xinhua_2014 <- read.csv("Xinhua_news_articles_2000-2014/Xinhua_2014.csv")
#head(Xinhua_2000 )
library(tidyverse)
#https://hbctraining.github.io/Intro-to-R/lessons/08_intro_tidyverse.html
Xinhua_2014 <- Xinhua_2014 %>% 
  rownames_to_column() %>% 
  as_tibble()

#replace empty country with extracted locations
Xinhua_2014$country <- ifelse(Xinhua_2014$country==" ", Xinhua_2014$extracted_locations, Xinhua_2014$country)

```

```{r}
df <- Xinhua_2014  %>% 
  pull(country) %>% 
  str_split("[|]")

#max(lengths(df))

names(df) <- Xinhua_2014$rowname
#df_2 <- data.frame(matrix(unlist(df), nrow=max(lengths(df)), byrow=TRUE),stringsAsFactors=FALSE)

library (plyr)
df_2 <- ldply (df, data.frame)
df_2 <- tibble(df_2)
colnames(df_2)[2] <- "country_mentioned"

df_2$countries_mentioned <- as.factor(df_2$country_mentioned)
```

```{r}
library(dplyr)
new_df_2014 <- df_2 %>% 
  group_by(country_mentioned) %>%
  dplyr::summarise(n = n()) %>%
#  df_2[!(df_2$country_mentioned == "")]  %>%
#  mutate(freq = round(n/sum(n), 3)) %>%
  arrange(desc(n))

new_df_2014 <- new_df_2014 %>% mutate(year=2014)

#duplicated name summarise in both packages
#https://statisticsglobe.com/r-error-must-only-be-used-inside-dplyr-verbs
```

```{r}
# list all of the files here
new_df_2000
new_df_2001
new_df_2002
new_df_2003
new_df_2004
new_df_2005
new_df_2006
new_df_2007
new_df_2008 
new_df_2009
new_df_2010
new_df_2011
new_df_2012
new_df_2013
new_df_2014
```

```{r}
all_df <- rbind(new_df_2000,
new_df_2001,
new_df_2002,
new_df_2003,
new_df_2004,
new_df_2005,
new_df_2006,
new_df_2007,
new_df_2008,
new_df_2009,
new_df_2010,
new_df_2011,
new_df_2012,
new_df_2013,
new_df_2014)
str(all_df)
```

```{r}
#transform to wide data for better graphing
#https://cran.r-project.org/web/packages/data.table/vignettes/datatable-reshape.html
library(data.table)
data_all_df_long <- dcast(all_df, country_mentioned ~ year, value.var = "n")
head(data_all_df_long, 20)

```

```{r export data}

#write.csv(data_all_df_long, "Xinhua_2001_2014_countrycounts.csv")

```

```{r get frequency tables}

### try this one
all_df %>% 
  group_by(country_mentioned, year) %>%
#  dplyr::summarise(n2 = n()) %>%
  mutate(freq_perc = round(100 * n / sum(all_df[all_df$year==2000,]$n), digits=2))

#sum the values instead of counting
sum(all_df[all_df$year==2000,]$n)

###end of trying
#################
freq_perc_by_year <- matrix(NA, nrow=length(existing_years), ncol=1)

existing_years <- seq(2000, 2014, by=1)

for (i in 1:length(existing_years)){
  freq_perc_by_year[i] = sum(all_df[all_df$year==existing_years[i],]$n)
}

freq_perc_by_year <- cbind(freq_perc_by_year, existing_years)
colnames(freq_perc_by_year)[1] <- "total_n_by_year"
colnames(freq_perc_by_year)[2] <- "year"

```

```{r merge the two}

all_df2 <- dplyr::inner_join(all_df, data.frame(freq_perc_by_year), by='year')

all_df2 <- all_df2 %>% 
  group_by(country_mentioned, year) %>%
#  dplyr::summarise(n2 = n()) %>%
  mutate(freq_perc = round(100 * n / total_n_by_year, digits=2))

```

```{r frequency tables}
#transform to wide data for better graphing
#https://cran.r-project.org/web/packages/data.table/vignettes/datatable-reshape.html
library(data.table)
data_all_df2_long <- reshape2::dcast(all_df2, country_mentioned ~ year, value.var = c("freq_perc"))
head(data_all_df2_long, 20)

```

```{r export data frequency}

#write.csv(data_all_df2_long, "Xinhua_2001_2014_countryfrequencies.csv")

```

### 2021-10-14 02_clean_and_merge/03_clean_archer_data.R
cleaning

@@ -7,3 +7,32 @@
 
 rm(list = ls())
 library(tidyverse)
+
+
+# load data ---------------------------------------------------------------
+
+year <- as.list(2000:2014)
+dts <-
+  lapply(
+    year,
+    function(x) {
+      read_csv(
+        paste0(
+          str_remove(getwd(), "/git_version"),
+          "/Xinhua news articles_2000-2014/",
+          "Xinhua_", x, ".csv"
+        )
+      )
+    }
+  ) # useful for now to leave as a list
+
+
+
+# clean -------------------------------------------------------------------
+
+dts %>%
+  map(
+    ~ .x %>% pull(country) %>%
+      str_split("[|]") %>%
+      str_replace(".*,", "")
+  )

### 2021-12-13 03_analysis/01_primary_analysis.R
thinking about identification approaches

@@ -50,9 +50,9 @@ trans_dt <-
     asinh # use inverse hyperbolic sine rather than log(1 + x)
   ) %>%
   group_by(recipient_iso3) %>%
-  # mutate(
-  #   aid = lag(aid, by = "year")
-  # ) %>%
+  mutate(
+    count = lead(count, by = "year")
+  ) %>%
   ungroup %>%
   na.omit
 
@@ -77,7 +77,7 @@ pdata <- # for estimating random recipient effects with censReg
 # Predicting Coverage
 spec <- 
   count ~ aid + pmm_polity + gdp + pop + unemp + disaster + civilwar +
-  dist + trade + atopally + as.factor(year) | 
+  dist + trade + atopally + as.factor(year)
 
 
 ml_tobit <- function(eq, count = T) { # multilevel tobit with recipient random effects
@@ -153,9 +153,9 @@ trans_dt <-
     asinh # use inverse hyperbolic sine rather than log(1 + x)
   ) %>%
   group_by(recipient_iso3) %>%
-  # mutate(
-  #   aid = lead(aid, by = "year")
-  # ) %>%
+  mutate(
+    aid = lead(aid, by = "year")
+  ) %>%
   ungroup %>%
   na.omit
 spec <- 

### 2021-12-13 03_analysis/___checking_lewbel_iv_with_simulation.R

@@ -1,0 +1,126 @@
+###################################################################
+# A check of the Lewbel (2012) approach to instrumental variables
+###################################################################
+
+library(tidyverse)
+library(seerrr)
+
+
+# simulate some endogenous data -------------------------------------------
+
+simulate( # based on example at:
+          # https://www.rdocumentation.org/packages/ivlewbel/versions/1.1/topics/lewbel
+  R = 10000,
+  x1 = rnorm(N, 0, 1),
+  x2 = rnorm(N, 0, 1),
+  u = rnorm(N, 0, 1),
+  s1 = rnorm(N, 0, 1),
+  s2 =  rnorm(N, 0, 1),
+  ov = rnorm(N, 0, 1),
+  z1 = rnorm(N, 0 ,1),
+  e1 = u + exp(x1)*s1 + exp(x2)*s1,
+  e2 = u + exp(-x1)*s2 + exp(-x2)*s2,
+  y1 = 1 + x1 + x2 + ov + e2 + 2*z1,
+  y2 = 1 + x1 + x2 + y1 + 2*ov + e1,
+) -> sim.data
+
+
+# use lewbel estimator ----------------------------------------------------
+
+# recover the "instruments"
+sim.data %>%
+  lapply(
+    X = .,
+    FUN = function(x) {
+      fit <- lm(y1 ~ x1 + x2, data = x)
+      eps <- resid(fit)
+      z   <- with(x, cbind(x1, x2))
+      zbr <- apply(z, 2, function(x) (x - mean(x)) * eps^2)
+      colnames(zbr) <- paste0("z", 1 + 1:ncol(zbr))
+      zbr <- as_tibble(zbr)
+      bind_cols(x, zbr)
+    }
+  ) -> sim.data
+
+# Estimate models
+
+estimate( # the lewbel instruments
+  sim.data,
+  y2 ~ y1 + x1 + x2 | z2 + z3 + x1 + x2,
+  vars = "y1",
+  estimator = iv_robust,
+  se_type = "stata"
+) -> sim.est1
+
+estimate( # the exogenous instrument
+  sim.data,
+  y2 ~ y1 + x1 + x2 | z1 + x1 + x2,
+  vars = "y1",
+  estimator = iv_robust,
+  se_type = "stata"
+) -> sim.est2
+
+estimate( # no instrument
+  sim.data,
+  y2 ~ y1 + x1 + x2,
+  vars = "y1",
+  se_type = "stata"
[…]

### 2021-12-14 02_clean_and_merge/02_clean_recipient_covariates.R
imputed and nonimputed versions of the data

@@ -8,7 +8,7 @@
 rm(list = ls())       # tidy the workspace
 library(tidyverse)    # for grammar
 library(democracyData)# a bunch of democracy datasets
-
+library(countrycode)  # to standardize country codes
 
 # democracy data ----------------------------------------------------------
 
@@ -246,13 +246,13 @@ start_n - nrow(na.omit(cov_data)) # that's better, but not great
 
 # Use random forests to impute remaining missing data
 library(missRanger)
-cov_data <- cov_data %>%
+imp_cov_data <- cov_data %>%
   missRanger(pmm.k = 3) # combine imputations with predictive mean matching
 
 # for citation of missRanger, see: https://academic.oup.com/bioinformatics/article/28/1/112/219101
 
 # Fix imputed distance vals to be mean of predictions for a given recipient
-cov_data <- cov_data %>%
+imp_cov_data <- imp_cov_data %>%
   group_by(recipient_iso3) %>%
   mutate_at(
     c("dist", "distw", "distwces"),
@@ -260,9 +260,35 @@ cov_data <- cov_data %>%
   )
 
 
+# Add regional dummies ---------------------------------------------------
+
+cov_data <- 
+  cov_data %>%
+  mutate(
+    region = countrycode(
+      recipient_iso3,
+      origin = "iso3c",
+      destination = "region"
+    )
+  )
+imp_cov_data <- 
+  imp_cov_data %>%
+  mutate(
+    region = countrycode(
+      recipient_iso3,
+      origin = "iso3c",
+      destination = "region"
+    )
+  )
+
+
 # save the results --------------------------------------------------------
 
 write_csv(
+  imp_cov_data,
+  paste0(getwd(), "/01_data/covariate_data/clean_covariate_data_imputed.csv")
+)
+write_csv(
   cov_data,
-  paste0(getwd(), "/01_data/covariate_data/clean_covariate_data.csv")
+  paste0(getwd(), "/01_data/covariate_data/clean_covariate_data_nonimputed.csv")
 )

### 2021-12-14 02_clean_and_merge/04_merge_datasets.R

@@ -7,6 +7,7 @@
 
 rm(list = ls())
 library(tidyverse)
+library(countrycode)
 
 
 # load data ---------------------------------------------------------------
@@ -21,15 +22,27 @@ xin_data <-
   )
 cov_data <-
   read_csv(
-    paste0(getwd(), "/01_data/covariate_data/clean_covariate_data.csv")
+    paste0(getwd(), "/01_data/covariate_data/clean_covariate_data_nonimputed.csv")
   )
-
+imp_cov_data <-
+  read_csv(
+    paste0(getwd(), "/01_data/covariate_data/clean_covariate_data_imputed.csv")
+  )
 
 # merge -------------------------------------------------------------------
 
 # merge the datasets by year and recipient code:
 
 final_data <-
+  left_join(
+    aid_data, xin_data,
+    by = c("recipient_iso3", "year")
+  ) %>%
+  left_join(
+    cov_data, 
+    by = c("recipient_iso3", "year")
+  )
+imp_final_data <-
   left_join(
     aid_data, xin_data,
     by = c("recipient_iso3", "year")
@@ -51,12 +64,21 @@ final_data <- final_data %>%
     c("count", "freq"),
     ~ replace_na(.x, 0)
   )
-
+imp_final_data <- imp_final_data %>%
+  mutate_at(
+    c("count", "freq"),
+    ~ replace_na(.x, 0)
+  )
 
 # save the final dataset --------------------------------------------------
 
 write_csv(
   final_data,
   file = 
-    paste0(getwd(), "/01_data/final_data/final_data.csv")
+    paste0(getwd(), "/01_data/final_data/final_data_nonimputed.csv")
+)
+write_csv(
+  imp_final_data,
+  file = 
+    paste0(getwd(), "/01_data/final_data/final_data_imputed.csv")
 )

### 2021-12-15 03_analysis/02_results_summary.Rmd
some preliminary results

---
title: "Results"
#author: "Miles D. Williams"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

**Note**: Table 1 shows results with the imputed dataset. Table 2 shows results with the non-imputed dataset.

```{r, results='asis'}
load(
  paste0(getwd(), "/tab1.R")
)
reg.tab1 <- reg.tab
cat(reg.tab1)
```

```{r, results='asis'}
load(
  paste0(getwd(), "/tab2.R")
)
reg.tab2 <- reg.tab
cat(reg.tab2)
```

### 2021-12-15 02_clean_and_merge/04_merge_datasets.R

@@ -48,7 +48,7 @@ imp_final_data <-
     by = c("recipient_iso3", "year")
   ) %>%
   left_join(
-    cov_data, 
+    imp_cov_data, 
     by = c("recipient_iso3", "year")
   )
 

### 2021-12-15 03_analysis/00_run_the_analysis.R

@@ -1,0 +1,29 @@
+########################################
+# Run the script for the main analysis
+########################################
+
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+library(tidyverse)
+library(censReg)
+library(AER)
+library(texreg)
+library(estimatr)
+
+
+# run analysis ------------------------------------------------------------
+
+data_sets <- c(
+  "final_data_imputed.csv",
+  "final_data_nonimputed.csv"
+)
+for(i in 1:2) {
+  cat("\nRUNNING ANALYSIS WITH:", data_sets[i], "......\n")
+  data_set <- data_sets[i]
+  source(
+    paste0(getwd(), "/03_analysis/01_primary_analysis.R")
+  )
+  if(i == 2) cat("\n.....DONE!")
+}

### 2021-12-15 03_analysis/01_primary_analysis.R

@@ -2,38 +2,12 @@
 # Primary Data Analysis
 #########################
 
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls())
-library(tidyverse)
-library(censReg)
-library(AER)
-library(texreg)
-
-
 # data --------------------------------------------------------------------
 
 dt <- 
   read_csv(
-    paste0(getwd(), "/01_data/final_data/final_data.csv")
+    paste0(getwd(), "/01_data/final_data/", data_set)
   )
-
-
-# summary stats -----------------------------------------------------------
-
-summary(dt) # general summary
-
-# histogram of aid
-ggplot(dt) +
-  aes(asinh(aid)) +
-  geom_histogram() +
-  labs(
-    x = "ODA-like Contributions\n(inverse hyberbolic sine)",
-    y = "Frequency"
-  ) +
-  theme_classic()
-
 
 
 # variable transformations ------------------------------------------------
@@ -51,20 +25,12 @@ trans_dt <-
   ) %>%
   group_by(recipient_iso3) %>%
   mutate(
-    count = lead(count, by = "year")
+    aid = lead(aid, by = "year"),
+    lead_count = lead(count, by = "year")
   ) %>%
   ungroup %>%
   na.omit
 
-# descriptives ------------------------------------------------------------
-
-ggplot(dt) + geom_histogram(aes(log(1+freq)))
-
-trans_dt %>%
-  ggplot() +
-  aes(aid, count) +
-  geom_point() +
-  geom_smooth(method = "lm")
 
 # setup panel -------------------------------------------------------------
 
@@ -74,42 +40,95 @@ pdata <- # for estimating random recipient effects with censReg
 
 # estimate main models ----------------------------------------------------
 
-# Predicting Coverage
-spec <- 
-  count ~ aid + pmm_polity + gdp + pop + unemp + disaster + civilwar +
+spec <- # specification without predictor of interest 
+  aid ~ pmm_polity + gdp + pop + unemp + disaster + civilwar +
   dist + trade + atopally + as.factor(year)
 
+# models to estimate:
+# 1. OLS
[…]

### 2021-12-19 03_analysis/ElasticNet.Rmd
Add files via upload

---
title: "ElasticNet and Lasso"
author: "Lucie Lu"
date: "12/18/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

data <- read.csv("https://raw.githubusercontent.com/milesdwilliams15/chinese_media_and_foreign_aid/main/01_data/final_data/final_data_imputed.csv")

library(Matrix)

set.seed(2234653)
split_data <- sample(nrow(data), floor(0.7*nrow(data)))
train_data <- data [split_data,]
test_data <- data [-split_data,]

library(glmnet) 
#train_sparse_3_sub <- sparse.model.matrix(~.,train_3_sub)
#test_sparse_3_sub <- sparse.model.matrix(~.,test_3_sub)

library(caret)

#set training control
train_control <- trainControl(method="cv", number = 10, 
                              search="random",
                              verboseIter=T)

sel_x <- train_data[c("count", "pmm_polity", "gdp", "pop", "unemp", "disaster", "civilwar",
                          "dist", "trade", "atopally")]

# tune the variables to get lambda and alpha for Elastic Net
fit_en <- train(y=train_data$aid, x=as.matrix(sel_x),
                              method="glmnet", tuneLength=25, trControl=train_control)

fit_elasticnet_f <- glmnet(y=train_data$aid, x=as.matrix(sel_x), 
                                 lambda = 2.17, alpha = 0.031)

coef(fit_elasticnet_f)

```

```{r}

sel_x_t <- test_data[c("count", "pmm_polity", "gdp", "pop", "unemp", "disaster", "civilwar",
                          "dist", "trade", "atopally")]

pred_elasticnet_f <- predict(fit_elasticnet_f, as.matrix(sel_x_t))
rmse_f <-  sqrt(mean((pred_elasticnet_f - test_data$aid)^2))
rmse_f

#this is very huge.....
library(ModelMetrics)
rmse(test_data$aid, pred_elasticnet_f)
```

```{r ridge}

set.seed(323445)
fit2 <- cv.glmnet(x = data.matrix(sel_x), y = train_data$aid, nfolds = 10, alpha = 1)
plot(fit2$glmnet.fit, "lambda")
plot(fit2) #MSE is huge here

# using the lambda minimizing the cross-validation error leaves us only the "count" variable. Odd.
coef(fit2, s = "lambda.min")

# nothing is left here... This gives a larger penalty with more shrinkage. 
coef(fit2, s = "lambda.1se")

```

### 2021-12-20 03_analysis/ElasticNet.Rmd
added variable transformations

@@
 data <- read.csv("https://raw.githubusercontent.com/milesdwilliams15/chinese_media_and_foreign_aid/main/01_data/final_data/final_data_imputed.csv")
+
+# MW: added variable transformations
+library(tidyverse)
+data <- data %>%
+  mutate(
+    income = gdp / pop
+  ) %>%
+  mutate_at(
+    c("aid", "count", "gdp", "income", "pop", "unemp",
+      "disaster", "dist", "distw", 
+      "distwces", "trade", "china_gdp"),
+    asinh # use inverse hyperbolic sine rather than log(1 + x)
+  ) %>%
+  group_by(recipient_iso3) %>%
+  mutate(
+    aid = lead(aid, by = "year"),
+    lead_count = lead(count, by = "year")
+  ) %>%
+  ungroup %>%
+  na.omit
 

### 2022-01-06 03_analysis/02_results_summary.Rmd
adding analysis by region

@@
 output: pdf_document
+header-includes:
+  - \usepackage{lscape}
+  - \usepackage{pdfpages}
 ---
@@
 
-**Note**: Table 1 shows results with the imputed dataset. Table 2 shows results with the non-imputed dataset.
+**Note**: Table 1 shows full panel results with the imputed dataset.
+Table 2 shows full panel results with the non-imputed dataset.
+Tables 3-5 show OLS, IV, and Lewbel IV estimates by region, respectively, for the imputed dataset.
+Tables 6-8 show the same with the non-imputed dataset.
 
@@
 ```
+
+\newpage
+\begin{landscape}
+
+```{r, results='asis'}
+load(
+  paste0(getwd(), "/ols_region_tab1.R")
+)
+cat(ols.region)
+```
+
+```{r, results='asis'}
+load(
+  paste0(getwd(), "/ivlag_region_tab1.R")
+)
+cat(ivlag.region)
+```
+
+```{r, results='asis'}
+load(
+  paste0(getwd(), "/ivlew_region_tab1.R")
+)
+cat(ivlew.region)
+```
+
+```{r, results='asis'}
+load(
+  paste0(getwd(), "/ols_region_tab2.R")
+)
+cat(ols.region)
+```
+
+```{r, results='asis'}
+load(
+  paste0(getwd(), "/ivlag_region_tab2.R")
+)
+cat(ivlag.region)
+```
+
+```{r, results='asis'}
+load(
+  paste0(getwd(), "/ivlew_region_tab2.R")
+)
+cat(ivlew.region)
+```
+
+\end{landscape}

### 2022-01-06 03_analysis/01_primary_analysis.R

@@ -99,7 +99,6 @@ iv_lag <- iv_robust(
 )
 
 ## Lewbel Instruments
-
 stage1.fit <- lm(
   update(spec, lead_count ~ .),
   data = pdata
@@ -126,6 +125,7 @@ iv_lewbel <- iv_robust(
   clusters = recipient_iso3
 )
 
+## Make regression table to summarize results:
 coef_map <- list(
   "count" = "Coverage (lag)",
   "lead_count" = "Coverage (in-year)",
@@ -160,10 +160,169 @@ reg.tab <- texreg(
   caption = "Model Estimates"
 )
 
-
-# regression tables -------------------------------------------------------
+## Save the regression table:
 save(
   reg.tab,
   file = paste0(getwd(), "/03_analysis/tab",i,".R")
 )
 
+
+# results by region -------------------------------------------------------
+
+spec <- # specification without predictor of interest 
+  aid ~ pmm_polity + gdp + pop + unemp + disaster + civilwar +
+  dist + trade + atopally + as.factor(year)
+pdata <- mutate(pdata, region = str_replace(region, "&", "+"))
+
+# models to estimate by region:
+# 1. OLS
+# 2. lag of dv as instrument for in-year dv
+# 3. internal instruments via Lewbel approach
+
+## OLS
+ols_region <- pdata %>% 
+  
+  # Split data by region
+  group_split(
+    region
+  ) %>% 
+  
+  # Estimate models for each region
+  map(
+    ~ lm_robust(
+        update(spec, ~ count + .),
+        data = .,
+        se_type = "stata",
+        clusters = recipient_iso3
+      )
+  ) %>%
+  
+  # Ensure the list of models is appropriately labeled
+  set_names(
+    sort(unique(pdata$region))
+  )
+  
+
+## With lag of DV as IV
+iv_spec <- 
+  aid ~ lead_count + pmm_polity + gdp + pop + unemp + disaster + civilwar +
+  dist + trade + atopally + as.factor(year) |
+  count +  pmm_polity + gdp + pop + unemp + disaster + civilwar +
+  dist + trade + atopally + as.factor(year)
+iv_lag_region <- pdata %>%
+  
+  # Split data by region
+  group_split(
+    region
+  ) %>%
+  
+  # Estimate models by region
+  map(
+    ~ iv_robust(
[…]

### 2022-01-27 02_clean_and_merge/02_clean_diplomacy_data.R
adding in the diplomacy data and tidying up

@@ -1,0 +1,49 @@
+###############################
+# Clean Chinese Diplomacy Data
+###############################
+
+
+# set up ------------------------------------------------------------------
+
+rm(list = ls())
+library(tidyverse)
+library(countrycode)
+
+
+# data --------------------------------------------------------------------
+
+dip_data <- read_csv(
+  paste0(
+    getwd(), "/01_data/PublicDiplomacy/ChinesePublicDiplomacy.csv"
+  )
+)
+
+
+# clean -------------------------------------------------------------------
+
+# keep only necessary variables
+dip_data <- dip_data %>%
+  transmute(
+    recipient_iso3 = countrycode(
+      receiving_country, "country.name", "iso3c"
+    ),
+    year = year,
+    govt_visits = government_visits,
+    mil_visits = str_replace(military_visits,"N/A","0") %>%
+      as.numeric(),
+    total_visits = total_elite_visits
+  )
+
+# drop rows with invalid country code:
+dip_data <- na.omit(dip_data)
+
+
+# save --------------------------------------------------------------------
+
+write_csv(
+  dip_data,
+  file = paste0(
+    getwd(),
+    "/01_data/PublicDiplomacy/clean_diplomacy_data.csv"
+  )
+)

### 2022-01-27 02_clean_and_merge/06_merge_datasets.R

@@ -16,6 +16,10 @@ aid_data <-
   read_csv(
     paste0(getwd(), "/01_data/aid_data/clean_aid_data.csv")
   )
+dip_data <-
+  read_csv(
+    paste0(getwd(), "/01_data/PublicDiplomacy/clean_diplomacy_data.csv")
+  )
 xin_data <-
   read_csv(
     paste0(getwd(), "/01_data/newsarticle/xinhua_cleaned.csv")
@@ -39,12 +43,20 @@ final_data <-
     by = c("recipient_iso3", "year")
   ) %>%
   left_join(
+    dip_data,
+    by = c("recipient_iso3", "year")
+  ) %>%
+  left_join(
     cov_data, 
     by = c("recipient_iso3", "year")
   )
 imp_final_data <-
   left_join(
     aid_data, xin_data,
+    by = c("recipient_iso3", "year")
+  ) %>%
+  left_join(
+    dip_data,
     by = c("recipient_iso3", "year")
   ) %>%
   left_join(
@@ -61,12 +73,12 @@ nrow(aid_data) - nrow(final_data) # no difference!
 
 final_data <- final_data %>%
   mutate_at(
-    c("count", "freq"),
+    c("count", "freq", "govt_visits", "mil_visits", "total_visits"),
     ~ replace_na(.x, 0)
   )
 imp_final_data <- imp_final_data %>%
   mutate_at(
-    c("count", "freq"),
+    c("count", "freq", "govt_visits", "mil_visits", "total_visits"),
     ~ replace_na(.x, 0)
   )
 

### 2022-02-10 04_paper/draft1.Rmd
updates to analysis and rough draft of intro

---
title: "Xinhua, Diplomacy, and Chinese Foreign Aid"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: yes
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
#bibliography: 07_cites/ref.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition Xinhua news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of Xinhua and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# Introduction

China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*. @fuchsRudyak2017 cite this fact as a reason Western governments assume Beijing deliberately keeps its international development finance a secret.

However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "south-south cooperation" (get cite). While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. So, absent transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition Xinhua news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of Xinhua and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.

### 2022-02-10 03_analysis/00_run_the_analysis.R

@@ -11,6 +11,7 @@ library(censReg)
 library(AER)
 library(texreg)
 library(estimatr)
+library(mgcv)
 
 
 # run analysis ------------------------------------------------------------

### 2022-02-10 03_analysis/01_primary_analysis.R

@@ -26,7 +26,8 @@ trans_dt <-
   group_by(recipient_iso3) %>%
   mutate(
     aid = lead(aid, by = "year"),
-    lead_count = lead(count, by = "year")
+    lead_count = lead(count, by = "year"),
+    lead_visits = lead(govt_visits, by = "year")
   ) %>%
   ungroup %>%
   na.omit
@@ -40,20 +41,20 @@ pdata <- # for estimating random recipient effects with censReg
 
 # estimate main models ----------------------------------------------------
 
-spec <- # specification without predictor of interest 
-  aid ~ govt_visits + pmm_polity + gdp + pop + unemp + disaster + civilwar +
+spec <- # specification without predictors of interest 
+  aid ~ pmm_polity + gdp + pop + unemp + disaster + civilwar +
   dist + trade + atopally + as.factor(year)
 
 # models to estimate:
 # 1. OLS
 # 2. multilevel Tobit with lag of dv
-# 3. selection and level ols with lag of dv
+# 3. selection (ml logit) and level (ols) with lag of dv
 # 4. lag of dv as instrument for in-year dv
 # 5. internal instruments via Lewbel approach
 
 ## OLS
 ols <- lm_robust(
-  update(spec, ~ count + .),
+  update(spec, ~ count + govt_visits + .),
   data = pdata,
   se_type = "stata",
   clusters = recipient_iso3
@@ -64,7 +65,7 @@ if(data_set == "final_data_nonimputed.csv") {
   ml_tobit <- NULL  
 } else {
   ml_tobit <- censReg(
-    update(spec, ~ count + .),
+    update(spec, ~ count + govt_visits + .),
     data = pdata,
     method = "BHHH"
   )
@@ -72,14 +73,15 @@ if(data_set == "final_data_nonimputed.csv") {
 
 
 ## Selection and Level
-ols_select <- lm_robust(
-  update(spec, aid>0 ~ count + .),
-  data = pdata,
-  se_type = "stata",
-  clusters = recipient_iso3
+glm_select <- gam(
+  update(spec, aid>0 ~ count + govt_visits + . +
+           s(recipient_iso3, bs = "re")),
[…]

### 2022-02-17 04_paper/draft1.Rmd
adding vdem to the dataset

@@
 While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
-So, absent transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
+So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
 
@@
 Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
+This work further helps in dispelling the notion that China engages in development finance in secret.

### 2022-02-17 02_clean_and_merge/05_clean_recipient_covariates.R

@@ -8,24 +8,38 @@
 rm(list = ls())       # tidy the workspace
 library(tidyverse)    # for grammar
 library(democracyData)# a bunch of democracy datasets
+library(vdem)         # to get the varieties of democracy dataset
 library(countrycode)  # to standardize country codes
 
 # democracy data ----------------------------------------------------------
 
-# For democracy data, we'll use 
+# From democracy data, we'll use 
 #   * Polity 2
 #   * Freedom House
 dem_data <-
   generate_democracy_scores_dataset(
     datasets = c(
       "polity_pmm", # polity
-      "fh_pmm"      # political + civil liberities
+      "fh_pmm"      # political + civil liberties
     ),
     "wide"
   )
 
+# To this, we'll add the five varieties of democracy indices
+#   * Electoral Democracy
+#   * Liberal Democracy
+#   * Participatory Democracy
+#   * Deliberative Democracy
+#   * Egalitarian Democracy
+vdem_data <- extract_vdem(
+  section_number = 2
+) %>%
+  select(vdem_country_name, year, v2x_polyarchy:v2x_egaldem)
+
 # limit to years needed (2000-2014)
 dem_data <- dem_data %>%
+  filter(year %in% 2000:2014)
+vdem_data <- vdem_data %>%
   filter(year %in% 2000:2014)
 
 # use iso3 code for later merging
@@ -38,6 +52,18 @@ dem_data <- dem_data %>%
   
   # Only keep vars of interest
   select(year, recipient_iso3, pmm_fh, pmm_polity)
+vdem_data <- vdem_data %>%
+  mutate(
+    recipient_iso3 = countrycode(
+      vdem_country_name, "country.name", "iso3c"
+    )
+  ) %>%
+  select(-vdem_country_name)
+
+# merge the democracy datasets
+dem_data <- left_join(
+  dem_data, vdem_data, by = c("year", "recipient_iso3")
+)
 
 
 # economic data -----------------------------------------------------------

### 2022-03-03 04_paper/draft1.Rmd
aid section draft

@@
 fontsize: 12pt
-#bibliography: 07_cites/ref.bib
+bibliography: ref.bib
 link-citations: yes
@@
 China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*.
-@fuchsRudyak2017 cite this fact as a reason Western governments assume Beijing deliberately keeps its international development finance a secret.
+@fuchsRudyak2019 cite this fact as a reason Western governments assume Beijing deliberately keeps its international development finance a secret.
 
 However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals.
-These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "south-south cooperation" (get cite).
-While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
+These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "south-south cooperation." While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
 So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
@@
 Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
-This work further helps in dispelling the notion that China engages in development finance in secret.
+
+This work further helps in dispelling the notion that China purposely engages in development finance in secret.
+Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage.
+
+# Motivations behind Chinese Foreign Aid
+
+China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors.
+While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests.
+For instance, evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
+At the same time, China seems to give more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
+Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment, and with more capacity to repay loans [@dreherEtAl2021].
+
+Surveys of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.^[Reported in blog post ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) by AidData on March 22, 2018.
+Accessed March 3, 2022].
+Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries.
+It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.
+
+If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing.
+Visual branding of aid has emerged as a growing concern among donors.
+The United States Agency for International Development (USAID), for example, cites its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief.^[See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US in Indonesia.
+Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."^[["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012.
+Accessed March 3, 2022.]
+
+# References

### 2022-03-10 04_paper/draft1.Rmd
a little more writing

@@
 While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests.
-For instance, evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
+Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
 At the same time, China seems to give more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
@@
 
-Surveys of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.^[Reported in blog post ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) by AidData on March 22, 2018.
-Accessed March 3, 2022].
-Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries.
+Two waves of surveys conducted by AidData of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.^[Reported by AidData ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) on March 22, 2018.
+Accessed March 3, 2022] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries.
 It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.
@@
 Visual branding of aid has emerged as a growing concern among donors.
-The United States Agency for International Development (USAID), for example, cites its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief.^[See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US in Indonesia.
+The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.^[See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US.
 Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."^[["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012.
@@
 
+Given the diplomatic uses of foreign aid, the enduring obscurity that surrounds Beijing's development finance is all the more puzzling.
+Unlike Western donors, China does not report its financing activities to an international organization or make its activities visible in an online database.
+To say transparency is out of character for Beijing is an understatement, but foreign aid is one issue area where transparency would arguably serve China's interests.
+So why the secrecy?
+
+As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret.
+But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.^[See @fuchsRudyak2019 for several related citations.] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing.
+Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA).
+However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.^[See this excellent summary entitled ["The Logic Behind China's Foreign Aid Agency"](https://carnegieendowment.org/2019/05/21/logic-behind-china-s-foreign-aid-agency-pub-79154) by the Carnegie Endowment for International Peace published May 21, 2019.
+Accessed March 10, 2022.]
+
 # References

### 2022-03-27 04_paper/draft1.Rmd
MW updates

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F)
+knitr::opts_chunk$set(echo = F, warning = F, message = F)
 ```
@@
 Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
-At the same time, China seems to give more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
-Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment, and with more capacity to repay loans [@dreherEtAl2021].
+At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
+Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].
 
@@
 
-Given the diplomatic uses of foreign aid, the enduring obscurity that surrounds Beijing's development finance is all the more puzzling.
+Given the diplomatic uses of foreign aid, the obscurity that surrounds Beijing's development finance is all the more puzzling.
 Unlike Western donors, China does not report its financing activities to an international organization or make its activities visible in an online database.
@@
 
+Absent transparency in reporting, there are other tools at Beijing's disposal that may complement the diplomatic objectives behind its foreign aid.
+In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives.
+We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences).
+We summarize these factors in greater detail in the following sections.
+
+# Media
+
+## First-level Agenda-setting
+
+Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public.
+That is, the public learns the importance of objects based on the amount of coverage that those objects receive.
+Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (McCombs & Shaw, 1972).
+More specifically, as Lang and Lang (1966) observe, “The mass media force attention to certain issues.
+They build up public images of political figures.
+They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about” (p.
+468).
+Since their seminal work, hundreds of studies have examined this media effect on the public.
+The vast majority support this agenda-setting notion (need some more extension or citations here).
+
+Over decades of rich research in agenda-setting, patterns show that the media affects what the public thinks about.
+That is, the salience of news media reports transfers to the perception of issue salience to the public (McCombs & Shaw, 1972).
+Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues (***).
+(transition to media objects such as nations)
+
+To extend this logic, media salience indicates significance for foreign countries named in media.
+Wanta et al.
+(2004) show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state received, the more likely respondents think the state was vitally important to the U.S.
+The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.
+
+## Selective Media Attention
+
+[Need some transition from the public to the news editors; in this story, we take news outlets as strategic actors here.]
+
+From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air.
+News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.
+
+Also, previous findings show the strategic consideration of news editors on considering what international news gets media cover.
+Not all countries in the world receive equal coverage.
+In fact, only a small portion of international events can get through the media gatekeepers and get media coverage.
+While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered.
+Golan and Wanta (2003)’s study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
+network television newscasts (ABC, CBS, NBC and CNN).
+They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa.
+A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (Chang, 1998; Sheafer et al.
+2013).
+
+Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and their newsworthiness to the news editors.
+
+## Second-level Agenda-setting
+
+In addition to swaying people’s attention, media agenda is also critical in building states’ image to international audiences.
+
+Recent research in the explication of second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by placing emphasis on certain attributes than others (Kiousis & Wu, 2008; ***).
+This entails a deeper media influence on shaping public attitudes.
+Improving one’s image to foreign audiences is the core of mediated public diplomacy.
+
+As a state-controlled media platform, *Xinhua* News Agency is often considered more than a news media platform.
+It is a public relations platform that government invests in altering its public relations with other countries.
+As such, scholars often focus on China’s mediated public diplomacy efforts through Xinhua.
+That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (Entman, 2008; Manheim, 1994; Sheafer & Gabay, 2009).
+Governments attempt to shape the global narrative positively regarding their leaders and foreign policies.
+The more Xinhua highlights positive Chinese influence on other countries, the higher potential for the news outlet to cultivate a positive foreign nation image.
+
+# Diplomacy
+
+# Hypotheses
+
+# Data and Methods
+
+To assess complementarities between China's bilateral diplomatic visits and *Xinhua* coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources.
+We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+The full dataset consists of unique recipient-year observations from 2000 to 2014.
+
+To normalize bilateral aid data, counts of country mentions, and the number of diplomatic visits, we apply the inverse hyperbolic sine transformation (ihs).
+We opt for this rather than the natural log because ihs is defined at zero (there are many zero observations for each of these variables) but is close enough in form to the natural log that estimates may still be interpreted as eslasticities or percent changes.
+
+We include several controls in analysis to adjust for sources of confounding and also to improve the precision of our estimates. Prior research points to a number of covariates that are relevant.
+
+The first set of controls consist of aid recipient characteristics.
+From the Penn World Table (version 9.1), we use real gross domestic product (GDP) in millions of 2011 USD.
+This serves as a proxy for the size of a recipient's economy.
+From the Penn World Table we also use population in millions and the number of people employed in millions.
+We normalize values using ihs to keep the transformation of the data consistent with that of the response.
+From the Institute for Health Metrics and Evaluation we use a yearly count of the number of individuals killed by natural disasters, and we again apply the ihs transformation.
+From PRIO/UCDP we use a binary measure of the presence of civil war, coded as 1 for each year where there is armed violence between two or more parties where one of the parties is the government and at least 25 battle-related deaths occur.
+To capture political and civil liberties we use Freedom House and adjust values so that higher values denote greater levels of freedom.
+We use this measure instead of Polity to avoid collinearities with civil war.
+
+We further control for bilateral characteristics between China and aid recipients.
+To account for economic ties we use total bilateral trade (imports plus exports) in millions of dollars.
+From ATOP we use a binary measure of alliances between recipients and China.
+This measure is coded as 1 if there is at least one of either a formal offensive, defensive, non-aggression, or neutrality agreement.
+Finally, form CEPII we use a measure of bilateral distance in kilometers between recipients and China.
+Both trade and distance are transformed using ihs.
+
+For our empirical strategy, we estimate models of the form
+$$\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}. \tag{1}$$
+In the above, subscript $r$ indexes the aid recipient and $t$ the year. The vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.
+
+We estimate the parameters of equation 1 using a variety of techniques to ensure the robustness of our estimates.
+First, because coverage and diplomatic visits may be endogenous to aid, we lag each by one year (along with all time-varying covariates).
+We then estimate the model via OLS and report robust standard errors clustered by recipient.
+
+However, because there are a significant number of zero observations in the outcome, OLS may yield downward biased estimates of the parameters of interest.
+We thus additionally estimate equation 1 using the Tobit maximum likelihood estimator.
+To account for unobserved heterogeneity between, and dependence within, recipients we include random recipient intercepts in the model.
+
+In the event that the process that determines whether countries receive aid from China differs from the process that determines the amount of aid given, we further separate the estimation into selection and level equations as outlined by Cragg (year?).
+The selection equation is estimated using mixed effects logit with random recipient intercepts and the level equation is estimated using OLS with cluster-robust standard errors.
+
+Finally, because within-year coverage and visits may have greatest relevance for predicting the response, using the lag of each variable in model estimation may under-estimate the complementarities between coverage and visits with aid.
+However, estimating the models using same-year coverage and visits poses a challenge due to likely endogeneity between them and the response.
+Unable to find a satisfactory set of instruments
+
+# Results
+
+```{r, results='asis'}
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
+)
+reg.tab1 <- reg.tab
+cat(reg.tab1)
+```
+
+# Conclusion
+
+\clearpage
+
 # References

### 2022-03-27 03_analysis/01_primary_analysis.R

@@ -42,7 +42,7 @@ pdata <- # for estimating random recipient effects with censReg
 # estimate main models ----------------------------------------------------
 
 spec <- # specification without predictors of interest 
-  aid ~ pmm_polity + gdp + pop + unemp + disaster + civilwar +
+  aid ~ pmm_fh + gdp + pop + unemp + disaster + civilwar +
   dist + trade + atopally + as.factor(year)
 
 # models to estimate:
@@ -89,9 +89,9 @@ ols_level <- lm_robust(
 
 ## With lag of DV as IV
 iv_spec <- 
-  aid ~ lead_count + lead_visits + pmm_polity + gdp + pop + unemp + disaster + civilwar +
+  aid ~ lead_count + lead_visits + pmm_fh + gdp + pop + unemp + disaster + civilwar +
     dist + trade + atopally + as.factor(year) |
-    count + govt_visits +  pmm_polity + gdp + pop + unemp + disaster + civilwar +
+    count + govt_visits +  pmm_fh + gdp + pop + unemp + disaster + civilwar +
     dist + trade + atopally + as.factor(year)
 iv_lag <- iv_robust(
   iv_spec,
@@ -115,9 +115,9 @@ iv_lag <- iv_robust(
 # zbr <- as_tibble(zbr)
 # ndata <- bind_cols(pdata, zbr)
 # lewbel_spec <- 
-#   aid ~ lead_count + govt_visits + pmm_polity + gdp + pop + unemp + disaster + civilwar +
+#   aid ~ lead_count + govt_visits + pmm_fh + gdp + pop + unemp + disaster + civilwar +
 #     dist + trade + atopally + as.factor(year) |
-#     pmm_polity + gdp + pop + unemp + disaster + civilwar +
+#     pmm_fh + gdp + pop + unemp + disaster + civilwar +
 #     dist + trade + atopally + as.factor(year) + 
 #     z1 + z2 + z3 + z4 + z5 + z6 + z7 + z8 + z9
 # iv_lewbel <- iv_robust(
@@ -133,7 +133,7 @@ coef_map <- list(
   "lead_count" = "Coverage (in-year)",
   "govt_visits" = "Diplomatic Visits (lag)",
   "lead_visits" = "Diplomatic Visits (in-year)",
-  "pmm_polity" = "Polity",
+  "pmm_fh" = "Polity",
   "gdp" = "GDP",
   "pop" = "Population",
[…]

### 2022-03-29 04_paper/draft1.Rmd
more updates from MW

@@
   - \floatplacement{figure}{!t}
+  - \usepackage{caption}\captionsetup[table]{skip=5pt}
+  - \usepackage{dcolumn}
+  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}
+
 abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
@@
 $$\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}. \tag{1}$$
-In the above, subscript $r$ indexes the aid recipient and $t$ the year. The vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.
+In the above, subscript $r$ indexes the aid recipient and $t$ the year.
+The vector of parameters $\tau_t$ denotes fixed year intercepts, the vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.
 
@@
 
-In the event that the process that determines whether countries receive aid from China differs from the process that determines the amount of aid given, we further separate the estimation into selection and level equations as outlined by Cragg (year?).
+In the event that the process that determines whether countries receive aid from China differs from the process that determines the amount of aid given, we further separate the estimation into selection and level equations as outlined by @cragg1971.
 The selection equation is estimated using mixed effects logit with random recipient intercepts and the level equation is estimated using OLS with cluster-robust standard errors.
@@
 However, estimating the models using same-year coverage and visits poses a challenge due to likely endogeneity between them and the response.
-Unable to find a satisfactory set of instruments
+Unable to find a satisfactory set of instruments, we take two different approaches.
+For one, we leverage the variation in the one year lag of each predictor to instrument for in-year values of each.
+This approach has been applied elsewhere in the literature when dealing with time-series data [see @braumoeller2008].
+For the second approach, we use the internal instruments approach outlined by @lewbel2012, which leverages heteroskedasticity in the data to synthesize instrumental variables.
+
+We present results from each of these approaches in the following analysis.
+Further, in the Appendix we break down the sample by geographic region in the event that different dynamics govern decisions within different sets of aid recipients.
 
@@
 
-```{r, results='asis'}
+```{r}
+library(tidyverse)
+library(kableExtra)
+dt <- read_csv(
+  paste0(str_remove(getwd(), "/04_paper"), 
+         "/01_data/final_data/final_data_imputed.csv")
+)
+```
+
+Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014.
+Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.^[For multiple imputation we used the `missRanger` R package.
+See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.] Summary statistics are shown the Appendix.
+
+```{r, include=FALSE}
 load(
@@
 
+\begin{table}
+\caption{Model Estimates}
+\begin{center}
+\begin{tabular}{l c c c c c c}
+\hline
+ & OLS & ML Tobit & Selection & Level & IV Lag & IV Lewbel \\
+\hline
+Coverage (lag)              & $0.63^{*}$      & $1.29^{**}$    & $0.18^{***}$  & $0.11$          &                 &                 \\
+                            & $(0.28)$        & $(0.43)$       & $(0.05)$      & $(0.14)$        &                 &                 \\
+Coverage (in-year)          &                 &                &               &                 & $0.67^{*}$      & $0.51^{\cdot}$  \\
+                            &                 &                &               &                 & $(0.31)$        & $(0.29)$        \\
+Diplomatic Visits (lag)     & $0.93^{**}$     & $1.54^{\cdot}$ & $0.21^{**}$   & $0.36^{*}$      &                 &                 \\
+                            & $(0.34)$        & $(0.83)$       & $(0.07)$      & $(0.15)$        &                 &                 \\
+Diplomatic Visits (in-year) &                 &                &               &                 & $1.08^{**}$     & $1.38^{**}$     \\
+                            &                 &                &               &                 & $(0.41)$        & $(0.45)$        \\
+Freedom House               & $-0.36$         & $-0.58$        & $-0.08^{*}$   & $-0.20^{*}$     & $-0.36$         & $-0.39$         \\
+                            & $(0.28)$        & $(0.40)$       & $(0.04)$      & $(0.09)$        & $(0.28)$        & $(0.29)$        \\
+GDP                         & $-2.71^{***}$   & $-4.83^{***}$  & $-0.77^{***}$ & $0.01$          & $-2.73^{***}$   & $-2.68^{***}$   \\
+                            & $(0.36)$        & $(0.48)$       & $(0.06)$      & $(0.17)$        & $(0.36)$        & $(0.34)$        \\
+Population                  & $2.52^{***}$    & $5.26^{***}$   & $0.69^{***}$  & $0.27$          & $2.51^{***}$    & $2.56^{***}$    \\
+                            & $(0.35)$        & $(0.76)$       & $(0.06)$      & $(0.17)$        & $(0.35)$        & $(0.36)$        \\
+Unemployment                & $0.18$          & $0.84$         & $0.13$        & $-0.05$         & $0.19$          & $0.20$          \\
+                            & $(0.47)$        & $(0.95)$       & $(0.08)$      & $(0.19)$        & $(0.47)$        & $(0.47)$        \\
+Disaster Deaths             & $0.18$          & $0.14$         & $0.04$        & $0.02$          & $0.18$          & $0.17$          \\
+                            & $(0.17)$        & $(0.27)$       & $(0.03)$      & $(0.05)$        & $(0.17)$        & $(0.16)$        \\
+Civil War                   & $-1.62^{\cdot}$ & $-2.77^{*}$    & $-0.38^{*}$   & $-0.75^{\cdot}$ & $-1.62^{\cdot}$ & $-1.57^{\cdot}$ \\
+                            & $(0.91)$        & $(1.25)$       & $(0.15)$      & $(0.39)$        & $(0.92)$        & $(0.91)$        \\
+Trade                       & $0.14$          & $-0.18$        & $0.04$        & $0.03$          & $0.14$          & $0.14$          \\
+                            & $(0.15)$        & $(0.18)$       & $(0.03)$      & $(0.05)$        & $(0.15)$        & $(0.15)$        \\
+Alliance                    & $0.36$          & $2.00$         & $0.29$        & $-0.64$         & $0.07$          & $-0.32$         \\
+                            & $(0.94)$        & $(2.75)$       & $(0.22)$      & $(0.47)$        & $(0.94)$        & $(1.00)$        \\
+Distance                    & $1.84^{*}$      & $4.12^{\cdot}$ & $0.49^{***}$  & $0.55$          & $1.94^{*}$      & $2.21^{*}$      \\
+                            & $(0.83)$        & $(2.34)$       & $(0.15)$      & $(0.37)$        & $(0.87)$        & $(0.87)$        \\
+\hline
+Adj. R$^2$                  & $0.19$          &              &             & $0.11$          & $0.20$          & $0.20$          \\
+Num. obs.                   & $1932$          & $1932$         & $1932$        & $982$           & $1932$          & $1932$          \\
+Deviance explained          &               &              & $0.15$        &               &               &               \\
+\hline
+\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$; $^{\cdot}p<0.1$}}
+\end{tabular}
+\label{table:coefficients}
+\end{center}
+\end{table}
+
+Table 1 reports the regression coefficients for equation 1 using each of the estimation techniques outlined in the previous section.
+Estimates for the controls comport with prior research, save that the coefficients for democracy using the Freedom House measure reach conventional levels of statistical significance in the selection and level estimates.
+Contra @dreherEtAl2018, these estimates suggest China disproportionately targets its development finance to authoritarian regimes.
+While this result is not statistically significant for the alternative estimators, the coefficient remains consistently negative across all estimation techniques.
+
+Consistent with other studies, China prioritizes recipients with smaller economies and larger populations.
+Depending on the estimation strategy, greater distance is related to *more* aid, which is a finding that runs contrary to patterns observed for DAC donors.
+This result likely is driven by China's prioritization of aid giving in Sub-Saharan Africa.
+Finally, China seems to have a bias against giving aid in the context of ongoing conflict.
+Across estimation strategies, the coefficient on civil war is negative and marginally significant ($p < 0.1$) in four of the models and statistically significant ($p < 0.05$) in two.
+
+China does not appear to discriminate on the basis of other measures of need, such as unemployment and natural disaster deaths.
+Further, trade and alliances, measures of material and strategic importance to Beijing, show no significant relationship with aid.
+
+Turning to the estimates of interest, across specifications the coefficients on media coverage in *Xinhua* and the number of diplomatic visits run in the expected direction.
+Expressed as elasticities, a majority of the estimates suggest that a one percent greater yearly instances of coverage are associated with more than half a percent to over one percent greater aid received by an aid recipient relative to another aid recipient.
+Further, one percent greater diplomatic visits is related to almost one percent to one and a half percent greater aid to that recipient relative to another.
+
 # Conclusion
@@
 
+# Appendix
+
+\clearpage
+
+\captionsetup{labelformat=AppendixTables}
+\setcounter{table}{0}
+
+```{r}
+dt %>%
+  mutate(
+    aid = aid / 1000000,
+    count = count / 1000,
+    trade = trade / 1000000000,
+    gdp = gdp / 1000000,
+    pop = pop / 1000000
+  ) %>%
+  summarize(
+    across(
+      c(aid, count, govt_visits, pmm_fh, gdp:unemp, disaster:dist, trade, atopally),
+      list(Mean = mean, Median = median, SD = sd, Min. = min, Max. = max),
+      na.rm=T
+    ) 
+  ) %>%
+  pivot_longer(cols = everything()) %>%
+  separate(
+    col = name,
+    into = c(" ", "stat"),
+    sep = "_(?=[^_]+$)"
+  ) %>%
+  mutate(
+    value = scales::comma(round(value, 2))
+  ) %>%
+  pivot_wider(
+    values_from = value,
+    names_from = stat
+  ) %>%
+  mutate(
+    " " = c(
+      "Aid (millions)",
+      "Article Mentions (thousands)",
+      "Government Visits",
+      "Freedom House",
+      "GDP (in 100 millions)",
+      "Population (in millions)",
+      "Unemployment Rate",
+      "Disaster Deaths",
+      "Civil War",
+      "Distance (in kilometers)",
+      "Trade (in millions)",
+      "Allies"
+    )
+  ) %>%
+  kbl(
+    caption = "Summary Statistics (2000-2014)",
+    booktabs = T,
+    linesep = ""
+  )
+```
+
+\clearpage
+
 # References

### 2022-03-29 03_analysis/01_primary_analysis.R

@@ -100,32 +100,45 @@ iv_lag <- iv_robust(
   clusters = recipient_iso3
 )
 
-## Lewbel Instruments
-# stage1.fit <- lm(
-#   update(spec, lead_count ~ .),
-#   data = pdata
-# )
-# eps <- resid(stage1.fit)
-# z <- model.frame(
-#   update(spec, ~ . - as.factor(year)),
-#   data = pdata
-# )[, -1]
-# zbr <- apply(z, 2, function(x) (x - mean(x)) * eps^2)
-# colnames(zbr) <- paste0("z", 1:ncol(zbr))
-# zbr <- as_tibble(zbr)
-# ndata <- bind_cols(pdata, zbr)
-# lewbel_spec <- 
-#   aid ~ lead_count + govt_visits + pmm_fh + gdp + pop + unemp + disaster + civilwar +
-#     dist + trade + atopally + as.factor(year) |
-#     pmm_fh + gdp + pop + unemp + disaster + civilwar +
-#     dist + trade + atopally + as.factor(year) + 
-#     z1 + z2 + z3 + z4 + z5 + z6 + z7 + z8 + z9
-# iv_lewbel <- iv_robust(
-#   lewbel_spec,
-#   data = ndata,
-#   se_type = "stata",
-#   clusters = recipient_iso3
-# )
+# Lewbel Instruments
+stage1.fitz <- lm(
+  update(spec, lead_count ~ .),
+  data = pdata
+)
+stage1.fitv <- lm(
+  update(spec, lead_visits ~ .),
+  data = pdata
+)
+epsz <- resid(stage1.fitz)
+epsv <- resid(stage1.fitv)
+z <- model.frame(
+  update(spec, ~ . - as.factor(year)),
+  data = pdata
+)[, -1]
+v <- model.frame(
+  update(spec, ~ . - as.factor(year)),
+  data = pdata
+)[, -1]
+zbr <- apply(z, 2, function(x) (x - mean(x)) * epsz^2)
+vbr <- apply(v, 2, function(x) (x - mean(x)) * epsv^2)
+colnames(zbr) <- paste0("z", 1:ncol(zbr))
+colnames(vbr) <- paste0("v", 1:ncol(vbr))
+zbr <- as_tibble(zbr)
+vbr <- as_tibble(vbr)
+ndata <- bind_cols(pdata, zbr, vbr)
+lewbel_spec <-
[…]

### 2022-03-31 04_paper/draft1.Rmd
more updates

@@
   - \usepackage{dcolumn}
+  - \usepackage{rotating}
   - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}
@@
 To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition Xinhua news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-We find that greater media coverage of developing countries targeted at a foreign audience via the English version of Xinhua and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
+To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
 Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
@@
 It is a public relations platform that government invests in altering its public relations with other countries.
-As such, scholars often focus on China’s mediated public diplomacy efforts through Xinhua.
+As such, scholars often focus on China’s mediated public diplomacy efforts through *Xinhua*.
 That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (Entman, 2008; Manheim, 1994; Sheafer & Gabay, 2009).
 Governments attempt to shape the global narrative positively regarding their leaders and foreign policies.
-The more Xinhua highlights positive Chinese influence on other countries, the higher potential for the news outlet to cultivate a positive foreign nation image.
+The more *Xinhua* highlights positive Chinese influence on other countries, the higher potential for the news outlet to cultivate a positive foreign nation image.
 
@@
 Turning to the estimates of interest, across specifications the coefficients on media coverage in *Xinhua* and the number of diplomatic visits run in the expected direction.
-Expressed as elasticities, a majority of the estimates suggest that a one percent greater yearly instances of coverage are associated with more than half a percent to over one percent greater aid received by an aid recipient relative to another aid recipient.
+Expressed as elasticities, the range of estimates suggest that one percent greater yearly instances of coverage in one recipient relative to another are associated with more than half a percent to over one percent greater aid received by that aid recipient.
 Further, one percent greater diplomatic visits is related to almost one percent to one and a half percent greater aid to that recipient relative to another.
+This finding is consistent with the view that China's development finance has public diplomacy and international legitimacy functions.
 
 # Conclusion
+
+Does Beijing intentionally keep its development finance a secret [@fuchsRudyak2019]? Or, does it use foreign aid as a public tool of diplomacy and to promote its own international legitimacy?
+
+In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
+These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
+To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
+To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
+Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
+
+This work further helps in dispelling the notion that China purposely engages in development finance in secret.
+Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage.
 
@@
 # Appendix
+
+Table A.1 shows summary statistics for the data sample used in the main analysis.
 
@@
 
+```{r, results='asis'}
+tabs <- c(
+  "ols_region_tab1.R",
+  "ivlag_region_tab1.R"
+)
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"), 
+         "/03_analysis/",tabs[1])
+)
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"),
+         "/03_analysis/",tabs[2])
+)
+#cat(ols.region)
+#cat(ivlag.region)
+```
+
 \clearpage

### 2022-03-31 03_analysis/01_primary_analysis.R

@@ -188,7 +188,7 @@ save(
 # results by region -------------------------------------------------------
 
 spec <- # specification without predictor of interest 
-  aid ~ govt_visits + pmm_fh + gdp + pop + unemp + disaster + civilwar +
+  aid ~ pmm_fh + gdp + pop + unemp + disaster + civilwar +
   dist + trade + atopally + as.factor(year)
 pdata <- mutate(pdata, region = str_replace(region, "&", "+"))
 
@@ -208,7 +208,7 @@ ols_region <- pdata %>%
   # Estimate models for each region
   map(
     ~ lm_robust(
-        update(spec, ~ count + .),
+        update(spec, ~ count + govt_visits + .),
         data = .,
         se_type = "stata",
         clusters = recipient_iso3
@@ -316,14 +316,18 @@ ols.region <- texreg(
   custom.coef.map = coef_map,
   include.ci = F,
   stars = c(0.001, 0.01, 0.05, 0.1),
-  caption = "OLS Estimates by Region"
+  caption = "OLS Estimates by Region",
+  caption.above = T,
+  sideways = T
 )
 ivlag.region <- texreg(
   iv_lag_region,
   custom.coef.map = coef_map,
   include.ci = F,
   stars = c(0.001, 0.01, 0.05, 0.1),
-  caption = "IV Lag Estimates by Region"
+  caption = "IV Lag Estimates by Region",
+  caption.above = T,
+  sideways = T
 )
 # ivlew.region <- texreg(
 #   iv_lewbel_region,

### 2022-04-04 04_paper/Draft2.Rmd

--- 2022-03-27 04_paper/draft1.Rmd
@@
 ---
-title: "Xinhua, Diplomacy, and Chinese Foreign Aid"
+title: "Friends Get More Money, Attention and Handshake: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
 author: ["Lucie Lu","Miles D. Williams"]
@@
 fontsize: 12pt
-bibliography: ref.bib
+bibliography: ref_Xinhua.bib
 link-citations: yes
@@
   - \floatplacement{figure}{!t}
+  - \usepackage{caption}\captionsetup[table]{skip=5pt}
+  - \usepackage{dcolumn}
+  - \usepackage{rotating}
+  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}
+
 abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
@@
 To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition Xinhua news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-We find that greater media coverage of developing countries targeted at a foreign audience via the English version of Xinhua and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
+To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
 Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
@@
 
-However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals.
-These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "south-south cooperation." While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
+However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals.
+These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
+@mattingly_when_2021 use experiments to demonstrate that investing in both foreign aids and public diplomacy efforts can improve its image abroad and reduce concerns about the threat it poses.
+Both foreign aids and public diplomacy are scarce resources for government to build bilateral relationships and improve its image abroad.
+It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and invest in bilateral relationships through aids, mediated public diplomacy and diplomatic visits.
+To our knowledge, none of the existing studies examine systematically which countries are “friends” to get more benefits of aids from the perspective of Beijing’s diplomacy efforts.
+We conceptualize two opposite modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open.
 So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
 
+We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionally larger China’s foreign aid.
 We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
+Both dimensions are important to build its public diplomacy efforts.
 These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition Xinhua news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-We find that greater media coverage of developing countries targeted at a foreign audience via the English version of Xinhua and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
-Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
+To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
+All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.
+
+To test this expectation, we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
+Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy-seeking objectives on the world stage.
 
@@
 Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage.
+To our understanding, this is the first attempt to use media agenda-setting and public diplomacy decision to explain Chinese foreign aids allocations.
+At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to aid-needed developing countries, are all crucial to achieving a state’s foreign policy goals and promoting its soft power.
 
@@
 
+Agenda-setting refers to the ability of media to signal to the public what is important.
 Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public.
 That is, the public learns the importance of objects based on the amount of coverage that those objects receive.
-Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (McCombs & Shaw, 1972).
-More specifically, as Lang and Lang (1966) observe, “The mass media force attention to certain issues.
+Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972).
+More specifically, as @berelson_mass_1966 observe, “The mass media force attention to certain issues.
 They build up public images of political figures.
@@
 
-Over decades of rich research in agenda-setting, patterns show that the media affects what the public thinks about.
-That is, the salience of news media reports transfers to the perception of issue salience to the public (McCombs & Shaw, 1972).
-Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues (***).
-(transition to media objects such as nations)
+Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963’s famous notation that the media is “stunningly successful in telling its readers what to think *about*” (p.
+13; emphasis added).
+That is, the salience of news media reports transfers to the perception of issue salience to the public (@mccombs_agenda-setting_1972).
+Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals’ perceptions of the relative importance and salience of the issues.
 
-To extend this logic, media salience indicates significance for foreign countries named in media.
-Wanta et al.
-(2004) show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state received, the more likely respondents think the state was vitally important to the U.S.
+To extend this logic, media salience indicates significance for foreign countries named in the media.
+@wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S.
 The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.
@@
 
-[Need some transition from the public to the news editors; in this story, we take news outlets as strategic actors here.]
-
+With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention.
 From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air.
@@
 
-Also, previous findings show the strategic consideration of news editors on considering what international news gets media cover.
+Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover.
 Not all countries in the world receive equal coverage.
@@
 While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered.
-Golan and Wanta (2003)’s study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
+@golan_international_2003-1’s study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
 network television newscasts (ABC, CBS, NBC and CNN).
 They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa.
-A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (Chang, 1998; Sheafer et al.
-2013).
-
-Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and their newsworthiness to the news editors.
+A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (@sheafer_relative_2014-1).
+Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.
 
@@
 
-In addition to swaying people’s attention, media agenda is also critical in building states’ image to international audiences.
+In addition to swaying people's attention, media agenda-setting is also critical in building states' image to international audiences.
+@nye_public_2008-2 suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications, with an aim to improve the country's "soft power".
+Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press.
+China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.
 
-Recent research in the explication of second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by placing emphasis on certain attributes than others (Kiousis & Wu, 2008; ***).
-This entails a deeper media influence on shaping public attitudes.
-Improving one’s image to foreign audiences is the core of mediated public diplomacy.
+Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others (@entman_theorizing_2008; @kiousis_international_2008).
+Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes.
+Improving one's image to foreign audiences is the core objective of mediated public diplomacy.
 
-As a state-controlled media platform, *Xinhua* News Agency is often considered more than a news media platform.
-It is a public relations platform that government invests in altering its public relations with other countries.
-As such, scholars often focus on China’s mediated public diplomacy efforts through Xinhua.
-That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (Entman, 2008; Manheim, 1994; Sheafer & Gabay, 2009).
-Governments attempt to shape the global narrative positively regarding their leaders and foreign policies.
-The more Xinhua highlights positive Chinese influence on other countries, the higher potential for the news outlet to cultivate a positive foreign nation image.
+As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency.
+It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy (@shambaugh_chinas_2015-1).
+It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires.
+The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea.
+It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format.
+Governments use media to tell its story to the world and improve its public relations with other countries.
+As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*.
+That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009).
 
-# Diplomacy
+Despite growing in the global media landscape, *Xinhua*, as an international broadcaster, needs foreign audiences.
+Simply providing more information will not improve their image in the Western world.
+Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack.
+As @druckman_limits_2001 presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
+On the other hand, *Xinhua* needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.
+
+Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information.
+It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
+Taking into account the limited space of **Xinhua** to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.
+
+# Public Diplomacy
+
+Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country.
+For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people – and listen to them" (@hoffman_introduction_1968, p.
+4).
+In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" (@deibel_culture_1976, p.
+15).
+
+	An image that fits into a traditional mental image of public diplomacy is "diplomats engaged in traditional negotiations under the glare of publicity" (@deibel_culture_1976, p.
+13).
+In addition to negotiations behind closed doors, records of visits have symbolic evidence to show the bilateral relationships between countries.
+The elite-level diplomacy, government-to-government diplomatic visit, is the focus in this section.
+Government-to-government visits are important as leaders' resources are scarce.
+They often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships (@nitsch_state_2005).
+Leader visits also have implications on the host leaders' security in office (@malis_state_2021) and the states' security issues (@mcmanus_making_2018).
+In all, diplomatic visits send important an important positive signal that the visiting and hosting countries support each other and have closer relationships.
+
+Visiting leaders can increase the awareness of themselves and their country among citizens in the host country.
+@goldsmith_spinning_2009 find that the impact of high-level government visits on foreign publics' opinions is contextual.
+U.S.
+visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq.
+Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy.
+The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect.
+The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries (@goldsmith_does_2021).
+In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.
+
+In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.
+From the perspective of communication, diplomatic visit is a signal of support and proximity of the countries.
+The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.
 
@@
 
+We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion.
+News editors build the credibility of the news agency to transmit information around the globe.
+High-level officials spend time and resources to visit other countries for economic or security purposes – to strengthen the bilateral relationship.
+Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically.
+In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing.
+They are in the potential friend circle.
+While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic.
+Foreign aid, instead, provides tangible and materials support to the countries in need.
+Hence, we expect China to prioritize giving foreign aid to its “friends” -- countries where China has developed multi-facet relationships through public diplomacy efforts.
+This rationale leads to our hypotheses:
+
+*H1: When developing countries receive more media exposure in *Xinhua*, they are more likely to receive more foreign aid from China.*
+
+*H2: When developing countries host or visit Chinese high-level diplomatic visits more frequently, they are more likely to receive more foreign aid from China.*
+
 # Data and Methods
 
-To assess complementarities between China's bilateral diplomatic visits and *Xinhua* coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources.
-We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+To assess complementarities between China's bilateral diplomatic visits and **Xinhua** coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources.
+We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition **Xinhua** news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
 The full dataset consists of unique recipient-year observations from 2000 to 2014.
@@
 However, estimating the models using same-year coverage and visits poses a challenge due to likely endogeneity between them and the response.
-Unable to find a satisfactory set of instruments
+Unable to find a satisfactory set of instruments, we take two different approaches.
+For one, we leverage the variation in the one year lag of each predictor to instrument for in-year values of each.
+This approach has been applied elsewhere in the literature when dealing with time-series data [see @braumoeller2008].
+For the second approach, we use the internal instruments approach outlined by @lewbel2012, which leverages heteroskedasticity in the data to synthesize instrumental variables.
 
-# Results
-
-```{r, results='asis'}
-load(
-  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
-)
-reg.tab1 <- reg.tab
-cat(reg.tab1)
-```
-
-# Conclusion
+We present results from each of these approaches in the following analysis.
+Further, in the Appendix we break down the sample by geographic region in the event that different dynamics govern decisions within different sets of aid recipients.
 

### 2022-04-04 04_paper/Draft2.Rmd
latest mw

@@
 ---
-title: "Friends Get More Money, Attention and Handshake: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
+title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
 author: ["Lucie Lu","Miles D. Williams"]
@@
 It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
-Taking into account the limited space of **Xinhua** to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.
+Taking into account the limited space of *Xinhua* to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.
 
@@
 News editors build the credibility of the news agency to transmit information around the globe.
-High-level officials spend time and resources to visit other countries for economic or security purposes – to strengthen the bilateral relationship.
-Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically.
+High-level officials spend time and resources to visit other countries for economic or security purposes to strengthen their bilateral relationship.
+Since both approaches involve limited time and resources, we expect that Beijing will choose on whom to cast the spotlight, and whom to visit, strategically.
 In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing.
@@
 While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic.
-Foreign aid, instead, provides tangible and materials support to the countries in need.
-Hence, we expect China to prioritize giving foreign aid to its “friends” -- countries where China has developed multi-facet relationships through public diplomacy efforts.
+Foreign aid, instead, provides tangible and material support to countries in need.
+Hence, we expect China to prioritize giving foreign aid to its “friends”---countries where China has developed strong relationships through public diplomacy efforts.
 This rationale leads to our hypotheses:
 
-*H1: When developing countries receive more media exposure in *Xinhua*, they are more likely to receive more foreign aid from China.*
+> *H1: When developing countries receive more media exposure in *Xinhua*, they are more likely to receive more foreign aid from China.*
 
-*H2: When developing countries host or visit Chinese high-level diplomatic visits more frequently, they are more likely to receive more foreign aid from China.*
+> *H2: When developing countries host or visit Chinese high-level diplomatic visits more frequently, they are more likely to receive more foreign aid from China.*
 
@@
 We present results from each of these approaches in the following analysis.
-Further, in the Appendix we break down the sample by geographic region in the event that different dynamics govern decisions within different sets of aid recipients.
+
+# Results
+
+```{r}
+library(tidyverse)
+library(kableExtra)
+dt <- read_csv(
+  paste0(str_remove(getwd(), "/04_paper"), 
+         "/01_data/final_data/final_data_imputed.csv")
+)
+```
+
+Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014.
+Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.^[For multiple imputation we used the `missRanger` R package.
+See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.] Summary statistics are shown the Appendix.
+
+```{r, include=FALSE}
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
+)
+reg.tab1 <- reg.tab
+cat(reg.tab1)
+```
+
+\begin{table}
+\caption{Model Estimates}
+\begin{center}
+\begin{tabular}{l c c c c c c}
+\hline
+ & OLS & ML Tobit & Selection & Level & IV Lag & IV Lewbel \\
+\hline
+Coverage (lag)              & $0.63^{*}$      & $1.29^{**}$    & $0.18^{***}$  & $0.11$          &                 &                 \\
+                            & $(0.28)$        & $(0.43)$       & $(0.05)$      & $(0.14)$        &                 &                 \\
+Coverage (in-year)          &                 &                &               &                 & $0.67^{*}$      & $0.51^{\cdot}$  \\
+                            &                 &                &               &                 & $(0.31)$        & $(0.29)$        \\
+Diplomatic Visits (lag)     & $0.93^{**}$     & $1.54^{\cdot}$ & $0.21^{**}$   & $0.36^{*}$      &                 &                 \\
+                            & $(0.34)$        & $(0.83)$       & $(0.07)$      & $(0.15)$        &                 &                 \\
+Diplomatic Visits (in-year) &                 &                &               &                 & $1.08^{**}$     & $1.38^{**}$     \\
+                            &                 &                &               &                 & $(0.41)$        & $(0.45)$        \\
+Freedom House               & $-0.36$         & $-0.58$        & $-0.08^{*}$   & $-0.20^{*}$     & $-0.36$         & $-0.39$         \\
+                            & $(0.28)$        & $(0.40)$       & $(0.04)$      & $(0.09)$        & $(0.28)$        & $(0.29)$        \\
+GDP                         & $-2.71^{***}$   & $-4.83^{***}$  & $-0.77^{***}$ & $0.01$          & $-2.73^{***}$   & $-2.68^{***}$   \\
+                            & $(0.36)$        & $(0.48)$       & $(0.06)$      & $(0.17)$        & $(0.36)$        & $(0.34)$        \\
+Population                  & $2.52^{***}$    & $5.26^{***}$   & $0.69^{***}$  & $0.27$          & $2.51^{***}$    & $2.56^{***}$    \\
+                            & $(0.35)$        & $(0.76)$       & $(0.06)$      & $(0.17)$        & $(0.35)$        & $(0.36)$        \\
+Unemployment                & $0.18$          & $0.84$         & $0.13$        & $-0.05$         & $0.19$          & $0.20$          \\
+                            & $(0.47)$        & $(0.95)$       & $(0.08)$      & $(0.19)$        & $(0.47)$        & $(0.47)$        \\
+Disaster Deaths             & $0.18$          & $0.14$         & $0.04$        & $0.02$          & $0.18$          & $0.17$          \\
+                            & $(0.17)$        & $(0.27)$       & $(0.03)$      & $(0.05)$        & $(0.17)$        & $(0.16)$        \\
+Civil War                   & $-1.62^{\cdot}$ & $-2.77^{*}$    & $-0.38^{*}$   & $-0.75^{\cdot}$ & $-1.62^{\cdot}$ & $-1.57^{\cdot}$ \\
+                            & $(0.91)$        & $(1.25)$       & $(0.15)$      & $(0.39)$        & $(0.92)$        & $(0.91)$        \\
+Trade                       & $0.14$          & $-0.18$        & $0.04$        & $0.03$          & $0.14$          & $0.14$          \\
+                            & $(0.15)$        & $(0.18)$       & $(0.03)$      & $(0.05)$        & $(0.15)$        & $(0.15)$        \\
+Alliance                    & $0.36$          & $2.00$         & $0.29$        & $-0.64$         & $0.07$          & $-0.32$         \\
+                            & $(0.94)$        & $(2.75)$       & $(0.22)$      & $(0.47)$        & $(0.94)$        & $(1.00)$        \\
+Distance                    & $1.84^{*}$      & $4.12^{\cdot}$ & $0.49^{***}$  & $0.55$          & $1.94^{*}$      & $2.21^{*}$      \\
+                            & $(0.83)$        & $(2.34)$       & $(0.15)$      & $(0.37)$        & $(0.87)$        & $(0.87)$        \\
+\hline
+Adj. R$^2$                  & $0.19$          &              &             & $0.11$          & $0.20$          & $0.20$          \\
+Num. obs.                   & $1932$          & $1932$         & $1932$        & $982$           & $1932$          & $1932$          \\
+Deviance explained          &               &              & $0.15$        &               &               &               \\
+\hline
+\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$; $^{\cdot}p<0.1$}}
+\end{tabular}
+\label{table:coefficients}
+\end{center}
+\end{table}
+
+Table 1 reports the regression coefficients for equation 1 using each of the estimation techniques outlined in the previous section.
+Estimates for the controls comport with prior research, save that the coefficients for democracy using the Freedom House measure reach conventional levels of statistical significance in the selection and level estimates.
+Contra @dreherEtAl2018, these estimates suggest China disproportionately targets its development finance to authoritarian regimes.
+While this result is not statistically significant for the alternative estimators, the coefficient remains consistently negative across all estimation techniques.
+
+Consistent with other studies, China prioritizes recipients with smaller economies and larger populations.
+Depending on the estimation strategy, greater distance is related to *more* aid, which is a finding that runs contrary to patterns observed for DAC donors.
+This result likely is driven by China's prioritization of aid giving in Sub-Saharan Africa.
+Finally, China seems to have a bias against giving aid in the context of ongoing conflict.
+Across estimation strategies, the coefficient on civil war is negative and marginally significant ($p < 0.1$) in four of the models and statistically significant ($p < 0.05$) in two.
+
+China does not appear to discriminate on the basis of other measures of need, such as unemployment and natural disaster deaths.
+Further, trade and alliances, measures of material and strategic importance to Beijing, show no significant relationship with aid.
+
+Turning to the estimates of interest, across specifications the coefficients on media coverage in *Xinhua* and the number of diplomatic visits run in the expected direction.
+Expressed as elasticities, the range of estimates suggest that one percent greater yearly instances of coverage in one recipient relative to another are associated with more than half a percent to over one percent greater aid received by that aid recipient.
+Further, one percent greater diplomatic visits is related to almost one percent to one and a half percent greater aid to that recipient relative to another.
+This finding is consistent with the view that China's development finance has public diplomacy and international legitimacy functions.
+
+# Conclusion
+
+Does Beijing intentionally keep its development finance a secret [@fuchsRudyak2019]? Or, does it use foreign aid as a public tool of diplomacy and to promote its legitimacy abroad?
+
+In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
+These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
+To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
+To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
+Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
+
+Much work, of course, remains to further interrogate the links between China's development finance and its strategic and diplomatic objectives.
+This study provides but a glimpse into the complementarities between Beijing's foreign aid and its public diplomacy.
+Even so, it contributes to our understanding of the strategic determinants of China's aid, which even now contains mysteries we have yet to resolve.
+
+\clearpage
+
+# Appendix
+
+Table A.1 shows summary statistics for the data sample used in the main analysis.
+
+\clearpage
+
+\captionsetup{labelformat=AppendixTables}
+\setcounter{table}{0}
+
+```{r}
+dt %>%
+  mutate(
+    aid = aid / 1000000,
+    count = count / 1000,
+    trade = trade / 1000000000,
+    gdp = gdp / 1000000,
+    pop = pop / 1000000
+  ) %>%
+  summarize(
+    across(
+      c(aid, count, govt_visits, pmm_fh, gdp:unemp, disaster:dist, trade, atopally),
+      list(Mean = mean, Median = median, SD = sd, Min. = min, Max. = max),
+      na.rm=T
+    ) 
+  ) %>%
+  pivot_longer(cols = everything()) %>%
+  separate(
+    col = name,
+    into = c(" ", "stat"),
+    sep = "_(?=[^_]+$)"
+  ) %>%
+  mutate(
+    value = scales::comma(round(value, 2))
+  ) %>%
+  pivot_wider(
+    values_from = value,
+    names_from = stat
+  ) %>%
+  mutate(
+    " " = c(
+      "Aid (millions)",
+      "Article Mentions (thousands)",
+      "Government Visits",
+      "Freedom House",
+      "GDP (in 100 millions)",
+      "Population (in millions)",
+      "Unemployment Rate",
+      "Disaster Deaths",
+      "Civil War",
+      "Distance (in kilometers)",
+      "Trade (in millions)",
+      "Allies"
+    )
+  ) %>%
+  kbl(
+    caption = "Summary Statistics (2000-2014)",
+    booktabs = T,
+    linesep = ""
+  )
+```
+
+```{r, results='asis'}
+tabs <- c(
+  "ols_region_tab1.R",
+  "ivlag_region_tab1.R"
+)
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"), 
+         "/03_analysis/",tabs[1])
+)
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"),
+         "/03_analysis/",tabs[2])
+)
+#cat(ols.region)
+#cat(ivlag.region)
+```
 

### 2022-04-06 05_Presentation/MPSA_AID_Paper_Presentation.tex
Add files via upload

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathabx}
\usepackage{mathpazo}
\usepackage{eulervm}
\usepackage{natbib}

%% Load the markdown package
\usepackage[citations,footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,pipeTables,tableCaptions,hybrid]{markdown}
%%begin novalidate
\markdownSetup{rendererPrototypes={
 link = {\href{#2}{#1}},
 headingOne = {\section{#1}},
 headingTwo = {\subsection{#1}},
 headingThree = {\begin{frame}\frametitle{#1}},
 headingFour = {\begin{block}{#1}},
 horizontalRule = {\end{block}}
}}

%%end novalidate

\usetheme{Dresden}
\usefonttheme{serif}
\usecolortheme{rose}

\title{Friends Get More Money, Attention and Handshakes:
Chinese Foreign Aid, Xinhua and Diplomatic Visits}

\author{Lucie Lu, Miles D. Williams\\ University of Illinois at Urbana-Champaign}
\date {MPSA 2022 \\ April 8, 2022}

\begin{document}

\maketitle

\begin{frame}{Puzzle}

\begin{itemize}
    \item China seems to deliberately keep its foreign aids secret
    \item However, aids as part of the "South-South cooperation" improve China's image abroad.
    \item Two opposite modes of interactions: foreign aids and media/public diplomacy -- secret and open
\end{itemize}

\end{frame}

\begin{frame}{Research Question and Argument}

\begin{itemize}
    \item Research Question: How does China’s foreign aid relate to Beijing’s efforts at public diplomacy and international recognition?

   \item Argument: Countries that receive higher media exposure and diplomacy efforts are
strategically more important to Beijing, and in turn receive disproportionally larger China’s
foreign aid.

\end{itemize}
\end{frame}

\begin{frame}{Argument Continued}

Two dimensions of Chinese public diplomacy efforts:

\begin{itemize}
    \item state-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
    \item China’s bilateral South-South diplomatic activities

\end{itemize}

Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} benefits of aids.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Motivations behind Chinese Foreign Aid}

Mirror Western donors:

\begin{itemize}
    \item Countries in need \begin{footnotesize} (Dreher et al. 2018) \end{footnotesize}
    \item Countries import more goods from China \begin{footnotesize} (Dreher and Fuchs, 2015) \end{footnotesize}
    \item Countries with more natural resources, closer voting alignment with Beijing, more capacity to repay loans \begin{footnotesize} (Dreher et al., 2021) \end{footnotesize}
\end{itemize}

Similar to Western donors, the transparency of foreign aid arguably serve China’s interests.
\end{frame}

\begin{frame}{Motivations behind Chinese Foreign Aid}
The obscurity seems to have more to do with capacity and logistics, rather than intention \begin{footnotesize} (Dreher et al. 2018) \end{footnotesize}. We
explore the \textbf{connections }between China’s bilateral development finance and other, visible,
activities linked to diplomatic and legitimacy-seeking objectives.

\end{frame}

\begin{frame}{Media: First-level Agenda-setting}

\begin{itemize}
\item What's covered in the news signal to the public what is important \begin{footnotesize} (McCombs \& Shaw, 1972) \end{footnotesize}

\item Media coverage of the countries will lead to the countries as a whole becoming more
salient among the public. \begin{footnotesize} (Wanta et al., 2004) \end{footnotesize}

\item News editors as gatekeepers: the increased media salience suggests the salience of the foreign countries to the audiences and the \textbf{newsworthiness }to the news editors.
\end{itemize}

\end{frame}

\begin{frame}{Media: Second-level Agenda-setting}

\begin{itemize}
\item Media are critical in building states’ image to international audiences \begin{footnotesize} (Nye, 2008) \end{footnotesize}

\item Media coverage shapes public attitudes -- core objective of mediated public diplomacy. \begin{footnotesize} (Entman, 2008; Kiousis \& Wu, 2008) \end{footnotesize}

\item Xinhua has dual roles: reporting news and building the China
image as part of Beijing’s “going out” strategy \begin{footnotesize} (Shambaugh, 2015) \end{footnotesize}

\item Its primary function is to transmit information. It reports on a variety of global issues
with different regional focuses to meet the standard of international news competitors -- \textbf{editors' choices} of what countries get more coverage
\end{itemize}

\end{frame}

\begin{frame}{Public Diplomacy}

\begin{itemize}
\item Visiting leaders can increase the awareness of themselves and their country among
citizens in the host country \begin{footnotesize} (Goldsmith \& Horiuchi, 2009; Goldsmith et al., 2021) \end{footnotesize}

\item Diplomatic visits usually come with policy agenda between two countries,
and the two are expected to cooperate in various domains through their negotiations.

\item Diplomatic visit is a signal of support and proximity of
the countries.

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Hypotheses}

\begin{itemize}

\item Both media exposure and public diplomacy involve limited time and resources,
we expect that Beijing will choose on whom to cast the spotlight, and whom to visit,
strategically.

\item We expect China to prioritize giving foreign
aid to its “friends” -- countries where China has developed strong relationships through
public diplomacy efforts.

\end{itemize}

\end{frame}

\begin{frame}{Hypotheses}

\begin{itemize} 
    \item \textit{H1:} When developing countries receive more media exposure in Xinhua, they are more
likely to receive more foreign aid from China.
    \item \textit{H2:} When developing countries host or visit Chinese high-level diplomatic visits more
frequently, they are more likely to receive more foreign aid from China.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Data and Methods}

Unique recipient-year observations from 2000 to 2014

\begin{itemize}

\item DV: bilateral aid data (AidData’s Chinese development finance dataset)

\item IV: number of diplomatic visits (AidData’s compiled yearly counts of bilateral official
diplomatic visits from China)

\item IV: counts of country media coverage (Millions of English edition Xinhua news articles scraped by the Cline Center for Advanced Social Research)

\end{itemize}

\end{frame}

\begin{frame}{Data and Methods}

\begin{itemize}

\item Covariates: aid recipient characteristics (GDP, presence of war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances)

\item Model Specifications: OLS with robust standard errors clustered by recipients; Tobit maximum likelihood estimator; selection and level equations; instrumental variables

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Results}

\end{frame}

\end{document}

### 2022-04-07 05_Presentation/MPSA_AID_Paper_Presentation.tex

@@
 \begin{itemize}
-    \item China seems to deliberately keep its foreign aids secret
-    \item However, aids as part of the "South-South cooperation" improve China's image abroad.
-    \item Two opposite modes of interactions: foreign aids and media/public diplomacy -- secret and open
+    \item China seems to deliberately keep its foreign aid giving a secret.
+    \item However, development finace arguably should promote "South-South cooperation" and improve China's image abroad.
+    \item \textit{Such goals require transparency, so what should we make of its absence?}
 \end{itemize}
@@
 \begin{itemize}
-    \item Research Question: How does China’s foreign aid relate to Beijing’s efforts at public diplomacy and international recognition?
+\item \textbf{The Puzzle}: \textit{Absent formal modes of transparency, what evidence do we have that Chinese aid serves public diplomacy?}
+\item \textbf{Argument}: \textit{We should observe complementarties between where China sends a greater number of diplomatic missions and that receive greater media coverage in outlets targeted at foreign audiences with where China gives greater foreign aid.}
+\end{itemize}
 
-   \item Argument: Countries that receive higher media exposure and diplomacy efforts are
-strategically more important to Beijing, and in turn receive disproportionally larger China’s
-foreign aid.
-
-\end{itemize}
 \end{frame}
@@
 \begin{itemize}
-    \item state-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
+    \item State-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
     \item China’s bilateral South-South diplomatic activities
@@
 
-Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} benefits of aids.
+Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} aid.
 
@@
 
-Similar to Western donors, the transparency of foreign aid arguably serve China’s interests.
 \end{frame}
@@
 \begin{frame}{Motivations behind Chinese Foreign Aid}
+
+Like Western donors, China should have an interest in generating goodwill toward Beijing.
+
+\begin{itemize}
+    \item US cites benefits from public branding of tsunami relief to Indonesia in 2004.
+    \item Surveys of policymakers show increasing influence of Beijing.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Motivations behind Chinese Foreign Aid}
+
 The obscurity seems to have more to do with capacity and logistics, rather than intention \begin{footnotesize} (Dreher et al. 2018) \end{footnotesize}. We
@@
 \begin{itemize}
-\item What's covered in the news signal to the public what is important \begin{footnotesize} (McCombs \& Shaw, 1972) \end{footnotesize}
+\item What's covered in the news signals to the public what is important \begin{footnotesize} (McCombs \& Shaw, 1972) \end{footnotesize}
 
@@
 
-\item Xinhua has dual roles: reporting news and building the China
+\item \textit{Xinhua} has dual roles: reporting news and building the China
 image as part of Beijing’s “going out” strategy \begin{footnotesize} (Shambaugh, 2015) \end{footnotesize}
@@
 
-\item Diplomatic visit is a signal of support and proximity of
-the countries.
+\item Diplomatic visit is a signal of support and closeness of countries.
 
@@
 aid to its “friends” -- countries where China has developed strong relationships through
-public diplomacy efforts.
+public diplomacy efforts -- and to countries it seeks to highlight to Western audiences.
 
@@
 \begin{itemize} 
-    \item \textit{H1:} When developing countries receive more media exposure in Xinhua, they are more
+    \item \textit{H1:} When developing countries receive more media exposure in \textit{Xinhua}, they are more
 likely to receive more foreign aid from China.
-    \item \textit{H2:} When developing countries host or visit Chinese high-level diplomatic visits more
+    \item \textit{H2:} When developing countries host Chinese high-level diplomatic visits more
 frequently, they are more likely to receive more foreign aid from China.
@@
 
-Unique recipient-year observations from 2000 to 2014
+Unique recipient-year observations from 2001 to 2014
 
@@
 
-\item IV: counts of country media coverage (Millions of English edition Xinhua news articles scraped by the Cline Center for Advanced Social Research)
+\item IV: counts of country media coverage (Millions of English edition \textit{Xinhua} news articles scraped by the Cline Center for Advanced Social Research)
 
@@
 
-\item Covariates: aid recipient characteristics (GDP, presence of war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances)
+\item Covariates: aid recipient characteristics (GDP, presence of civil war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances)
 
-\item Model Specifications: OLS with robust standard errors clustered by recipients; Tobit maximum likelihood estimator; selection and level equations; instrumental variables
+\item Model Specifications: $\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}.$
+
+\item Estimation: OLS (CR1 errors), Tobit (random recipient intercepts), Logit/Selection (random recipient intercepts), Level/OLS (CR1 errors), Lagged IV (CR1 errors), Lewbel IV (CR1 errors).
 
@@
 
+\begin{table}
+
+\caption{Model Estimates}
+\centering
+\begin{tabular}[t]{lr>{}lr>{}lr>{}lr>{}lr>{}lr>{}l}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Linear} & \multicolumn{2}{c}{Tobit} & \multicolumn{2}{c}{Selection} & \multicolumn{2}{c}{Level} & \multicolumn{2}{c}{IV Lag} & \multicolumn{2}{c}{IV Lewbel} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
+  & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI\\
+\midrule
+Coverage & 0.63 & \includegraphics[width=0.67in, height=0.17in]{} & 1.29 & \includegraphics[width=0.67in, height=0.17in]{} & 0.18 & \includegraphics[width=0.67in, height=0.17in]{} & 0.11 & \includegraphics[width=0.67in, height=0.17in]{} & 0.67 & \includegraphics[width=0.67in, height=0.17in]{} & 0.51 & \includegraphics[width=0.67in, height=0.17in]{}\\
+Visits & 0.93 & \includegraphics[width=0.67in, height=0.17in]{} & 1.54 & \includegraphics[width=0.67in, height=0.17in]{} & 0.21 & \includegraphics[width=0.67in, height=0.17in]{} & 0.36 & \includegraphics[width=0.67in, height=0.17in]{} & 1.08 & \includegraphics[width=0.67in, height=0.17in]{} & 1.38 & \includegraphics[width=0.67in, height=0.17in]{}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame}{Conclusion}
+
+\begin{itemize}
+    \item Despite a lack of formal transparency China's foreign aid serves a public role.
+    \item Beijing's development finance complements its efforts at south-south diplomacy.
+    \item And its development finance complements media coverage of aid recipients targted at Western audiences.
+\end{itemize}
+
+\textbf{Like Western donors, visibility foreign aid serves China’s interests.}
 \end{frame}

### 2022-04-07 04_paper/Draft2.Rmd
adding new 'figure'

@@
 library(kableExtra)
+library()
 dt <- read_csv(
@@
   paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
+)
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/model_list1.R") 
 )
@@
 While this result is not statistically significant for the alternative estimators, the coefficient remains consistently negative across all estimation techniques.
+
+```{r}
+coef_table <- map_dfr(
+  model_list,
+  ~ tidy(coeftest(.x))
+) %>%
+  filter(
+    str_detect(term, "count") | 
+      str_detect(term, "visits")
+  ) %>%
+  mutate(
+    conf.low = estimate - 1.96 * std.error,
+    conf.high = estimate + 1.96 * std.error,
+    term = rep(c("Coverage", "Visits"), len = n())
+  ) %>%
+  select(term, estimate, conf.low, conf.high)
+tibble(
+  "1" = coef_table$term[1:2],
+  "2" = coef_table$estimate[1:2],
+  "3" = " ",
+  "4" = coef_table$estimate[3:4],
+  "5" = " ",
+  "6" = coef_table$estimate[5:6],
+  "7" = " ",
+  "8" = coef_table$estimate[7:8],
+  "9" = " ",
+  "10" = coef_table$estimate[9:10],
+  "11" = " ",
+  "12" = coef_table$estimate[11:12],
+  "13" = " "
+) %>% 
+  mutate_if(is.numeric, function(x) round(x, 2)) %>%
+  kable("latex", booktabs = T,
+        caption = "Model Estimates",
+        col.names = c(
+          " ", rep(c("Est.", "95% CI"), len = 12)
+        )) %>%
+  kable_classic(full_width = F) %>%
+  column_spec(
+    3, image = spec_pointrange(
+      x = coef_table$estimate[1:2],
+      xmin = coef_table$conf.low[1:2],
+      xmax = coef_table$conf.high[1:2],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    5, image = spec_pointrange(
+      x = coef_table$estimate[3:4],
+      xmin = coef_table$conf.low[3:4],
+      xmax = coef_table$conf.high[3:4],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    7, image = spec_pointrange(
+      x = coef_table$estimate[5:6],
+      xmin = coef_table$conf.low[5:6],
+      xmax = coef_table$conf.high[5:6],
+      vline = 0,
+      lim = c(0, max(coef_table$conf.high[5:6]))
+    )
+  ) %>%
+  column_spec(
+    9, image = spec_pointrange(
+      x = coef_table$estimate[7:8],
+      xmin = coef_table$conf.low[7:8],
+      xmax = coef_table$conf.high[7:8],
+      vline = 0
+    )
+  )%>%
+  column_spec(
+    11, image = spec_pointrange(
+      x = coef_table$estimate[9:10],
+      xmin = coef_table$conf.low[9:10],
+      xmax = coef_table$conf.high[9:10],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    13, image = spec_pointrange(
+      x = coef_table$estimate[11:12],
+      xmin = coef_table$conf.low[11:12],
+      xmax = coef_table$conf.high[11:12],
+      vline = 0
+    )
+  ) %>%
+  add_header_above(
+    c(
+      " " = 1,
+      "Linear" = 2,
+      "Tobit" = 2,
+      "Selection" = 2,
+      "Level" = 2,
+      "IV Lag" = 2,
+      "IV Lewbel" = 2
+    )
+  )%>% cat()
+
+```
 

### 2022-04-07 03_analysis/01_primary_analysis.R

@@ -168,6 +168,10 @@ model_list <- list(
 if(data_set == "final_data_nonimputed.csv") {
   model_list[[2]] <- NULL
 }
+save(
+  model_list,
+  file = paste0(getwd(), "/03_analysis/model_list",i,".R")
+)
 
 reg.tab <- texreg(
   model_list,

### 2022-04-08 04_paper/Draft2.Rmd
save this

--- 2022-04-04 04_paper/Draft2.Rmd
@@
 )
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/model_list1.R") 
+)
 reg.tab1 <- reg.tab
@@
 While this result is not statistically significant for the alternative estimators, the coefficient remains consistently negative across all estimation techniques.
+
+```{r}
+coef_table <- map_dfr(
+  model_list,
+  ~ estimatr::tidy(lmtest::coeftest(.x))
+) %>%
+  filter(
+    str_detect(term, "count") | 
+      str_detect(term, "visits")
+  ) %>%
+  mutate(
+    conf.low = estimate - 1.96 * std.error,
+    conf.high = estimate + 1.96 * std.error,
+    term = rep(c("Coverage", "Visits"), len = n())
+  ) %>%
+  select(term, estimate, conf.low, conf.high)
+tibble(
+  "1" = coef_table$term[1:2],
+  "2" = coef_table$estimate[1:2],
+  "3" = " ",
+  "4" = coef_table$estimate[3:4],
+  "5" = " ",
+  "6" = coef_table$estimate[5:6],
+  "7" = " ",
+  "8" = coef_table$estimate[7:8],
+  "9" = " ",
+  "10" = coef_table$estimate[9:10],
+  "11" = " ",
+  "12" = coef_table$estimate[11:12],
+  "13" = " "
+) %>% 
+  mutate_if(is.numeric, function(x) round(x, 2)) %>%
+  kbl(booktabs = T,
+        caption = "Table 1: Model Estimates",
+        col.names = c(
+          " ", rep(c("Est.", "95% CI"), len = 12)
+        )) %>%
+  kable_classic(full_width = F) %>%
+  column_spec(
+    3, image = spec_pointrange(
+      x = coef_table$estimate[1:2],
+      xmin = coef_table$conf.low[1:2],
+      xmax = coef_table$conf.high[1:2],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    5, image = spec_pointrange(
+      x = coef_table$estimate[3:4],
+      xmin = coef_table$conf.low[3:4],
+      xmax = coef_table$conf.high[3:4],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    7, image = spec_pointrange(
+      x = coef_table$estimate[5:6],
+      xmin = coef_table$conf.low[5:6],
+      xmax = coef_table$conf.high[5:6],
+      vline = 0,
+      lim = c(0, max(coef_table$conf.high[5:6]))
+    )
+  ) %>%
+  column_spec(
+    9, image = spec_pointrange(
+      x = coef_table$estimate[7:8],
+      xmin = coef_table$conf.low[7:8],
+      xmax = coef_table$conf.high[7:8],
+      vline = 0
+    )
+  )%>%
+  column_spec(
+    11, image = spec_pointrange(
+      x = coef_table$estimate[9:10],
+      xmin = coef_table$conf.low[9:10],
+      xmax = coef_table$conf.high[9:10],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    13, image = spec_pointrange(
+      x = coef_table$estimate[11:12],
+      xmin = coef_table$conf.low[11:12],
+      xmax = coef_table$conf.high[11:12],
+      vline = 0
+    )
+  ) %>%
+  add_header_above(
+    c(
+      " " = 1,
+      "Linear" = 2,
+      "Tobit" = 2,
+      "Selection" = 2,
+      "Level" = 2,
+      "IV Lag" = 2,
+      "IV Lewbel" = 2
+    )
+  )
+
+```
 

### 2022-05-31 04_paper/Draft2.Rmd
commiting some minor edits

--- 2022-04-04 04_paper/Draft2.Rmd
@@
 
-abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
-We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
+abstract: "China's international development finance has been long suspecpted to serve Beijing's efforts to promote its legitamcy and image on the world stage and to support closer ties with aid recipients.
+But what is puzzling is that these goals require transparency and publicity of development projects, which are two virtues China's development finance has historically lacked.
+We bring a novel perspective to this issue by considering how China's foreign aid complements more visible foreign policy levers Beijing may use to accomplish its goals: (1) state run media coverage of developing countries intended for foreign audiences and (2) bilateral diplomatic visits.
+These activities capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
+To the extent that China’s development finance is intended to support these goals, we expect greater coverage of a developing country in Chinese media directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid.
 To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
 We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
-Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
+Our results support the view that Chinese aid allocation maps to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
 ---
@@
 These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
-@mattingly_when_2021 use experiments to demonstrate that investing in both foreign aids and public diplomacy efforts can improve its image abroad and reduce concerns about the threat it poses.
-Both foreign aids and public diplomacy are scarce resources for government to build bilateral relationships and improve its image abroad.
-It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and invest in bilateral relationships through aids, mediated public diplomacy and diplomatic visits.
-To our knowledge, none of the existing studies examine systematically which countries are “friends” to get more benefits of aids from the perspective of Beijing’s diplomacy efforts.
-We conceptualize two opposite modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open.
+@mattingly_when_2021 use experiments to demonstrate that investing in both foreign aid and public diplomacy efforts can improve China's image abroad and reduce concerns about the threat it poses.
+Importantly, both foreign aid and public diplomacy are scarce resources for building bilateral relationships and improving one's image abroad.
+It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and to invest in bilateral relationships through aid, mediated public diplomacy, and diplomatic visits.
+
+We conceptualize two distinct but complementary modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open.
 So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
 
-We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionally larger China’s foreign aid.
+We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionately larger China’s foreign aid.
 We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
@@
 Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage.
-To our understanding, this is the first attempt to use media agenda-setting and public diplomacy decision to explain Chinese foreign aids allocations.
-At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to aid-needed developing countries, are all crucial to achieving a state’s foreign policy goals and promoting its soft power.
+To our understanding, this is the first attempt to use media agenda-setting and public diplomacy to explain Chinese foreign aids allocations.
+At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to developing countries are all crucial to Beijing achieving its foreign policy goals and promoting its soft power.
 
@@
 
-To assess complementarities between China's bilateral diplomatic visits and **Xinhua** coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources.
-We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition **Xinhua** news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources.
+We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
 The full dataset consists of unique recipient-year observations from 2000 to 2014.
@@
 While this result is not statistically significant for the alternative estimators, the coefficient remains consistently negative across all estimation techniques.
+
+```{r, echo=FALSE}
+coef_table <- map_dfr(
+  model_list,
+  ~ estimatr::tidy(lmtest::coeftest(.x))
+) %>%
+  filter(
+    str_detect(term, "count") | 
+      str_detect(term, "visits")
+  ) %>%
+  mutate(
+    conf.low = estimate - 1.96 * std.error,
+    conf.high = estimate + 1.96 * std.error,
+    term = rep(c("Coverage", "Visits"), len = n())
+  ) %>%
+  select(term, estimate, conf.low, conf.high)
+tibble(
+  "1" = coef_table$term[1:2],
+  "2" = coef_table$estimate[1:2],
+  "3" = " ",
+  "4" = coef_table$estimate[3:4],
+  "5" = " ",
+  "6" = coef_table$estimate[5:6],
+  "7" = " ",
+  "8" = coef_table$estimate[7:8],
+  "9" = " ",
+  "10" = coef_table$estimate[9:10],
+  "11" = " ",
+  "12" = coef_table$estimate[11:12],
+  "13" = " "
+) %>% 
+  mutate_if(is.numeric, function(x) round(x, 2)) %>%
+  kable(booktabs = T,
+        format = "latex",
+        caption = "Table 1: Model Estimates",
+        col.names = c(
+          " ", rep(c("Est.", "95% CI"), len = 12)
+        )) %>%
+  kable_classic(full_width = F) %>%
+  column_spec(
+    3, image = spec_pointrange(
+      x = coef_table$estimate[1:2],
+      xmin = coef_table$conf.low[1:2],
+      xmax = coef_table$conf.high[1:2],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    5, image = spec_pointrange(
+      x = coef_table$estimate[3:4],
+      xmin = coef_table$conf.low[3:4],
+      xmax = coef_table$conf.high[3:4],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    7, image = spec_pointrange(
+      x = coef_table$estimate[5:6],
+      xmin = coef_table$conf.low[5:6],
+      xmax = coef_table$conf.high[5:6],
+      vline = 0,
+      lim = c(0, max(coef_table$conf.high[5:6]))
+    )
+  ) %>%
+  column_spec(
+    9, image = spec_pointrange(
+      x = coef_table$estimate[7:8],
+      xmin = coef_table$conf.low[7:8],
+      xmax = coef_table$conf.high[7:8],
+      vline = 0
+    )
+  )%>%
+  column_spec(
+    11, image = spec_pointrange(
+      x = coef_table$estimate[9:10],
+      xmin = coef_table$conf.low[9:10],
+      xmax = coef_table$conf.high[9:10],
+      vline = 0
+    )
+  ) %>%
+  column_spec(
+    13, image = spec_pointrange(
+      x = coef_table$estimate[11:12],
+      xmin = coef_table$conf.low[11:12],
+      xmax = coef_table$conf.high[11:12],
+      vline = 0
+    )
+  ) %>%
+  add_header_above(
+    c(
+      " " = 1,
+      "Linear" = 2,
+      "Tobit" = 2,
+      "Selection" = 2,
+      "Level" = 2,
+      "IV Lag" = 2,
+      "IV Lewbel" = 2
+    )
+  ) %>% cat
+
+```
 

### 2022-05-31 04_paper/slides.Rmd
commiting some minor edits

--- 2022-04-06 05_Presentation/MPSA_AID_Paper_Presentation.tex
@@
-\documentclass{beamer}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{mathabx}
-\usepackage{mathpazo}
-\usepackage{eulervm}
-\usepackage{natbib}
+---
+output: beamer_presentation
+header-includes:
+  - \usepackage[utf8]{inputenc}
+  - \usepackage[T1]{fontenc}
+  - \usepackage{mathabx}
+  - \usepackage{mathpazo}
+  - \usepackage{eulervm}
+  - \usepackage{natbib}
+---
 
@@
 
-\end{frame}
+\begin{table}
 
-\end{document}
+\caption{Model Estimates}
+\centering
+\begin{tabular}[t]{lr>{}lr>{}lr>{}lr>{}lr>{}lr>{}l}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Linear} & \multicolumn{2}{c}{Tobit} & \multicolumn{2}{c}{Selection} & \multicolumn{2}{c}{Level} & \multicolumn{2}{c}{IV Lag} & \multicolumn{2}{c}{IV Lewbel} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
+  & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI\\
+\midrule
+Coverage & 0.63 & \includegraphics[width=0.67in, height=0.17in]{} & 1.29 & \includegraphics[width=0.67in, height=0.17in]{} & 0.18 & \includegraphics[width=0.67in, height=0.17in]{} & 0.11 & \includegraphics[width=0.67in, height=0.17in]{} & 0.67 & \includegraphics[width=0.67in, height=0.17in]{} & 0.51 & \includegraphics[width=0.67in, height=0.17in]{}\\
+Visits & 0.93 & \includegraphics[width=0.67in, height=0.17in]{} & 1.54 & \includegraphics[width=0.67in, height=0.17in]{} & 0.21 & \includegraphics[width=0.67in, height=0.17in]{} & 0.36 & \includegraphics[width=0.67in, height=0.17in]{} & 1.08 & \includegraphics[width=0.67in, height=0.17in]{} & 1.38 & \includegraphics[width=0.67in, height=0.17in]{}\\
+\bottomrule
+\end{tabular}
+\end{table}

### 2022-05-31 04_paper/slides.tex
commiting some minor edits

--- 2022-05-31 04_paper/slides.Rmd
@@
----
-output: beamer_presentation
-header-includes:
-  - \usepackage[utf8]{inputenc}
-  - \usepackage[T1]{fontenc}
-  - \usepackage{mathabx}
-  - \usepackage{mathpazo}
-  - \usepackage{eulervm}
-  - \usepackage{natbib}
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  ignorenonframetext,
+]{beamer}
+\usepackage{pgfpages}
+\setbeamertemplate{caption}[numbered]
+\setbeamertemplate{caption label separator}{: }
+\setbeamercolor{caption name}{fg=normal text.fg}
+\beamertemplatenavigationsymbolsempty
+% Prevent slide breaks in the middle of a paragraph
+\widowpenalties 1 10000
+\raggedbottom
+\setbeamertemplate{part page}{
+  \centering
+  \begin{beamercolorbox}[sep=16pt,center]{part title}
+    \usebeamerfont{part title}\insertpart\par
+  \end{beamercolorbox}
+}
+\setbeamertemplate{section page}{
+  \centering
+  \begin{beamercolorbox}[sep=12pt,center]{part title}
+    \usebeamerfont{section title}\insertsection\par
+  \end{beamercolorbox}
+}
+\setbeamertemplate{subsection page}{
+  \centering
+  \begin{beamercolorbox}[sep=8pt,center]{part title}
+    \usebeamerfont{subsection title}\insertsubsection\par
+  \end{beamercolorbox}
+}
+\AtBeginPart{
+  \frame{\partpage}
+}
+\AtBeginSection{
+  \ifbibliography
+  \else
+    \frame{\sectionpage}
+  \fi
+}
+\AtBeginSubsection{
+  \frame{\subsectionpage}
+}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\newif\ifbibliography
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{mathabx}
+\usepackage{mathpazo}
+\usepackage{eulervm}
+\usepackage{natbib}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-%% Load the markdown package
+\author{}
+\date{\vspace{-2.5em}}
+
+\begin{document}
+
+\begin{frame}
+\%\% Load the markdown package
+
 \usepackage[citations,footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,pipeTables,tableCaptions,hybrid]{markdown}
-%%begin novalidate
-\markdownSetup{rendererPrototypes={
+
+\%\%begin novalidate \markdownSetup{rendererPrototypes={
  link = {\href{#2}{#1}},
@@
 
-%%end novalidate
+\%\%end novalidate
 
@@
 
-\begin{document}
+\textbackslash begin\{document\}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%
 
-\begin{frame}{Results}
+\textbackslash begin\{frame\}\{Results\}
 
@@
 \end{table}
+\end{frame}
+
+\end{document}

### 2022-06-10 04_paper/Draft3.Rmd
Add files via upload

--- 2022-04-08 04_paper/Draft2.Rmd
@@
 It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and invest in bilateral relationships through aids, mediated public diplomacy and diplomatic visits.
-To our knowledge, none of the existing studies examine systematically which countries are “friends” to get more benefits of aids from the perspective of Beijing’s diplomacy efforts.
+To our knowledge, none of the existing studies systematically examine which countries are “friends” to get more benefits of aids from the perspective of Beijing’s diplomacy efforts.
 We conceptualize two opposite modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open.
@@
 We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-Both dimensions are important to build its public diplomacy efforts.
+Both dimensions are important to building its public diplomacy efforts.
 These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
@@
 Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage.
-To our understanding, this is the first attempt to use media agenda-setting and public diplomacy decision to explain Chinese foreign aids allocations.
+To our understanding, this is the first attempt to use media agenda-setting and public diplomacy decision to explain Chinese foreign aidS allocations.
 At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to aid-needed developing countries, are all crucial to achieving a state’s foreign policy goals and promoting its soft power.
@@
 
-## First-level Agenda-setting
+## First-level Agenda-setting and Selective Media Attention
 
@@
 468).
-Since their seminal work, hundreds of studies have examined this media effect on the public.
+Since their seminal work, hundreds of studies have examined the agenda-setting effect on the public.
 The vast majority support this agenda-setting notion (need some more extension or citations here).
@@
 To extend this logic, media salience indicates significance for foreign countries named in the media.
-@wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S.
-The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.
+@wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S..
+The countries' media coverage will lead to the countries becoming more salient among the public.
 
-## Selective Media Attention
-
-With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention.
+With the implication of the media salience in mind, news editor is a source of gatekeeping power for those who can tell us where to focus our attention.
 From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air.
@@
 
-## Second-level Agenda-setting
+## Xinhua’s Effforts to Set Agenda
 
@@
 Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others (@entman_theorizing_2008; @kiousis_international_2008).
-Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes.
-Improving one's image to foreign audiences is the core objective of mediated public diplomacy.
+Compared to the first-level agenda-setting, this mechanism entails a more profound media influence on shaping public attitudes in the public’s perceptions.
+Since news media have a significant impact on shaping the public's perceptions, investing in international news markets to improve one's image to foreign audiences is the core objective of mediated public diplomacy.
 
@@
 It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format.
-Governments use media to tell its story to the world and improve its public relations with other countries.
-As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*.
+Governments use media to tell their story to the world and improve their public relations with other countries.
+As such, scholars often focus on China's mediated public diplomacy efforts through *Xinhua*.
 That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009).
@@
 
-Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information.
+Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit the information as a credible news outlet.
 It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
@@
 visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq.
-Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy.
+Again, the credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy.
 The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect.
 The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries (@goldsmith_does_2021).
-In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.
+In most cases, the host leader has the leverage to provide news frames for the journalists to report the government-to-government visit positively.
 
 In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.
-From the perspective of communication, diplomatic visit is a signal of support and proximity of the countries.
+From the perspective of communication, diplomatic visits signal the countries' support and proximity.
 The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.
@@
 )
-load(
-  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/model_list1.R") 
-)
 reg.tab1 <- reg.tab
@@
 While this result is not statistically significant for the alternative estimators, the coefficient remains consistently negative across all estimation techniques.
-
-```{r}
-coef_table <- map_dfr(
-  model_list,
-  ~ estimatr::tidy(lmtest::coeftest(.x))
-) %>%
-  filter(
-    str_detect(term, "count") | 
-      str_detect(term, "visits")
-  ) %>%
-  mutate(
-    conf.low = estimate - 1.96 * std.error,
-    conf.high = estimate + 1.96 * std.error,
-    term = rep(c("Coverage", "Visits"), len = n())
-  ) %>%
-  select(term, estimate, conf.low, conf.high)
-tibble(
-  "1" = coef_table$term[1:2],
-  "2" = coef_table$estimate[1:2],
-  "3" = " ",
-  "4" = coef_table$estimate[3:4],
-  "5" = " ",
-  "6" = coef_table$estimate[5:6],
-  "7" = " ",
-  "8" = coef_table$estimate[7:8],
-  "9" = " ",
-  "10" = coef_table$estimate[9:10],
-  "11" = " ",
-  "12" = coef_table$estimate[11:12],
-  "13" = " "
-) %>% 
-  mutate_if(is.numeric, function(x) round(x, 2)) %>%
-  kbl(booktabs = T,
-        caption = "Table 1: Model Estimates",
-        col.names = c(
-          " ", rep(c("Est.", "95% CI"), len = 12)
-        )) %>%
-  kable_classic(full_width = F) %>%
-  column_spec(
-    3, image = spec_pointrange(
-      x = coef_table$estimate[1:2],
-      xmin = coef_table$conf.low[1:2],
-      xmax = coef_table$conf.high[1:2],
-      vline = 0
-    )
-  ) %>%
-  column_spec(
-    5, image = spec_pointrange(
-      x = coef_table$estimate[3:4],
-      xmin = coef_table$conf.low[3:4],
-      xmax = coef_table$conf.high[3:4],
-      vline = 0
-    )
-  ) %>%
-  column_spec(
-    7, image = spec_pointrange(
-      x = coef_table$estimate[5:6],
-      xmin = coef_table$conf.low[5:6],
-      xmax = coef_table$conf.high[5:6],
-      vline = 0,
-      lim = c(0, max(coef_table$conf.high[5:6]))
-    )
-  ) %>%
-  column_spec(
-    9, image = spec_pointrange(
-      x = coef_table$estimate[7:8],
-      xmin = coef_table$conf.low[7:8],
-      xmax = coef_table$conf.high[7:8],
-      vline = 0
-    )
-  )%>%
-  column_spec(
-    11, image = spec_pointrange(
-      x = coef_table$estimate[9:10],
-      xmin = coef_table$conf.low[9:10],
-      xmax = coef_table$conf.high[9:10],
-      vline = 0
-    )
-  ) %>%
-  column_spec(
-    13, image = spec_pointrange(
-      x = coef_table$estimate[11:12],
-      xmin = coef_table$conf.low[11:12],
-      xmax = coef_table$conf.high[11:12],
-      vline = 0
-    )
-  ) %>%
-  add_header_above(
-    c(
-      " " = 1,
-      "Linear" = 2,
-      "Tobit" = 2,
-      "Selection" = 2,
-      "Level" = 2,
-      "IV Lag" = 2,
-      "IV Lewbel" = 2
-    )
-  )
-
-```
 
@@
 # References
+In the above, subscript $r$ indexes the aid recipient and $t$ the year. The vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.
+
+We estimate the parameters of equation 1 using a variety of techniques to ensure the robustness of our estimates.
+First, because coverage and diplomatic visits may be endogenous to aid, we lag each by one year (along with all time-varying covariates).
+We then estimate the model via OLS and report robust standard errors clustered by recipient.
+
+However, because there are a significant number of zero observations in the outcome, OLS may yield downward biased estimates of the parameters of interest.
+We thus additionally estimate equation 1 using the Tobit maximum likelihood estimator.
+To account for unobserved heterogeneity between, and dependence within, recipients we include random recipient intercepts in the model.
+
+In the event that the process that determines whether countries receive aid from China differs from the process that determines the amount of aid given, we further separate the estimation into selection and level equations as outlined by Cragg (year?).
+The selection equation is estimated using mixed effects logit with random recipient intercepts and the level equation is estimated using OLS with cluster-robust standard errors.
+
+Finally, because within-year coverage and visits may have greatest relevance for predicting the response, using the lag of each variable in model estimation may under-estimate the complementarities between coverage and visits with aid.
+However, estimating the models using same-year coverage and visits poses a challenge due to likely endogeneity between them and the response.
+Unable to find a satisfactory set of instruments
+
+# Results
+
+```{r, results='asis', eval=F}
+load(
+  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
+)
+reg.tab1 <- reg.tab
+cat(reg.tab1)
+```
+
+# Conclusion
+
+\clearpage
+
+# References

### 2022-06-12 04_paper/Draft2.Rmd
commiting minor changes to old draft

@@
 
-However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals.
-These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
-@mattingly_when_2021 use experiments to demonstrate that investing in both foreign aid and public diplomacy efforts can improve China's image abroad and reduce concerns about the threat it poses.
-Importantly, both foreign aid and public diplomacy are scarce resources for building bilateral relationships and improving one's image abroad.
-It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and to invest in bilateral relationships through aid, mediated public diplomacy, and diplomatic visits.
-
-We conceptualize two distinct but complementary modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open.
+However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals.
+These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "South-South cooperation." While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
 So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
 
-We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionately larger China’s foreign aid.
-We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-Both dimensions are important to build its public diplomacy efforts.
-These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.
+We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities.
+These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
+To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
 
-To test this expectation, we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+To test this expectation, we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
 We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
-Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy-seeking objectives on the world stage.
+Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy-seeking objectives on the world stage.
 
 This work further helps in dispelling the notion that China purposely engages in development finance in secret.
-Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage.
-To our understanding, this is the first attempt to use media agenda-setting and public diplomacy to explain Chinese foreign aids allocations.
-At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to developing countries are all crucial to Beijing achieving its foreign policy goals and promoting its soft power.
+Much to the contrary, China's development finance moves in step with visible acts of diplomacy and external-facing media coverage.
+To our understanding, this is the first attempt to use media agenda-setting and public diplomacy to explain Chinese foreign aid allocations.
+As we show, government-sponsored communication, diplomatic outreach, and financial assistance to developing countries are all crucial to Beijing achieving its foreign policy goals and promoting its soft power.
 
@@
 China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors.
-While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests.
-Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
+@bermeo2018 provides a recent and authoritative review of the literature on donor objectives, which have historically centered on some combination both of non-development geopolitical and material interests, and of legitimate efforts to address recipient country needs.
+Beijing's aid giving appears to follow a similarly mixed set of motivations.
+Studies show that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
 At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
@@
 
-Two waves of surveys conducted by AidData of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.^[Reported by AidData ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) on March 22, 2018.
-Accessed March 3, 2022] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries.
+Two waves of surveys conducted by AidData of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.[^1] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries.
 It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.
+
+[^1]: Reported by AidData ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) on March 22, 2018.
+Accessed March 3, 2022
 
@@
 Visual branding of aid has emerged as a growing concern among donors.
-The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.^[See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US.
-Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."^[["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012.
-Accessed March 3, 2022.]
+The United States Agency for International Development (USAID), for example, cited its "brand identity" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.[^2] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US.
+Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."[^3]
+
+[^2]: See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).
+
+[^3]: ["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012.
+Accessed March 3, 2022.
 
@@
 Unlike Western donors, China does not report its financing activities to an international organization or make its activities visible in an online database.
-To say transparency is out of character for Beijing is an understatement, but foreign aid is one issue area where transparency would arguably serve China's interests.
+To say transparency is out of character for Beijing is an understatement, but foreign aid is one issue where transparency would arguably serve China's interests.
 So why the secrecy?
@@
 As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret.
-But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.^[See @fuchsRudyak2019 for several related citations.] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing.
+But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.[^4] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing.
 Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA).
-However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.^[See this excellent summary entitled ["The Logic Behind China's Foreign Aid Agency"](https://carnegieendowment.org/2019/05/21/logic-behind-china-s-foreign-aid-agency-pub-79154) by the Carnegie Endowment for International Peace published May 21, 2019.
-Accessed March 10, 2022.]
+However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.[^5]
 
-Absent transparency in reporting, there are other tools at Beijing's disposal that may complement the diplomatic objectives behind its foreign aid.
-In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives.
-We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences).
-We summarize these factors in greater detail in the following sections.
+[^4]: See @fuchsRudyak2019 for several related citations.
+
+[^5]: See this excellent summary entitled ["The Logic Behind China's Foreign Aid Agency"](https://carnegieendowment.org/2019/05/21/logic-behind-china-s-foreign-aid-agency-pub-79154) by the Carnegie Endowment for International Peace published May 21, 2019.
+Accessed March 10, 2022.
+
+Nonetheless, absent transparency in reporting, it has proved difficult to provide direct confirmation that China's foreign aid is motivated by such public goals as south-south diplomacy and international legitimacy.
+However, newly available datasets offer an opportunity to empirically probe these motives.
+In this study, we explore the connections between China's bilateral development finance and critical *visible* activities linked to the diplomatic and legitimacy-seeking objectives scholars attribute to China's international development finance.
+We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing state-run media.
+
+The details of these factors are covered in greater detail in the following sections.
+However, to quickly summarize our argument, we believe diplomatic visits and media coverage are important factors for two reasons.
+
+First, they signal the importance of developing countries to Beijing.
+Just like development finance, diplomatic trips and media coverage are subject to scarcity---the first in terms of limited resources and bandwidth; the second in terms of time dedicated to writing, editing, and publishing content.
+Within the rationalist framework most often adopted by IR scholars who study international aid, this implies a direct correspondence between the countries that host diplomatic visits and that are subjects of state-sponsored news articles and the importance of developing countries to China.
+In short, visits and coverage are costly, and they therefore tell us something about which developing countries Beijing values most.
+
+Second, diplomatic visits and state-sponsored media coverage are *visible* acts.
+Though some diplomatic visits are certainly covert, most are public, even performative displays of the closeness and alignment between host and guest.
+And media coverage are by their very nature public.
+
+Thus, taken together, diplomatic visits to, and state-run media coverage of, developing countries serve both as signals of the importance of developing countries to Beijing and as visible indicators of the diplomatic and legitimacy-seeking objectives proposed to motivate China's international development finance activities.
 
@@
 Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972).
-More specifically, as @berelson_mass_1966 observe, “The mass media force attention to certain issues.
+More specifically, as @berelson_mass_1966 observe, "The mass media force attention to certain issues.
 They build up public images of political figures.
-They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about” (p.
+They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about" (p.
 468).
@@
 
-Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963’s famous notation that the media is “stunningly successful in telling its readers what to think *about*” (p.
+Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963's famous notation that the media is "stunningly successful in telling its readers what to think *about*" (p.
 13; emphasis added).
 That is, the salience of news media reports transfers to the perception of issue salience to the public (@mccombs_agenda-setting_1972).
-Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals’ perceptions of the relative importance and salience of the issues.
+Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals' perceptions of the relative importance and salience of the issues.
 
@@
 While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered.
-@golan_international_2003-1’s study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
+@golan_international_2003-1's study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
 network television newscasts (ABC, CBS, NBC and CNN).
@@
 It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
-Taking into account the limited space of *Xinhua* to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.
+Taking into account the limited space of *Xinhua* to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage.
 
@@
 Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country.
-For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people – and listen to them" (@hoffman_introduction_1968, p.
+For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" (@hoffman_introduction_1968, p.
 4).
@@
 
-We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion.
-News editors build the credibility of the news agency to transmit information around the globe.
-High-level officials spend time and resources to visit other countries for economic or security purposes to strengthen their bilateral relationship.
-Since both approaches involve limited time and resources, we expect that Beijing will choose on whom to cast the spotlight, and whom to visit, strategically.
-In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing.
-They are in the potential friend circle.
-While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic.
-Foreign aid, instead, provides tangible and material support to countries in need.
-Hence, we expect China to prioritize giving foreign aid to its “friends”---countries where China has developed strong relationships through public diplomacy efforts.
+We have made the case that Beijing's international development finance serves, among a diverse set of objectives, the promotion of diplomatic ties abroad and a particular image of China and its role in the international community.
+But, we have also highlighted a puzzle.
+If policymakers in China seek to support these goals with foreign aid, why the lack of transparency about where and how much China spends on development finance?
+We contend that limited transparency is much less a purposeful choice but a product of a complex bureaucracy that makes data reporting logistically impractical.
+Nonetheless, if China's foreign aid does indeed support this pair of objectives we should expect its giving to parallel other activities that are visible acts of diplomacy and image building.
+
+In this paper, we focus on the special roles that state-sponsored media outreach and diplomatic visits have in promoting international legitimacy and stronger diplomatic ties with "southern" country governments.
+In addition to being visible actions taken by Beijing to support these goals, envoys and media coverage are also costly due to limited resources in terms of time and funding.
+We expect, therefore, that Beijing will choose on whom to cast the spotlight, and whom to visit, strategically.
+In particular, countries that receive higher state-sponsored media coverage and that host a greater number of diplomatic visits should be strategically important in the eyes of Beijing.
+
+However, while public diplomacy is one way to increase a state's soft power, in the end, visits and media are fleeting and symbolic.
+To reinforce the objectives pursued through these visible acts of diplomacy, we argue that Beijing uses other tools, such as foreign aid, to provide tangible and material support to important countries.
+Hence, we expect that to the extent that Beijing uses foreign aid as a tool in support of these particular foreign policy goals, we should see Chinese development finance parallel these different but complementary activities.
 This rationale leads to our hypotheses:
 
-> *H1: When developing countries receive more media exposure in *Xinhua*, they are more likely to receive more foreign aid from China.*
+> *H1: When developing countries receive more media exposure in* Xinhua*, they are more likely to receive more foreign aid from China.*
 
@@
 To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources.
-We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-The full dataset consists of unique recipient-year observations from 2000 to 2014.
+We merge AidData's Chinese development finance dataset [@dreherEtAl2021 and @dreherEtAl2022] with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China [@aidData2021] and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research [-@cline2022].
+The full dataset consists of unique recipient-year observations from 2000 to 2014.[^6]
+
+[^6]: Version 1.0 of the Chinese development finance dataset may be obtained at: <http://aiddata.org/data/chinese-global-official-finance-dataset>.
+The data on China's public diplomacy can be obtained at: <http://china-dashboard.aiddata.org/>.
+Finally, the Archer portal used to access extracted features in the Global News Index at the Cline Center can be found at: <https://databank.illinois.edu/datasets/IDB-2179938>.
 
@@
 
-For our empirical strategy, we estimate models of the form
-$$\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}. \tag{1}$$
-In the above, subscript $r$ indexes the aid recipient and $t$ the year.
+For our empirical strategy, we estimate models of the form $$\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}.
+\tag{1}$$ In the above, subscript $r$ indexes the aid recipient and $t$ the year.
 The vector of parameters $\tau_t$ denotes fixed year intercepts, the vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.
@@
 Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014.
-Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.^[For multiple imputation we used the `missRanger` R package.
-See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.] Summary statistics are shown the Appendix.
+Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.[^7] Summary statistics are shown the Appendix.
+
+[^7]: For multiple imputation we used the `missRanger` R package. See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.
 
@@
 
+```{=tex}
 \begin{table}
@@
 \end{table}
-
+```
 Table 1 reports the regression coefficients for equation 1 using each of the estimation techniques outlined in the previous section.
@@
 
-In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities.
+These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
+To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
+To test this expectation we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
 We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
-Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
+Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy seeking objectives on the world stage.
 
@@
 
+```{=tex}
 \captionsetup{labelformat=AppendixTables}
 \setcounter{table}{0}
-
+```
 ```{r}

### 2022-06-12 04_paper/Draft2.Rmd
more changes to draft 2

@@
 
-However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals.
+While limited transparency is the norm for Beijing, in the context of its global development finance the lack of transparency is a puzzle.
+Many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material foreign policy goals.
 These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "South-South cooperation." While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
@@
 
-We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities.
-These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
+We probe this question empirically by exploiting two newly available datasets of Chinese media coverage of developing countries intended for foreign audiences and of China's bilateral diplomatic visits, respectively.
+These activities capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
+To the extent that China's development finance is targeted at these goals, we expect China to complement greater state-run media coverage of developing countries and greater bilateral diplomatic activity with greater development finance.
 
-To test this expectation, we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+To test this expectation, we merge AidData's Chinese development finance dataset with: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
 We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
@@
 Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA).
-However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.[^5]
+While it was established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.[^5]
 
@@
 
-Nonetheless, absent transparency in reporting, it has proved difficult to provide direct confirmation that China's foreign aid is motivated by such public goals as south-south diplomacy and international legitimacy.
-However, newly available datasets offer an opportunity to empirically probe these motives.
-In this study, we explore the connections between China's bilateral development finance and critical *visible* activities linked to the diplomatic and legitimacy-seeking objectives scholars attribute to China's international development finance.
+Absent transparency, how does Beijing leverage its global development finance in support of its diplomatic interests and international recognition?
+In this paper, we seek out an answer by looking at other kinds of visible foreign policy activities.
+We exploit two newly available datasets to explore the connections between China's bilateral development finance and critical *visible* activities linked to the diplomatic and legitimacy-seeking objectives scholars attribute to China's international development finance.
 We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing state-run media.
@@
 First, they signal the importance of developing countries to Beijing.
-Just like development finance, diplomatic trips and media coverage are subject to scarcity---the first in terms of limited resources and bandwidth; the second in terms of time dedicated to writing, editing, and publishing content.
-Within the rationalist framework most often adopted by IR scholars who study international aid, this implies a direct correspondence between the countries that host diplomatic visits and that are subjects of state-sponsored news articles and the importance of developing countries to China.
+Just like development finance, diplomatic visits and state-run media coverage are subject to scarcity---the first in terms of limited resources and bandwidth; the second in terms of time dedicated to writing, editing, and publishing content.
+Within the rationalist framework most often adopted by IR scholars who study international aid,[^6] this implies a direct correspondence between the countries that host diplomatic visits and that are subjects of state-sponsored news articles and the importance of developing countries to China.
 In short, visits and coverage are costly, and they therefore tell us something about which developing countries Beijing values most.
+
+[^6]: @bermeo2018 and @BDM2009 are exemplary examples of IR research in international aid that falls within the rationalist tradition.
 
@@
 
-# Media
+# Xinhua and Setting the Agenda
 
-## First-level Agenda-setting
+Media agenda-setting is critical in building a state's image to international audiences.
+@nye_public_2008-2 suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications with the aim to improve a country's "soft power".
+Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press.
+For this reason, China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by the international press.
+
+As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency.
+It has had a dual role: reporting news and building up China's image abroad as part of Beijing's "going out" strategy [@shambaugh_chinas_2015-1].
+It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires.
+Among many audiences, the agency targets developing countries, where the Western press has contracted out in recent years due to the decline of advertisement revenues.
+It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more viewer-friendly format.
+Beijing uses media to tell its story to the world and improve its public relations with other countries.
+As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*.
+That is, they study how government-sponsored international broadcasting contributes to influencing public or elite opinion among foreign countries [@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009)]
+
+Despite growing in the global media landscape, *Xinhua*, as an international broadcaster, needs foreign audiences.
+Simply providing more information will not improve their image in the Western world.
+As @druckman_limits_2001 notes, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
+On the other hand, *Xinhua* needs to maintain low political bias and higher professional standards to assert its brand and increase its international competitiveness.
+
+Hence, while *Xinhua* plays a major role in defining, shaping, and projecting China's image, its primary function is to transmit information.
+It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
+
+However, mere information transmission is rarely a neutral act.
+It reflects certain priorities, which in turn effect the priorities and perceptions of audiences.
+Research on the first-level and second-level agenda-setting power of media illustrates this fact.
+
+## First and Second Level Agenda-Setting
 
 Agenda-setting refers to the ability of media to signal to the public what is important.
-Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public.
-That is, the public learns the importance of objects based on the amount of coverage that those objects receive.
-Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972).
+Media coverage of a foreign country measures how important a country is to its reporting country and, in particular, to the public.
+The public learns the importance of issues based on the amount of coverage that those issues receive.
+Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues [@mccombs_agenda-setting_1972].
 More specifically, as @berelson_mass_1966 observe, "The mass media force attention to certain issues.
@@
 
-Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963's famous notation that the media is "stunningly successful in telling its readers what to think *about*" (p.
+Over decades of rich research in agenda-setting, empirical patterns support Cohen's [-@cohen_press_1963] idea that the media is "stunningly successful in telling its readers what to think *about*" (p.
 13; emphasis added).
-That is, the salience of news media reports transfers to the perception of issue salience to the public (@mccombs_agenda-setting_1972).
+That is, the salience of news media reports transfers to the perception of issue salience to the public [@mccombs_agenda-setting_1972].
 Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals' perceptions of the relative importance and salience of the issues.
 
-To extend this logic, media salience indicates significance for foreign countries named in the media.
-@wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S.
+To extend this logic, media salience indicates the significance of foreign countries named in the media.
+@wanta_agenda_2004-3 show that coverage of foreign nations in the news in the US relates to respondents' perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the US.
 The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.
 
-## Selective Media Attention
+Recent research on what is called second-level agenda-setting suggests that news media can influence how people think about a topic by emphasizing certain issues or subjects over and above others [@entman_theorizing_2008; @kiousis_international_2008].
+Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes.
+Rather simply focusing on what the public thinks about more, second-level agenda setting emphasizes media's ability to shape how the public think about issues.
+In the case of *Xinhua*, this implies an ability to shape how foreign audiences perceive the countries covered by the news service.
 
-With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention.
-From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air.
+## Editorial Gatekeeping and Scarcity
+
+When it comes to agenda-setting, the *editor* is a critical source of gatekeeping power.
+From the perspective of news outlets, limited by time and space, editors can only select a handful of stories while relegating many others to file drawer.
 News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.
 
-Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover.
+Also, previous findings show the strategic consideration of news editors in considering what international news gets media coveriage.
 Not all countries in the world receive equal coverage.
-In fact, only a small portion of international events can get through the media gatekeepers and get media coverage.
-While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered.
-@golan_international_2003-1's study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
-network television newscasts (ABC, CBS, NBC and CNN).
-They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa.
-A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (@sheafer_relative_2014-1).
-Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.
+In fact, only a small portion of international events get through the media gatekeepers.
+While powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered.
+@golan_international_2003-1's study examines how 138 elections held between 1998 and 2000 were covered by US network television newscasts (ABC, CBS, NBC and CNN).
+They found that elections in Europe, Asia or the Middle East received more substantial coverage than those in Latin America and Africa.
+A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, and geopolitical position in the world system as key predictors of coverage [@sheafer_relative_2014-1]
 
-## Second-level Agenda-setting
-
-In addition to swaying people's attention, media agenda-setting is also critical in building states' image to international audiences.
-@nye_public_2008-2 suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications, with an aim to improve the country's "soft power".
-Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press.
-China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.
-
-Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others (@entman_theorizing_2008; @kiousis_international_2008).
-Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes.
-Improving one's image to foreign audiences is the core objective of mediated public diplomacy.
-
-As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency.
-It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy (@shambaugh_chinas_2015-1).
-It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires.
-The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea.
-It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format.
-Governments use media to tell its story to the world and improve its public relations with other countries.
-As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*.
-That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009).
-
-Despite growing in the global media landscape, *Xinhua*, as an international broadcaster, needs foreign audiences.
-Simply providing more information will not improve their image in the Western world.
-Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack.
-As @druckman_limits_2001 presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
-On the other hand, *Xinhua* needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.
-
-Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information.
-It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
-Taking into account the limited space of *Xinhua* to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage.
+It seems unlikely that *Xinhua* would be an exception to the rule that biases exist in the gatekeeping decisions of editors.
+However, in the case of *Xinhua*, given the discussion of its role in China's "going out" strategy, it seems reasonable that its bias will be in favor of countries that are important to Beijing.
+In particular, it will cover countries that are important to Beijing's foreign policy goals.
 
@@
 
-Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country.
-For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" (@hoffman_introduction_1968, p.
-4).
-In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" (@deibel_culture_1976, p.
-15).
+The previous section illustrates that media agenda-setting is an essential step in a country's public diplomacy as it tries to influence the perceptions of a foreign audience.
+To borrow from one media scholar, external facing media allow Beijing to "speak to [foreign] people -- and listen to them" [@hoffman_introduction_1968, 4] In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audiences" [@deibel_culture_1976, 15].
 
-An image that fits into a traditional mental image of public diplomacy is "diplomats engaged in traditional negotiations under the glare of publicity" (@deibel_culture_1976, p.
-13).
-In addition to negotiations behind closed doors, records of visits have symbolic evidence to show the bilateral relationships between countries.
-The elite-level diplomacy, government-to-government diplomatic visit, is the focus in this section.
-Government-to-government visits are important as leaders' resources are scarce.
-They often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships (@nitsch_state_2005).
-Leader visits also have implications on the host leaders' security in office (@malis_state_2021) and the states' security issues (@mcmanus_making_2018).
-In all, diplomatic visits send important an important positive signal that the visiting and hosting countries support each other and have closer relationships.
+A traditional mental image of public diplomacy is "diplomats engaged in traditional negotiations under the glare of publicity" [@deibel_culture_1976, 13].
+In addition to negotiations behind closed doors, records of visits provide symbolic evidence of the bilateral relationship between countries.
+Perhaps most importantly, government-to-government visits are not costless---they require time and resources to orchestrate and enact.
+They often are meant to develop and strengthen bilateral relations, especially with respect to bilateral trade [@nitsch_state_2005].
+Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and on the host state's security in general [@mcmanus_making_2018].
+In all, diplomatic visits send an important signal that the visiting and hosting countries support each other and have a close relationship.
 
-Visiting leaders can increase the awareness of themselves and their country among citizens in the host country.
+Visiting leaders also can increase awareness of themselves among citizens in the host country.
 @goldsmith_spinning_2009 find that the impact of high-level government visits on foreign publics' opinions is contextual.
-U.S.
-visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq.
+US visits had large and positive impacts until the international media reported the negative aspects of the "war on terror" in Iraq.
 Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy.
 The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect.
-The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries (@goldsmith_does_2021).
-In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.
-
-In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.
-From the perspective of communication, diplomatic visit is a signal of support and proximity of the countries.
-The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.
+The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries [@goldsmith_does_2021].
 
@@
 However, while public diplomacy is one way to increase a state's soft power, in the end, visits and media are fleeting and symbolic.
-To reinforce the objectives pursued through these visible acts of diplomacy, we argue that Beijing uses other tools, such as foreign aid, to provide tangible and material support to important countries.
+To reinforce the objectives pursued through these visible acts of diplomacy, we argue that Beijing uses other tools, such as foreign aid, to provide material support to important countries.
 Hence, we expect that to the extent that Beijing uses foreign aid as a tool in support of these particular foreign policy goals, we should see Chinese development finance parallel these different but complementary activities.
@@
 We merge AidData's Chinese development finance dataset [@dreherEtAl2021 and @dreherEtAl2022] with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China [@aidData2021] and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research [-@cline2022].
-The full dataset consists of unique recipient-year observations from 2000 to 2014.[^6]
+The full dataset consists of unique recipient-year observations from 2000 to 2014.[^7]
 
-[^6]: Version 1.0 of the Chinese development finance dataset may be obtained at: <http://aiddata.org/data/chinese-global-official-finance-dataset>.
+[^7]: Version 1.0 of the Chinese development finance dataset may be obtained at: <http://aiddata.org/data/chinese-global-official-finance-dataset>.
 The data on China's public diplomacy can be obtained at: <http://china-dashboard.aiddata.org/>.
@@
 The first set of controls consist of aid recipient characteristics.
-From the Penn World Table (version 9.1), we use real gross domestic product (GDP) in millions of 2011 USD.
-This serves as a proxy for the size of a recipient's economy.
+From the Penn World Table (version 9.1), we use real gross domestic product (GDP) in millions of 2011 USD [@feenstraEtAl2015].[^8] This serves as a proxy for the size of a recipient's economy.
 From the Penn World Table we also use population in millions and the number of people employed in millions.
 We normalize values using ihs to keep the transformation of the data consistent with that of the response.
-From the Institute for Health Metrics and Evaluation we use a yearly count of the number of individuals killed by natural disasters, and we again apply the ihs transformation.
-From PRIO/UCDP we use a binary measure of the presence of civil war, coded as 1 for each year where there is armed violence between two or more parties where one of the parties is the government and at least 25 battle-related deaths occur.
-To capture political and civil liberties we use Freedom House and adjust values so that higher values denote greater levels of freedom.
-We use this measure instead of Polity to avoid collinearities with civil war.
+From the Institute for Health Metrics and Evaluation we use a yearly count of the number of individuals killed by natural disasters, and we again apply the ihs transformation [-@gbdcn2021].[^9] From PRIO/UCDP we use a binary measure of the presence of civil war, coded as 1 for each year where there is armed violence between two or more parties where one of the parties is the government and at least 25 battle-related deaths occur [@gleditschEtAl2002; @petterssonEtAl2021].[^10] To capture political and civil liberties we use Freedom House and adjust values so that higher values denote greater levels of freedom.[^11] We use this measure instead of Polity to avoid collinearities with civil war.
+
+[^8]: Available at <https://doi.org/10.15141/S50T0R>.
+
+[^9]: Available at <https://ghdx.healthdata.org/gbd-results-tool>.
+
+[^10]: Available at <https://ucdp.uu.se/downloads/index.html#armedconflict>.
+
+[^11]: Available at <https://freedomhouse.org/>.
 
 We further control for bilateral characteristics between China and aid recipients.
-To account for economic ties we use total bilateral trade (imports plus exports) in millions of dollars.
-From ATOP we use a binary measure of alliances between recipients and China.
-This measure is coded as 1 if there is at least one of either a formal offensive, defensive, non-aggression, or neutrality agreement.
-Finally, form CEPII we use a measure of bilateral distance in kilometers between recipients and China.
-Both trade and distance are transformed using ihs.
+We account for bilateral distance in kilometers between China and developing countries using the distance measure from CEPII's gravity dataset [@mayerZignago2011].
+To adjust for economic interests, we account for bilateral trade, data for which comes from CEPII's TRADEHIST dataset [@fouquinHugot2016].[^12] The former is log-transformed, while the latter is transformed via the inverse hyperbolic sine.
+Finally, to account for geostrategic interests, we use the alliance measure from the ATOP database, which takes the value 1 if Beijing and a recipient share an formal military alliance [@leedsEtAl2002].[^13]
+
+[^12]: Both available at <http://www.cepii.fr/cepii/en/bdd_modele/bdd.asp>.
+
+[^13]: Available at <http://www.atopdata.org/>.
 
@@
 Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014.
-Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.[^7] Summary statistics are shown the Appendix.
+Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.[^14] Summary statistics are shown the Appendix.
 
-[^7]: For multiple imputation we used the `missRanger` R package. See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.
+[^14]: For multiple imputation we used the `missRanger` R package. See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.
 
@@
 
-```{r, echo=FALSE}
+```{r eval=FALSE, include=FALSE}
 coef_table <- map_dfr(
@@
     )
-  ) %>% cat
+  )
 

### 2022-06-14 04_paper/Draft2.Rmd
william & mary draft

@@
 ---
-title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
+title: "Friends Get More Money, Attention, and Handshakes: Xinhua, Diplomacy, and Chinese Foreign Aid"
 author: ["Lucie Lu","Miles D. Williams"]
@@
 
-In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities.
+In this study, we tackle this question by exploiting new data on Chinese state-run media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic visits.
 These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.

### 2022-06-14 05_Presentation/aiddata_presentation.Rmd
AidData conference presentation

---
title: "Friends Get More Money, Attention, and Handshakes: Xinhua, Diplomacy, and Chinese Foreign Aid"
subtitle: "AidData Academic Roundtable"
author: ["Lucie Lu & Miles D. Williams", "*University of Illinois at Urbana-Champaign*"]
date: 'June 24, 2022'
footer: "AidData Academic Roundtable"
output: 
  powerpoint_presentation:
    reference_doc: my_template.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
```

## What We Know

```{r}
include_graphics("china_aid_logo.jpg")
```

## What We Know

China targets aid recipients on the basis of:

-   Development need (Dreher et al. 2018)

-   Who imports more Chinese goods (Dreher and Fuchs, 2015)

-   Who has more natural resources, closer voting alignment with Beijing in the UN, and more capacity to repay loans (Dreher et al., 2021)

## What We Know

-   Like Western donors, China should wield international aid, in part, to generate goodwill toward Beijing.

<!-- -->

-   We know that this has been important for the US (e.g. tsunami relief to Indonesia in 2004)

-   There is some evidence that the perception fo Beijing's influence in developing countries is growing (per differences in 2014 and 2017 waves of AidData surveys of policymakers in 126 countries)

## Puzzle

```{r}
include_graphics("low_transparency.jpeg")
```

## Puzzle

The obscurity may have more to do with capacity than intention (Dreher et al. 2018).

## Puzzle

But transparency remains.

## Research Question and Argument

**The Puzzle**: Absent traditional modes of transparency, how does Beijing leverage its international development finance in service of its diplomatic and legitimacy-seeking objectives?

## Research Question and Argument

**The Answer**: China complements other **visible** public diplomacy and legitimacy-seeking activities with greater development finance.

## Our Data

Explanatory Variables:

-   AidData's *China's Public Diplomacy Dashboard*

-   Cline Center for Advanced Social Research's *Global News Index and Extracted Features Repository*

Outcome:

-   AidData's *Global Chinese Development Finance Dataset*

## The Underlying Logic

Two dimensions of Beijing's public diplomacy:

-   "South-South" diplomatic visits

    -   Visible and symbolic show of support and aligment

-   State-sponsored *Xinhua* coverage of developing countries

    -   Agenda-setting tool and signal of Beijing's priorities for foreign audiences

## Preview

Analysis shows that:

-   More Diplomatic Visits $\to$ More Aid

-   More State-sponsored Coverage $\to$ More Aid

## Why this Matters

These results don't just support the view **that** Beijing uses aid to support diplomatic and goals and promote its agenda. They show **how** Beijing uses aid to accomplish these goals.

## Why this Matters

Visits and coverage put a spotlight on China's priorities, while aid provides material backing that these visible signals are more than hollow performances.

## Diplomacy and Media in China's Foreign Policy

**Why focus on diplomatic visits and external-facing state-run media coverage in *Xinhua*?**

## Diplomacy

-   Visiting leaders can increase the awareness of themselves and their country among citizens in the host country (Goldsmith and Horiuchi, 2009; Goldsmith et al., 2021)

-   Diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.

-   Diplomatic visit is a signal of support and closeness of countries.

## Outward Facing Media Coverage

-   What's covered in the news signals to the public what is important (McCombs and Shaw, 1972)

-   Media are critical in building states' image to international audiences (Nye, 2008)

-   Media coverage shapes public attitudes --- core objective of mediated public diplomacy. (Entman, 2008; Kiousis and Wu, 2008)

-   *Xinhua* has dual roles:

    -   Reporting news

    -   Building up China's image (e.g., Beijing's "going out" strategy --- Shambaug, 2015)

## Diplomacy and Media and China's Foreign Policy

Visits and outward media coverage are **visible** and are linked to efforts to build **strong ties** with other nations and to **shape perceptions of Beijing's priorities**.

## The Importance of Scarcity

-   Visits and coverage provide visible signals about Beijing's priorities because they are scarce commodities.

-   Visits require planning and resources to implement.

-   Writing, editing, and publishing news articles (even online) requires time and money.

-   Limited resources and bandwidth forces choices about what countries to visit and to highlight in news stories.

-   Visits and coverage reflect Beijing's **strategic priorities.**

## Here's the Bark...Where's the Bite?

-   As important as visits and coverage are for signaling Beijing's commitments and shaping global perceptions of its priorities...

-   ...they are performative acts if they are backed up by no material support.

-   Enter global development finance.

-   Beijing uses international aid to complement its visible displays of its priorities.

## Hypotheses

H1: When developing countries receive more media exposure in *Xinhua*, they receive more foreign aid from China.

H2: When developing countries host more Chinese high-level diplomatic visits, they receive more foreign aid from China.

## Data and Methods

| Variable               | Description                                                                                        | Source                                                                                               |
|------------------------|----------------------------------------------------------------------------------------------------|------------------------------------------------------------------------------------------------------|
| Outcome                | bilateral ODA-like flows from China to developing countries                                        | AidData's *Chinese Development Finance Dataset*                                                      |
| Explanatory Variable 1 | the number of bilateral diplomatic visits hosted by recipients from Beijing                        | AidData's compiled yearly counts of bilateral official diplomatic visits from China                  |
| Explanatory Variable 2 | the number of times a developing country is mentioned in a year in the English edition of *Xinhua* | compiled from millions of *Xinhua* articles scraped by the Cline Center for Advanced Social Research |

: The Data: Unique recipient-year observations from 2001-2014

## Data and Methods

-   Use multiple regression to adjust for various controls.

-   Apply numerous estimation approaches --- multiple estimators are justifiable, but each has its flaws.

## Results

```{r}
include_graphics("results_figure.jpg")
```

## Conclusion

-   Despite limited visibility through traditional means, China's global development finance serves a very public set of objectives.

-   Beijing leverages aid in support of such goals by complementing visible acts that signal its priorities with greater foreign aid spending.

-   These findings not only support the view that China's aid is partly in service of public diplomacy...

-   ...but also show how aid supports this objective.

## Thank You

Miles D. Williams: milesdw2\@illinois.edu

Lucie Lu: lul3\@illinois.edu

## Appendix: Model and Estimation

| Item          | Description                                                                                                                                                                                    |
|---------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| Covariates    | aid recipient characteristics (GDP, presence of civil war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances) |
| Specification | `asinh(aid) ~ asinh(coverage) + asinh(visits) + covariates + recipient + year`                                                                                                                 |
| Estimation    | OLS (CR1 errors), Tobit (random recipient intercepts), Logit/Selection (random recipient intercepts), Level/OLS (CR1 errors), Lagged IV (CR1 errors), Lewbel IV (CR1 errors).                  |

### 2022-06-14 05_Presentation/aiddata_presentation.tex
AidData conference presentation

--- 2022-04-07 05_Presentation/MPSA_AID_Paper_Presentation.tex
@@
 %% Load the markdown package
-\usepackage[citations,footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,pipeTables,tableCaptions,hybrid]{markdown}
+\usepackage[footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,hybrid]{markdown}
 %%begin novalidate
@@
 
-\title{Friends Get More Money, Attention and Handshakes:
-Chinese Foreign Aid, Xinhua and Diplomatic Visits}
+\title{Friends Get More Money, Attention, and Handshakes:
+Xinhua, Diplomacy, and Chinese Foreign Aid}
 
-\author{Lucie Lu, Miles D. Williams\\ University of Illinois at Urbana-Champaign}
-\date {MPSA 2022 \\ April 8, 2022}
+\author{Lucie Lu, Miles D. Williams \\ University of Illinois at Urbana-Champaign}
+\date {AidData Academic Roundtable \\ June 24, 2022}
 
@@
 
-\begin{itemize}
-    \item China seems to deliberately keep its foreign aid giving a secret.
-    \item However, development finace arguably should promote "South-South cooperation" and improve China's image abroad.
-    \item \textit{Such goals require transparency, so what should we make of its absence?}
-\end{itemize}
+\includegraphics[width=\linewidth]{china_aid_logo.jpg}
+
+\end{frame}
+
+\begin{frame}{Puzzle}
+
+\includegraphics[width=\linewidth]{low_transparency.jpeg}
 
@@
 
+\textbf{The Puzzle}: \textit{Absent traditional modes of transparency, how does Beijing leverage its international development finance in service of its diplomatic and legitimacy-seeking objectives?}
+
+\end{frame}
+
+\begin{frame}{Research Question and Argument}
+
+\textbf{Our Answer}: \textit{China complements other} \textbf{visible} \textit{foreign policy activities with greater development finance.}
+
+\begin{frame}{Research Question and Argument}
+
 \begin{itemize}
-\item \textbf{The Puzzle}: \textit{Absent formal modes of transparency, what evidence do we have that Chinese aid serves public diplomacy?}
-\item \textbf{Argument}: \textit{We should observe complementarties between where China sends a greater number of diplomatic missions and that receive greater media coverage in outlets targeted at foreign audiences with where China gives greater foreign aid.}
+  \item AidData's \textit{China's Public Diplomacy Dashboard}
+  \item Cline Center for Advanced Social Research's \textit{Global News Index and Extracted Features Repository}
 \end{itemize}
@@
 
-Two dimensions of Chinese public diplomacy efforts:
+Two dimensions of Beijing's public diplomacy:
 
 \begin{itemize}
-    \item State-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
-    \item China’s bilateral South-South diplomatic activities
+    \item China’s bilateral South-South diplomatic activities.
+    \item State-sponsored \textit{Xinhua} media coverage of developing countries intended for foreign audiences.
 
 \end{itemize}
-
-Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} aid.
 

### 2022-07-14 05_Presentation/aiddata_presentation.Rmd
added china data 2.0

@@
 -   Like Western donors, China should wield international aid, in part, to generate goodwill toward Beijing.
-
-<!-- -->
-
 -   We know that this has been important for the US (e.g. tsunami relief to Indonesia in 2004)
-
 -   There is some evidence that the perception fo Beijing's influence in developing countries is growing (per differences in 2014 and 2017 waves of AidData surveys of policymakers in 126 countries)
@@
 
-The obscurity may have more to do with capacity than intention (Dreher et al. 2018).
+-   Some argue that this is an intentional and strategic choice.
 
-## Puzzle
+-   But it may have more to do with capacity (Dreher et al. 2018).
 
-But transparency remains.
+-   Limited transparency remains nonetheless.
 
@@
 
--   AidData's *China's Public Diplomacy Dashboard*
+-   **Bilateral Diplomatic Visits** - AidData's *China's Public Diplomacy Dashboard*
 
--   Cline Center for Advanced Social Research's *Global News Index and Extracted Features Repository*
+-   **State-run Media Coverage** - Cline Center for Advanced Social Research's *Global News Index and Extracted Features Repository*
 
@@
 
--   AidData's *Global Chinese Development Finance Dataset*
+-   **Bilateral Development Assistance** - AidData's *Global Chinese Development Finance Dataset*
 
@@
 
--   Diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.
+-   Diplomatic visits usually come with a policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.
 
@@
 
-H1: When developing countries receive more media exposure in *Xinhua*, they receive more foreign aid from China.
+**H1**: When developing countries receive more media exposure in *Xinhua*, they receive more foreign aid from China.
 
-H2: When developing countries host more Chinese high-level diplomatic visits, they receive more foreign aid from China.
+**H2**: When developing countries host more Chinese high-level diplomatic visits, they receive more foreign aid from China.
 
@@
 | Variable               | Description                                                                                        | Source                                                                                               |
-|------------------------|----------------------------------------------------------------------------------------------------|------------------------------------------------------------------------------------------------------|
+|------------------|---------------------------|----------------------------|
 | Outcome                | bilateral ODA-like flows from China to developing countries                                        | AidData's *Chinese Development Finance Dataset*                                                      |
@@
 
-Miles D. Williams: milesdw2\@illinois.edu
+**Miles D. Williams**: milesdw2\@illinois.edu
 
-Lucie Lu: lul3\@illinois.edu
+**Lucie Lu**: lul3\@illinois.edu
 
@@
 | Item          | Description                                                                                                                                                                                    |
-|---------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|----------------|--------------------------------------------------------|
 | Covariates    | aid recipient characteristics (GDP, presence of civil war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances) |

### 2022-07-20 02_clean_and_merge/01_clean_aid_data.R
Chinese development finance data good to go!

@@ -7,12 +7,14 @@
 
 rm(list = ls())
 library(tidyverse)
+library(here)
 
 
 # attach raw aid data -----------------------------------------------------
 
 aid_data <- readxl::read_excel(
-  paste0(getwd(), "/01_data/aid_data/GlobalChineseOfficialFinanceDataset_v1.0.xlsx")
+  path = here("01_data/aid_data/AidDatasGlobalChineseDevelopmentFinanceDataset_v2.0.xlsx"),
+  sheet = 'Global_CDF2.0'
 )
 dim(aid_data) # check size
 
@@ -21,27 +23,45 @@ dim(aid_data) # check size
 # clean -------------------------------------------------------------------
 
 # The readme pdf that came with the data suggests only keeping observations
-# listed as recommended_for_research==TRUE:
+# listed as 'Recommended For Aggregates' == 'Yes'
 aid_data <-
   aid_data %>%
-  filter(recommended_for_research==T)
+  filter(`Recommended For Aggregates`=='Yes')
 dim(aid_data) # new size
-
+sectors <- paste(
+  aid_data$`Sector Code`,
+  aid_data$`Sector Name`
+) %>% unique
 # Now, clean up recipient names and aid values by year:
 clean_data <- aid_data %>%
   
   # only keep year, recipient code (use iso3), and aid amount
   transmute(
-    year = year,
-    recipient_iso3 = recipient_iso3,
-    aid = usd_defl_2014 # amount in 2014 US dollars
+    year = `Commitment Year`,
+    recipient_iso3 = countrycode::countrycode(
+      Recipient, 'country.name', 'iso3c'
+    ),
+    value =  `Amount (Constant USD2017)`,# amount in 2017 US dollars,
+    flow_class = case_when(
+      `Flow Class` == 'ODA-like' ~ 'aid',
+      `Flow Class` == 'OOF-like' ~ 'debt',
+      TRUE ~ 'drop'
+    ),
+    sector_code = `Sector Code`,
+    sector_name = `Sector Name`
   ) %>%
   
-  # there are multiple lines per recipient per year. aggregate
-  # to the sum of aid to a recipient in a given year:
+  # aggregate the data to be at the recipient-year level:
   group_by(year, recipient_iso3) %>%
   summarize(
-    aid = sum(aid, na.rm=T)
+    aid = sum(value[flow_class=='aid'], na.rm=T),
+    debt = sum(value[flow_class=='debt'], na.rm=T),
[…]

### 2022-07-31 02_clean_and_merge/Aid_articles_identified.Rmd
Add files via upload

---
title: "Aids/development news articles identified"
author: "Lucie Lu"
date: "2022-07-26"
output: pdf_document
---

```{r}

dat <- read.csv("C:/Users/Lucie Lu/Box Sync/Xinhua co-authoring project/Xinhua news articles_2000-2017/Xinhua_2016.csv")

```

```{r}
library(tidytext)
library(dplyr)
library(tm)
library(stringr)
```

```{r, eval=F}
# pre-processing
dat$title

tidy_news <- dat %>%
    select(title) %>%
    unnest_tokens("word", title)

data("stop_words")
tidy_news <- tidy_news %>%
      anti_join(stop_words)

tidy_news %>%
  count(word) %>%
    arrange(desc(n))
```

```{r}

# dictionary-based approach to subset

aids_dictionary <- c("aid", "aids", "donor",
                     "lend", "development", "investment", "growth", "support",
                         "business", "help", "construction", "education", "funds", "projects", 
                     "donate", "assist")

dat$title2 <- str_replace_all(dat$title, "[[:punct:]]", "")
sent2 <- unlist(strsplit(dat$title2, "\\."))
aids_news_title <- grep(paste0('\\b', aids_dictionary, '\\b', collapse = '|'), sent2, ignore.case = TRUE, value = TRUE)
pattern <- paste0(aids_news_title, collapse = "|")

```

```{r}
#check how long a code runs...
library(tictoc)
tic("processing")
aids_news3 <- dat[str_detect(dat$title2, pattern),]
toc()

#aids_news <- dat[str_detect(dat$title[1:100], paste(aids_news_title, collapse="|")),]
#sent[grepl(pattern, sent)]
#later on refine the search as extracted_organizations including China or Chinese

```

```{r}

#write.csv(aids_news3, "aids_news_2016.csv")

```

### 2022-07-31 02_clean_and_merge/Pre-process China related and country counts.Rmd
Add files via upload

---
title: "Pre-process China related and country counts"
author: "Lucie Lu"
date: "2022-07-29"
output: pdf_document
---

```{r}
#list.files("Xinhua_news_articles_2000-2014/")
df2 <- read.csv("C:/Users/Lucie Lu/Box Sync/Xinhua co-authoring project/Xinhua news articles_economy_related/Xinhua_2000_2017_aids_related.csv")

library(tidyverse)
#https://hbctraining.github.io/Intro-to-R/lessons/08_intro_tidyverse.html
df2  <- df2 %>% 
  rownames_to_column() %>% 
  as_tibble()

```

```{r}

#replace empty country with extracted locations
#df2$country <- ifelse(df2$country==" ", df2$extracted_locations, df2$country)

country2 <- matrix(NA, nrow=nrow(df2), ncol=1)
for (i in 1:nrow(df2)){
  country2[i,] <- ifelse(df2$country[i]=="", df2$extracted_locations[i], df2$country[i])
}

country2 <- as.data.frame(country2)
df2 <- cbind(df2, country2)
colnames(df2)[14] <- "country2_completed" 
```

```{r}
# identify China-related articles
#df2$country2_completed
China_dictionary <- c("People's Republic of China", "China", "Shanghai", "Beijing", "province")

df2$China_related <- ifelse(grepl(paste0('\\b', China_dictionary, '\\b', collapse = '|'), df2$country2_completed, China_dictionary)==T, 1, 0)
table(df2$China_related) #38618 related articles

```
```{r create years}

df2$year <- case_when(
  df2$column_label == 1 ~ "2000",
  df2$column_label == 2 ~ "2001",
  df2$column_label == 3 ~ "2002",
  df2$column_label == 4 ~ "2003",
  df2$column_label == 5 ~ "2004",
  df2$column_label == 6 ~ "2005",
  df2$column_label == 7 ~ "2006",
  df2$column_label == 8 ~ "2007",
  df2$column_label == 9 ~ "2008",
  df2$column_label == 10 ~ "2009",
  df2$column_label == 11 ~ "2010",
  df2$column_label == 12 ~ "2011",
  df2$column_label == 13 ~ "2012",
  df2$column_label == 14 ~ "2013",
  df2$column_label == 15 ~ "2014",
  df2$column_label == 16 ~ "2015",
  df2$column_label == 17 ~ "2016",
  df2$column_label == 18 ~ "2017",

)

table(df2$column_label)
table(df2$year)
df2$year <- as.factor(df2$year)
```

```{r}
df2_subset_China <- subset(df2, df2$China_related==1) #38,618
```

```{r, eval=F}

#write.csv(df2, "Xinhua_2000_2017_aids_news_processed.csv")
#write.csv(df2_subset_China, "Xinhua_2000_2017_aids_news_China_subset_processed.csv")
```

##########################################

```{r import multiple .csv files, eval=F}
#https://stackoverflow.com/questions/11433432/how-to-import-multiple-csv-files-at-once

temp = list.files(pattern="*.csv")
for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i]))
```

```{r}
Xinhua_2000 <- subset(df2_subset_China, df2_subset_China$year==2000)
#head(Xinhua_2000)
library(tidyverse)
#https://hbctraining.github.io/Intro-to-R/lessons/08_intro_tidyverse.html
#Xinhua_2000 <- Xinhua_2000 %>% 
#  rownames_to_column() %>% 
#  as_tibble()
```

```{r}
df <- Xinhua_2000  %>% 
  pull(country2_completed) %>% 
  str_split("[|]")
#max(lengths(df))
names(df) <- Xinhua_2000$rowname
#df_2 <- data.frame(matrix(unlist(df), nrow=max(lengths(df)), byrow=TRUE),stringsAsFactors=FALSE)
library (plyr)
df_2 <- ldply (df, data.frame)
df_2 <- tibble(df_2)
colnames(df_2)[2] <- "country_mentioned"
df_2$countries_mentioned <- as.factor(df_2$country_mentioned)
```

```{r}
library(dplyr)
new_df_2000 <- df_2 %>% 
  group_by(country_mentioned) %>%
  dplyr::summarise(n = n()) %>%
#  df_2[!(df_2$country_mentioned == "")]  %>%
#  mutate(freq = round(n/sum(n), 3)) %>%
  arrange(desc(n))

new_df_2000 <- new_df_2000 %>% mutate(year==2000)

new_df_2000$year <- 2000

#duplicated name summarise in both packages
#https://statisticsglobe.com/r-error-must-only-be-used-inside-dplyr-verbs
```

```{r get frequency table}

new_df_2000 <- new_df_2000%>% 
  group_by(country_mentioned) %>%
#  dplyr::summarise(n2 = n()) %>%
  mutate(freq_perc = round(100 * n / nrow(Xinhua_2000), digits=2)) #total number of reports in 2000

```

```{r}
# list all of the files here
new_df_2000
new_df_2001
new_df_2002
new_df_2003
new_df_2004
new_df_2005
new_df_2006
new_df_2007
new_df_2008 
new_df_2009
new_df_2010
new_df_2011
new_df_2012
new_df_2013
new_df_2014
new_df_2015
new_df_2016
new_df_2017
```

```{r}
all_df <- rbind(new_df_2000,
new_df_2001,
new_df_2002,
new_df_2003,
new_df_2004,
new_df_2005,
new_df_2006,
new_df_2007,
new_df_2008,
new_df_2009,
new_df_2010,
new_df_2011,
new_df_2012,
new_df_2013,
new_df_2014,
new_df_2015,
new_df_2016,
new_df_2017)
str(all_df)
```

```{r}
#write.csv(all_df, "total.csv")

```

```{r}
#transform to wide data for better graphing
#https://cran.r-project.org/web/packages/data.table/vignettes/datatable-reshape.html
library(data.table)
county_counts_long <- reshape2::dcast(all_df, country_mentioned ~ year, value.var = "n")
head(data_all_df_long, 50)

county_freq_long <- reshape2::dcast(all_df, country_mentioned ~ year, value.var = "freq_perc")
head(county_freq_long, 50)
```

```{r}

#install.packages("countrycode")
library(countrycode)
codelist$country.name.de
```

```{r export data}
#write.csv(county_counts_long, "Xinhua_2001_2017_aids_related_articles_countrycounts.csv")
```

```{r export data frequency}
#write.csv(county_freq_long, "Xinhua_2001_2017_aids_related_articles_countryfrequencies.csv")
```

### 2022-07-31 02_clean_and_merge/combine files.Rmd
Add files via upload

---
title: "Combine files"
author: "Lucie Lu"
date: "2022-07-28"
output: pdf_document
---

```{r setup}
# problem setting up working directory
# https://stackoverflow.com/questions/44816945/why-setting-working-directory-in-r-notebook-doesnt-change-working-directory-in
require("knitr")
knitr::opts_knit$set(root.dir = normalizePath("C:/Users/Lucie Lu/Box Sync/Xinhua co-authoring project/Xinhua news articles_economy_related")) 
getwd()
```

```{r}
temp <- list.files(pattern="*.csv")
listOfDataFrames <- lapply(temp, read.csv)
```

```{r}

df2 <- bind_rows(listOfDataFrames, .id = "column_label")
#115,675 observations

```

```{r}

#write.csv(df2, "Xinhua_2000_2017_aids_related.csv")

```

### 2022-07-31 02_clean_and_merge/03_02_Pre-process China related and country counts.Rmd
Update and rename Pre-process China related and country counts.Rmd to 03_02_Pre-process China related and country counts.Rmd

--- 2022-07-31 02_clean_and_merge/Pre-process China related and country counts.Rmd
@@
 ```{r}
+## need to manually update the years and files
 Xinhua_2000 <- subset(df2_subset_China, df2_subset_China$year==2000)

### 2022-08-02 02_clean_and_merge/02_clean_diplomacy_data.R
recommiting updated data

@@ -19,7 +19,8 @@ dip_data <- read_csv(
 
 
 # clean -------------------------------------------------------------------
-
+fix_it <- function(x) str_replace(x,"N/A","0") %>%
+  as.numeric()
 # keep only necessary variables
 dip_data <- dip_data %>%
   transmute(
@@ -27,10 +28,9 @@ dip_data <- dip_data %>%
       receiving_country, "country.name", "iso3c"
     ),
     year = year,
-    govt_visits = government_visits,
-    mil_visits = str_replace(military_visits,"N/A","0") %>%
-      as.numeric(),
-    total_visits = total_elite_visits
+    govt_visits = fix_it(government_visits),
+    mil_visits = fix_it(military_visits),
+    total_visits = fix_it(total_elite_visits)
   )
 
 # drop rows with invalid country code:

### 2022-08-02 02_clean_and_merge/04_clean_archer_data.R

@@ -7,72 +7,29 @@
 
 rm(list = ls())
 library(tidyverse)
-
+library(here)
 
 # load data ---------------------------------------------------------------
 
-counts <- read_csv(
-  "01_data/newsarticle/Xinhua_2001_2014_countrycounts.csv"
+data <- read_csv(
+  #"01_data/newsarticle/Xinhua_2001_2014_countrycounts.csv"
+  here("01_data/newsarticle/Xinhua_2010_2017_aids_articles_relevant_refined.csv")
 )
-frequs <- read_csv(
-  "01_data/newsarticle/Xinhua_2001_2014_countryfrequencies.csv"
-)
-
 
 # clean -------------------------------------------------------------------
 
-counts <- counts %>%
-  select(-X1) %>%
-  gather(
-    year, "count", -country_mentioned
-  ) %>%
+data <- data[,-c(1:3)] %>%
   mutate(
-    count = replace_na(count, 0),
-    country = str_remove(country_mentioned, ".*, "),
-    recipient_iso3 = countrycode::countrycode(
-      country, "country.name", "iso3c"
-    )
+    across(frequncies_by_year:counts_by_year, ~replace_na(.x, 0))
   ) %>%
-  select(recipient_iso3, year, count) %>%
-  na.omit
-
-frequs <- frequs %>%
-  select(-X1) %>%
-  gather(
-    year, "freq", -country_mentioned
-  ) %>%
-  mutate(
-    count = replace_na(freq, 0),
-    country = str_remove(country_mentioned, ".*, "),
-    recipient_iso3 = countrycode::countrycode(
-      country, "country.name", "iso3c"
-    )
-  ) %>%
-  select(recipient_iso3, year, freq) %>%
-  na.omit
-
-
-# merge country counts and freq -------------------------------------------
-
-archer <- full_join(
-  counts, frequs, by = c("recipient_iso3", "year")
-)
-
-# deal with duplicates and additional missing values
-archer <- archer %>%
-  mutate(
-    freq = replace_na(freq, 0)
-  ) %>%
-  group_by(recipient_iso3, year) %>%
-  summarize(
-    count = max(count),
-    freq  = max(freq)
+  rename(
+    frequencies_by_year = frequncies_by_year,
+    recipient_iso3 = recipient_iso
   )
-
 
 # save --------------------------------------------------------------------
 
 write_csv(
-  archer,
[…]

### 2022-08-02 02_clean_and_merge/05_clean_recipient_covariates.R

@@ -7,99 +7,70 @@
 
 rm(list = ls())       # tidy the workspace
 library(tidyverse)    # for grammar
+# remotes::install_github("xmarquez/democracyData", force = TRUE)
 library(democracyData)# a bunch of democracy datasets
-library(vdem)         # to get the varieties of democracy dataset
 library(countrycode)  # to standardize country codes
 
 # democracy data ----------------------------------------------------------
 
 # From democracy data, we'll use 
 #   * Polity 2
-#   * Freedom House
-dem_data <-
-  generate_democracy_scores_dataset(
-    datasets = c(
-      "polity_pmm", # polity
-      "fh_pmm"      # political + civil liberties
-    ),
-    "wide"
-  )
-
-# To this, we'll add the five varieties of democracy indices
-#   * Electoral Democracy
-#   * Liberal Democracy
-#   * Participatory Democracy
-#   * Deliberative Democracy
-#   * Egalitarian Democracy
-vdem_data <- extract_vdem(
-  section_number = 2
-) %>%
-  select(vdem_country_name, year, v2x_polyarchy:v2x_egaldem)
-
-# limit to years needed (1999-2017)
-dem_data <- dem_data %>%
-  filter(year %in% 1999:2017)
-vdem_data <- vdem_data %>%
-  filter(year %in% 1999:2017)
-
-# use iso3 code for later merging
-dem_data <- dem_data %>%
-  mutate(
-    recipient_iso3 = countrycode::countrycode(
-      cown, "cown", "iso3c"
-    )
-  ) %>%
-  
-  # Only keep vars of interest
-  select(year, recipient_iso3, pmm_fh, pmm_polity)
-vdem_data <- vdem_data %>%
-  mutate(
-    recipient_iso3 = countrycode(
-      vdem_country_name, "country.name", "iso3c"
-    )
-  ) %>%
-  select(-vdem_country_name)
-
-# merge the democracy datasets
-dem_data <- left_join(
-  dem_data, vdem_data, by = c("year", "recipient_iso3")
+#   * V-Dem
+dem_data <- generate_democracy_scores_dataset(
+  datasets = c('polity_annual', 'fh_full', 'vdem'),
+  output_format = 'wide',
+  verbose = F
 )
+dem_data <- dem_data %>%
+  transmute(
+    recipient_iso3 = countrycode(
+      cown, 'cown', 'iso3c'
+    ),
+    year,
+    polity2,
[…]

### 2022-08-02 02_clean_and_merge/06_merge_datasets.R

@@ -73,12 +73,14 @@ nrow(aid_data) - nrow(final_data) # no difference!
 
 final_data <- final_data %>%
   mutate_at(
-    c("count", "freq", "govt_visits", "mil_visits", "total_visits"),
+    c("counts_by_year", "frequencies_by_year", 
+      "govt_visits", "mil_visits", "total_visits"),
     ~ replace_na(.x, 0)
   )
 imp_final_data <- imp_final_data %>%
   mutate_at(
-    c("count", "freq", "govt_visits", "mil_visits", "total_visits"),
+    c("counts_by_year", "frequencies_by_year", 
+      "govt_visits", "mil_visits", "total_visits"),
     ~ replace_na(.x, 0)
   )
 

### 2022-08-02 02_clean_and_merge/06_merge_datasets.R
dropping invalid years

@@ -15,7 +15,7 @@ library(countrycode)
 aid_data <- 
   read_csv(
     paste0(getwd(), "/01_data/aid_data/clean_aid_data.csv")
-  )
+  ) %>% filter(year >= 2002)
 dip_data <-
   read_csv(
     paste0(getwd(), "/01_data/PublicDiplomacy/clean_diplomacy_data.csv")

### 2022-08-03 03_analysis/01_new_analysis.R
starting new analysis

@@ -1,0 +1,590 @@
+#########################
+# Updated analysis code #
+#########################
+
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls())
+library(tidyverse)
+library(censReg)
+library(AER)
+library(texreg)
+library(estimatr)
+library(mgcv)
+library(here)
+theme_set(theme_light())
+
+# data --------------------------------------------------------------------
+
+dt <- read_csv(
+  here('01_data/final_data/final_data_imputed.csv')
+)
+
+# descriptives ------------------------------------------------------------
+
+# summary stats
+stargazer::stargazer(
+  as.data.frame(dt),
+  type = 'text'
+)
+
+# aid and debt over time
+dt %>%
+  group_by(year) %>%
+  summarize(
+    Aid = sum(aid),
+    Debt = sum(debt)
+  ) %>%
+  pivot_longer(
+    Aid:Debt
+  ) %>%
+  mutate(
+    value = value / 1000000
+  ) %>%
+  ggplot() +
+  aes(
+    x = year,
+    y = value,
+    color = name
+  ) +
+  geom_line(
+    size = 0.75
+  ) +
+  scale_x_continuous(
+    n.breaks = 10
+  ) +
+  scale_y_continuous(
+    labels = scales::comma
+  ) +
+  scale_color_manual(
+    values = c(
+      'Aid' = 'royalblue',
+      'Debt' = 'indianred3'
+    )
+  ) +
+  labs(
+    x = NULL,
+    y = 'Yearly Total\n(millions $)',
+    color = NULL
+  ) +
+  theme(
+    legend.position = 'top'
+  )
+
+# coverage and visits by aid and debt
+dt %>%
+  group_by(year, aid > 0) %>%
+  summarize(
+    Coverage = sum(counts_by_year),
+    'Diplomatic Visits' = sum(govt_visits + mil_visits)
+  ) %>%
+  pivot_longer(
+    Coverage:`Diplomatic Visits`
+  ) %>%
+  ggplot() +
+  aes(
+    x = year,
+    y = value,
+    color = ifelse(`aid > 0`, 'Recipient', 'Non-recipient')
+  ) +
+  geom_line(
+    size = 0.75
+  ) +
+  scale_x_continuous(
+    n.breaks = 4
+  ) +
[…]

### 2022-08-03 03_analysis/01_new_analysis.R
some refinements

@@ -350,28 +350,14 @@ glmmTMB(
   ziformula = ~1,
   family = nbinom1
 ) -> znb_counts
-summary(znb_counts)
 glmmTMB(
   update(form, total_visits ~ . + as.factor(year) + (1 | recipient)),
   data = new_dt,
   ziformula = ~1,
   family = nbinom2
 ) -> znb_visits
+summary(znb_counts)
 summary(znb_visits)
-library(texreg)
-cmap <- list(
-  'Count model: typeAid' = 'Recipient',
-  'Count model: typeDebt' = 'Debtor',
-  'Count model: typeBoth' = 'Recipient-Debtor'
-)
-screenreg(
-  list(znb_counts, znb_visits),
-  custom.coef.map = cmap,
-  custom.model.names = c(
-    'Xinhua Coverage',
-    'Diplomatic Visits'
-  )
-)
 
 bind_rows(
   broom.mixed::tidy(
@@ -415,7 +401,8 @@ ggplot(fixed_effs) +
   labs(
     x = 'Coefficient with 95% CI',
     y = NULL,
-    color = 'Outcome'
+    color = 'Outcome',
+    caption = 'Mixed Effects Zero-inflated Negative Binomial Estimates'
   ) +
   geom_vline(
     xintercept = 0,
@@ -428,7 +415,10 @@ ggplot(fixed_effs) +
     )
   ) +
   theme(
-    legend.position = 'top'
+    legend.position = 'top',
+    plot.caption = element_text(
+      hjust = .5
+    )
   ) +
   guides(
     color = guide_legend(
@@ -456,35 +446,13 @@ pred_dt <- new_dt %>%
       mean
     )
   )
+
 tibble(
   None = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='None']))),
   Aid = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Aid']))),
   Debt = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Debt']))),
   Both = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Both'])))
 ) -> count_preds
-count_preds %>%
-  summarize(
-    across(
-      everything(),
-      mean
-    )
-  ) %>%
-  pivot_longer(
-    everything()
-  ) %>%
-  ggplot() +
-  aes(
[…]

### 2022-08-04 04_paper/Draft4.Rmd
more analysis and starting draft 4

--- 2022-06-10 04_paper/Draft3.Rmd
@@
 
+China's overseas development financing now surpasses that of the United States, the World Bank, and several other multilateral development and lending institutions combined.
+But despite the mamoth proportions of Beijing's aid (and increasingly debt) that it issues world wide, the motives behind its overseas activities remain a mystery.
 China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*.
@@
 
-However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals.
-These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility.
-@mattingly_when_2021 use experiments to demonstrate that investing in both foreign aids and public diplomacy efforts can improve its image abroad and reduce concerns about the threat it poses.
-Both foreign aids and public diplomacy are scarce resources for government to build bilateral relationships and improve its image abroad.
-It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and invest in bilateral relationships through aids, mediated public diplomacy and diplomatic visits.
-To our knowledge, none of the existing studies systematically examine which countries are “friends” to get more benefits of aids from the perspective of Beijing’s diplomacy efforts.
-We conceptualize two opposite modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open.
-So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
+The secrecy surrounding China's international development financing is puzzling.
+The painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
+Far from the rogue donor that many have feared, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors.
+Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
+These goals include international recognition and closer diplomatic ties with developing countries in what China calls "south-south" cooperation.
 
-We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionally larger China’s foreign aid.
-We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-Both dimensions are important to building its public diplomacy efforts.
-These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.
+However, these goals are difficult to accomplish in secret.
+This therefore raises a natural question.
+*How does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
 
-To test this expectation, we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
-Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy-seeking objectives on the world stage.
+We propose that despite the lack of formal reporting, Beijing can pursue recognition and diplomacy with its overseas financing with the help of other complementary foreign policy tools.
+Past research has shown that two specific instruments may play special roles in complementing these foreign policy objectives.
+First, international media are one way that countries can generate attention and promote a positive spin on their activities in foreign audiences.
+As Nye (2008) notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
+Perhaps in recognition of this, Beijing has expanded its outward facing state sponsored media activities and news reporting over the past two decades.
+This has been done in part through the English version of *Xinhua*, China's top state sponsored news agency.
 
-This work further helps in dispelling the notion that China purposely engages in development finance in secret.
-Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage.
-To our understanding, this is the first attempt to use media agenda-setting and public diplomacy decision to explain Chinese foreign aidS allocations.
-At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to aid-needed developing countries, are all crucial to achieving a state’s foreign policy goals and promoting its soft power.
+Second, aside from news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
+Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.
+These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.
 
-# Motivations behind Chinese Foreign Aid
+While public diplomacy and outward facing state sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes.
+In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance.
+Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* (to support China's image and to build publicity around its development activities) and be more frequent hosts of diplomatic missions from Beijing (to support closer bilateral cooperation).
 
-China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors.
-While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests.
-Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
-At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
-Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].
+As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to type.
+Until relatively recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
+However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD's official definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) has unmasked a considerable divergence in goals.
+The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreherEtAl2022.] Thus, as we test our hypotheses we also take care to distinguish between Beijing as donor from Beijing as lender.
 
-Two waves of surveys conducted by AidData of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.^[Reported by AidData ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) on March 22, 2018.
-Accessed March 3, 2022] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries.
-It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.
+The results from the analysis provide a novel perspective into the ways that China applies additional instruments to complement the goals it pursues via its overseas development financing.
+However, while the findings overall are consistent with our hypotheses, they do so in ways that also problematize the neat distinction between China's use of aid and its use of debt.
+In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's ODA recipients while no significant relationship exists between aid and diplomatic visits.
+Conversely, we find that debt is significantly linked to greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage.
+Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomacy with its debtors.
 
-If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing.
-Visual branding of aid has emerged as a growing concern among donors.
-The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.^[See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US.
-Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."^[["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012.
-Accessed March 3, 2022.]
-
-Given the diplomatic uses of foreign aid, the obscurity that surrounds Beijing's development finance is all the more puzzling.
-Unlike Western donors, China does not report its financing activities to an international organization or make its activities visible in an online database.
-To say transparency is out of character for Beijing is an understatement, but foreign aid is one issue area where transparency would arguably serve China's interests.
-So why the secrecy?
-
-As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret.
-But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.^[See @fuchsRudyak2019 for several related citations.] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing.
-Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA).
-However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.^[See this excellent summary entitled ["The Logic Behind China's Foreign Aid Agency"](https://carnegieendowment.org/2019/05/21/logic-behind-china-s-foreign-aid-agency-pub-79154) by the Carnegie Endowment for International Peace published May 21, 2019.
-Accessed March 10, 2022.]
-
-Absent transparency in reporting, there are other tools at Beijing's disposal that may complement the diplomatic objectives behind its foreign aid.
-In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives.
-We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences).
-We summarize these factors in greater detail in the following sections.
-
-# Media
-
-## First-level Agenda-setting and Selective Media Attention
-
-Agenda-setting refers to the ability of media to signal to the public what is important.
-Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public.
-That is, the public learns the importance of objects based on the amount of coverage that those objects receive.
-Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972).
-More specifically, as @berelson_mass_1966 observe, “The mass media force attention to certain issues.
-They build up public images of political figures.
-They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about” (p.
-468).
-Since their seminal work, hundreds of studies have examined the agenda-setting effect on the public.
-The vast majority support this agenda-setting notion (need some more extension or citations here).
-
-Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963’s famous notation that the media is “stunningly successful in telling its readers what to think *about*” (p.
-13; emphasis added).
-That is, the salience of news media reports transfers to the perception of issue salience to the public (@mccombs_agenda-setting_1972).
-Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals’ perceptions of the relative importance and salience of the issues.
-
-To extend this logic, media salience indicates significance for foreign countries named in the media.
-@wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S..
-The countries' media coverage will lead to the countries becoming more salient among the public.
-
-With the implication of the media salience in mind, news editor is a source of gatekeeping power for those who can tell us where to focus our attention.
-From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air.
-News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.
-
-Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover.
-Not all countries in the world receive equal coverage.
-In fact, only a small portion of international events can get through the media gatekeepers and get media coverage.
-While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered.
-@golan_international_2003-1’s study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
-network television newscasts (ABC, CBS, NBC and CNN).
-They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa.
-A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (@sheafer_relative_2014-1).
-Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.
-
-## Xinhua’s Effforts to Set Agenda
-
-In addition to swaying people's attention, media agenda-setting is also critical in building states' image to international audiences.
-@nye_public_2008-2 suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications, with an aim to improve the country's "soft power".
-Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press.
-China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.
-
-Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others (@entman_theorizing_2008; @kiousis_international_2008).
-Compared to the first-level agenda-setting, this mechanism entails a more profound media influence on shaping public attitudes in the public’s perceptions.
-Since news media have a significant impact on shaping the public's perceptions, investing in international news markets to improve one's image to foreign audiences is the core objective of mediated public diplomacy.
-
-As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency.
-It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy (@shambaugh_chinas_2015-1).
-It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires.
-The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea.
-It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format.
-Governments use media to tell their story to the world and improve their public relations with other countries.
-As such, scholars often focus on China's mediated public diplomacy efforts through *Xinhua*.
-That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009).
-
-Despite growing in the global media landscape, *Xinhua*, as an international broadcaster, needs foreign audiences.
-Simply providing more information will not improve their image in the Western world.
-Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack.
-As @druckman_limits_2001 presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
-On the other hand, *Xinhua* needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.
-
-Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit the information as a credible news outlet.
-It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
-Taking into account the limited space of *Xinhua* to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.
-
-# Public Diplomacy
-
-Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country.
-For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people – and listen to them" (@hoffman_introduction_1968, p.
-4).
-In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" (@deibel_culture_1976, p.
-15).
-
-An image that fits into a traditional mental image of public diplomacy is "diplomats engaged in traditional negotiations under the glare of publicity" (@deibel_culture_1976, p.
-13).
-In addition to negotiations behind closed doors, records of visits have symbolic evidence to show the bilateral relationships between countries.
-The elite-level diplomacy, government-to-government diplomatic visit, is the focus in this section.
-Government-to-government visits are important as leaders' resources are scarce.
-They often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships (@nitsch_state_2005).
-Leader visits also have implications on the host leaders' security in office (@malis_state_2021) and the states' security issues (@mcmanus_making_2018).
-In all, diplomatic visits send important an important positive signal that the visiting and hosting countries support each other and have closer relationships.
-
-Visiting leaders can increase the awareness of themselves and their country among citizens in the host country.
-@goldsmith_spinning_2009 find that the impact of high-level government visits on foreign publics' opinions is contextual.
-U.S.
-visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq.
-Again, the credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy.
-The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect.
-The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries (@goldsmith_does_2021).
-In most cases, the host leader has the leverage to provide news frames for the journalists to report the government-to-government visit positively.
-
-In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.
-From the perspective of communication, diplomatic visits signal the countries' support and proximity.
-The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.
-
-# Hypotheses
-
-We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion.
-News editors build the credibility of the news agency to transmit information around the globe.
-High-level officials spend time and resources to visit other countries for economic or security purposes to strengthen their bilateral relationship.
-Since both approaches involve limited time and resources, we expect that Beijing will choose on whom to cast the spotlight, and whom to visit, strategically.
-In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing.
-They are in the potential friend circle.
-While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic.
-Foreign aid, instead, provides tangible and material support to countries in need.
-Hence, we expect China to prioritize giving foreign aid to its “friends”---countries where China has developed strong relationships through public diplomacy efforts.
-This rationale leads to our hypotheses:
-
-> *H1: When developing countries receive more media exposure in *Xinhua*, they are more likely to receive more foreign aid from China.*
-
-> *H2: When developing countries host or visit Chinese high-level diplomatic visits more frequently, they are more likely to receive more foreign aid from China.*
-
-# Data and Methods
-
-To assess complementarities between China's bilateral diplomatic visits and **Xinhua** coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources.
-We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition **Xinhua** news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-The full dataset consists of unique recipient-year observations from 2000 to 2014.
-
-To normalize bilateral aid data, counts of country mentions, and the number of diplomatic visits, we apply the inverse hyperbolic sine transformation (ihs).
-We opt for this rather than the natural log because ihs is defined at zero (there are many zero observations for each of these variables) but is close enough in form to the natural log that estimates may still be interpreted as eslasticities or percent changes.
-
-We include several controls in analysis to adjust for sources of confounding and also to improve the precision of our estimates. Prior research points to a number of covariates that are relevant.
-
-The first set of controls consist of aid recipient characteristics.
-From the Penn World Table (version 9.1), we use real gross domestic product (GDP) in millions of 2011 USD.
-This serves as a proxy for the size of a recipient's economy.
-From the Penn World Table we also use population in millions and the number of people employed in millions.
-We normalize values using ihs to keep the transformation of the data consistent with that of the response.
-From the Institute for Health Metrics and Evaluation we use a yearly count of the number of individuals killed by natural disasters, and we again apply the ihs transformation.
-From PRIO/UCDP we use a binary measure of the presence of civil war, coded as 1 for each year where there is armed violence between two or more parties where one of the parties is the government and at least 25 battle-related deaths occur.
-To capture political and civil liberties we use Freedom House and adjust values so that higher values denote greater levels of freedom.
-We use this measure instead of Polity to avoid collinearities with civil war.
-
-We further control for bilateral characteristics between China and aid recipients.
-To account for economic ties we use total bilateral trade (imports plus exports) in millions of dollars.
-From ATOP we use a binary measure of alliances between recipients and China.
-This measure is coded as 1 if there is at least one of either a formal offensive, defensive, non-aggression, or neutrality agreement.
-Finally, form CEPII we use a measure of bilateral distance in kilometers between recipients and China.
-Both trade and distance are transformed using ihs.
-
-For our empirical strategy, we estimate models of the form
-$$\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}. \tag{1}$$
-In the above, subscript $r$ indexes the aid recipient and $t$ the year.
-The vector of parameters $\tau_t$ denotes fixed year intercepts, the vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.
-
-We estimate the parameters of equation 1 using a variety of techniques to ensure the robustness of our estimates.
-First, because coverage and diplomatic visits may be endogenous to aid, we lag each by one year (along with all time-varying covariates).
-We then estimate the model via OLS and report robust standard errors clustered by recipient.
-
-However, because there are a significant number of zero observations in the outcome, OLS may yield downward biased estimates of the parameters of interest.
-We thus additionally estimate equation 1 using the Tobit maximum likelihood estimator.
-To account for unobserved heterogeneity between, and dependence within, recipients we include random recipient intercepts in the model.
-
-In the event that the process that determines whether countries receive aid from China differs from the process that determines the amount of aid given, we further separate the estimation into selection and level equations as outlined by @cragg1971.
-The selection equation is estimated using mixed effects logit with random recipient intercepts and the level equation is estimated using OLS with cluster-robust standard errors.
-
-Finally, because within-year coverage and visits may have greatest relevance for predicting the response, using the lag of each variable in model estimation may under-estimate the complementarities between coverage and visits with aid.
-However, estimating the models using same-year coverage and visits poses a challenge due to likely endogeneity between them and the response.
-Unable to find a satisfactory set of instruments, we take two different approaches.
-For one, we leverage the variation in the one year lag of each predictor to instrument for in-year values of each.
-This approach has been applied elsewhere in the literature when dealing with time-series data [see @braumoeller2008].
-For the second approach, we use the internal instruments approach outlined by @lewbel2012, which leverages heteroskedasticity in the data to synthesize instrumental variables.
-
-We present results from each of these approaches in the following analysis.
-
-# Results
-
-```{r}
-library(tidyverse)
-library(kableExtra)
-dt <- read_csv(
-  paste0(str_remove(getwd(), "/04_paper"), 
-         "/01_data/final_data/final_data_imputed.csv")
-)
-```
-
-Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014.
-Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.^[For multiple imputation we used the `missRanger` R package.
-See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.] Summary statistics are shown the Appendix.
-
-```{r, include=FALSE}
-load(
-  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
-)
-reg.tab1 <- reg.tab
-cat(reg.tab1)
-```
-
-\begin{table}
-\caption{Model Estimates}
-\begin{center}
-\begin{tabular}{l c c c c c c}
-\hline
- & OLS & ML Tobit & Selection & Level & IV Lag & IV Lewbel \\
-\hline
-Coverage (lag)              & $0.63^{*}$      & $1.29^{**}$    & $0.18^{***}$  & $0.11$          &                 &                 \\
-                            & $(0.28)$        & $(0.43)$       & $(0.05)$      & $(0.14)$        &                 &                 \\
-Coverage (in-year)          &                 &                &               &                 & $0.67^{*}$      & $0.51^{\cdot}$  \\
-                            &                 &                &               &                 & $(0.31)$        & $(0.29)$        \\
-Diplomatic Visits (lag)     & $0.93^{**}$     & $1.54^{\cdot}$ & $0.21^{**}$   & $0.36^{*}$      &                 &                 \\
-                            & $(0.34)$        & $(0.83)$       & $(0.07)$      & $(0.15)$        &                 &                 \\
-Diplomatic Visits (in-year) &                 &                &               &                 & $1.08^{**}$     & $1.38^{**}$     \\
-                            &                 &                &               &                 & $(0.41)$        & $(0.45)$        \\
-Freedom House               & $-0.36$         & $-0.58$        & $-0.08^{*}$   & $-0.20^{*}$     & $-0.36$         & $-0.39$         \\
-                            & $(0.28)$        & $(0.40)$       & $(0.04)$      & $(0.09)$        & $(0.28)$        & $(0.29)$        \\
-GDP                         & $-2.71^{***}$   & $-4.83^{***}$  & $-0.77^{***}$ & $0.01$          & $-2.73^{***}$   & $-2.68^{***}$   \\
-                            & $(0.36)$        & $(0.48)$       & $(0.06)$      & $(0.17)$        & $(0.36)$        & $(0.34)$        \\
-Population                  & $2.52^{***}$    & $5.26^{***}$   & $0.69^{***}$  & $0.27$          & $2.51^{***}$    & $2.56^{***}$    \\
-                            & $(0.35)$        & $(0.76)$       & $(0.06)$      & $(0.17)$        & $(0.35)$        & $(0.36)$        \\
-Unemployment                & $0.18$          & $0.84$         & $0.13$        & $-0.05$         & $0.19$          & $0.20$          \\
-                            & $(0.47)$        & $(0.95)$       & $(0.08)$      & $(0.19)$        & $(0.47)$        & $(0.47)$        \\
-Disaster Deaths             & $0.18$          & $0.14$         & $0.04$        & $0.02$          & $0.18$          & $0.17$          \\
-                            & $(0.17)$        & $(0.27)$       & $(0.03)$      & $(0.05)$        & $(0.17)$        & $(0.16)$        \\
-Civil War                   & $-1.62^{\cdot}$ & $-2.77^{*}$    & $-0.38^{*}$   & $-0.75^{\cdot}$ & $-1.62^{\cdot}$ & $-1.57^{\cdot}$ \\
-                            & $(0.91)$        & $(1.25)$       & $(0.15)$      & $(0.39)$        & $(0.92)$        & $(0.91)$        \\
-Trade                       & $0.14$          & $-0.18$        & $0.04$        & $0.03$          & $0.14$          & $0.14$          \\
-                            & $(0.15)$        & $(0.18)$       & $(0.03)$      & $(0.05)$        & $(0.15)$        & $(0.15)$        \\
-Alliance                    & $0.36$          & $2.00$         & $0.29$        & $-0.64$         & $0.07$          & $-0.32$         \\
-                            & $(0.94)$        & $(2.75)$       & $(0.22)$      & $(0.47)$        & $(0.94)$        & $(1.00)$        \\
-Distance                    & $1.84^{*}$      & $4.12^{\cdot}$ & $0.49^{***}$  & $0.55$          & $1.94^{*}$      & $2.21^{*}$      \\
-                            & $(0.83)$        & $(2.34)$       & $(0.15)$      & $(0.37)$        & $(0.87)$        & $(0.87)$        \\
-\hline
-Adj. R$^2$                  & $0.19$          &              &             & $0.11$          & $0.20$          & $0.20$          \\
-Num. obs.                   & $1932$          & $1932$         & $1932$        & $982$           & $1932$          & $1932$          \\
-Deviance explained          &               &              & $0.15$        &               &               &               \\
-\hline
-\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$; $^{\cdot}p<0.1$}}
-\end{tabular}
-\label{table:coefficients}
-\end{center}
-\end{table}
-
-Table 1 reports the regression coefficients for equation 1 using each of the estimation techniques outlined in the previous section.
-Estimates for the controls comport with prior research, save that the coefficients for democracy using the Freedom House measure reach conventional levels of statistical significance in the selection and level estimates.
-Contra @dreherEtAl2018, these estimates suggest China disproportionately targets its development finance to authoritarian regimes.
-While this result is not statistically significant for the alternative estimators, the coefficient remains consistently negative across all estimation techniques.
-
-Consistent with other studies, China prioritizes recipients with smaller economies and larger populations.
-Depending on the estimation strategy, greater distance is related to *more* aid, which is a finding that runs contrary to patterns observed for DAC donors.
-This result likely is driven by China's prioritization of aid giving in Sub-Saharan Africa.
-Finally, China seems to have a bias against giving aid in the context of ongoing conflict.
-Across estimation strategies, the coefficient on civil war is negative and marginally significant ($p < 0.1$) in four of the models and statistically significant ($p < 0.05$) in two.
-
-China does not appear to discriminate on the basis of other measures of need, such as unemployment and natural disaster deaths.
-Further, trade and alliances, measures of material and strategic importance to Beijing, show no significant relationship with aid.
-
-Turning to the estimates of interest, across specifications the coefficients on media coverage in *Xinhua* and the number of diplomatic visits run in the expected direction.
-Expressed as elasticities, the range of estimates suggest that one percent greater yearly instances of coverage in one recipient relative to another are associated with more than half a percent to over one percent greater aid received by that aid recipient.
-Further, one percent greater diplomatic visits is related to almost one percent to one and a half percent greater aid to that recipient relative to another.
-This finding is consistent with the view that China's development finance has public diplomacy and international legitimacy functions.
-
-# Conclusion
-
-Does Beijing intentionally keep its development finance a secret [@fuchsRudyak2019]? Or, does it use foreign aid as a public tool of diplomacy and to promote its legitimacy abroad?
-
-In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
-Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.
-
-Much work, of course, remains to further interrogate the links between China's development finance and its strategic and diplomatic objectives.
-This study provides but a glimpse into the complementarities between Beijing's foreign aid and its public diplomacy.
-Even so, it contributes to our understanding of the strategic determinants of China's aid, which even now contains mysteries we have yet to resolve.
-
-\clearpage
-
-# Appendix
-
-Table A.1 shows summary statistics for the data sample used in the main analysis.
-
-\clearpage
-
-\captionsetup{labelformat=AppendixTables}
-\setcounter{table}{0}
-
-```{r}
-dt %>%
-  mutate(
-    aid = aid / 1000000,
-    count = count / 1000,
-    trade = trade / 1000000000,
-    gdp = gdp / 1000000,
-    pop = pop / 1000000
-  ) %>%
-  summarize(
-    across(
-      c(aid, count, govt_visits, pmm_fh, gdp:unemp, disaster:dist, trade, atopally),
-      list(Mean = mean, Median = median, SD = sd, Min. = min, Max. = max),
-      na.rm=T
-    ) 
-  ) %>%
-  pivot_longer(cols = everything()) %>%
-  separate(
-    col = name,
-    into = c(" ", "stat"),
-    sep = "_(?=[^_]+$)"
-  ) %>%
-  mutate(
-    value = scales::comma(round(value, 2))
-  ) %>%
-  pivot_wider(
-    values_from = value,
-    names_from = stat
-  ) %>%
-  mutate(
-    " " = c(
-      "Aid (millions)",
-      "Article Mentions (thousands)",
-      "Government Visits",
-      "Freedom House",
-      "GDP (in 100 millions)",
-      "Population (in millions)",
-      "Unemployment Rate",
-      "Disaster Deaths",
-      "Civil War",
-      "Distance (in kilometers)",
-      "Trade (in millions)",
-      "Allies"
-    )
-  ) %>%
-  kbl(
-    caption = "Summary Statistics (2000-2014)",
-    booktabs = T,
-    linesep = ""
-  )
-```
-
-```{r, results='asis'}
-tabs <- c(
-  "ols_region_tab1.R",
-  "ivlag_region_tab1.R"
-)
-load(
-  paste0(stringr::str_remove(getwd(), "/04_paper"), 
-         "/03_analysis/",tabs[1])
-)
-load(
-  paste0(stringr::str_remove(getwd(), "/04_paper"),
-         "/03_analysis/",tabs[2])
-)
-#cat(ols.region)
-#cat(ivlag.region)
-```
+The reason why these diverging patterns exist between China's aid and debt related activities poses a new puzzle for future research.
+It further reveals that China's supposed "split personality" when it comes to aid and debt may be more a matter of degree than of absolutes.
 
@@
 # References
-In the above, subscript $r$ indexes the aid recipient and $t$ the year. The vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.
-
-We estimate the parameters of equation 1 using a variety of techniques to ensure the robustness of our estimates.
-First, because coverage and diplomatic visits may be endogenous to aid, we lag each by one year (along with all time-varying covariates).
-We then estimate the model via OLS and report robust standard errors clustered by recipient.
-
-However, because there are a significant number of zero observations in the outcome, OLS may yield downward biased estimates of the parameters of interest.
-We thus additionally estimate equation 1 using the Tobit maximum likelihood estimator.
-To account for unobserved heterogeneity between, and dependence within, recipients we include random recipient intercepts in the model.
-
-In the event that the process that determines whether countries receive aid from China differs from the process that determines the amount of aid given, we further separate the estimation into selection and level equations as outlined by Cragg (year?).
-The selection equation is estimated using mixed effects logit with random recipient intercepts and the level equation is estimated using OLS with cluster-robust standard errors.
-
-Finally, because within-year coverage and visits may have greatest relevance for predicting the response, using the lag of each variable in model estimation may under-estimate the complementarities between coverage and visits with aid.
-However, estimating the models using same-year coverage and visits poses a challenge due to likely endogeneity between them and the response.
-Unable to find a satisfactory set of instruments
-
-# Results
-
-```{r, results='asis', eval=F}
-load(
-  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
-)
-reg.tab1 <- reg.tab
-cat(reg.tab1)
-```
-
-# Conclusion
-
-\clearpage
-
-# References

### 2022-08-04 03_analysis/01_new_analysis.R

@@ -325,62 +325,83 @@ dt %>%
     )
   ) -> new_dt
 
-form <- ~ type + income + pop + disaster + civilwar +
+type_form <- ~ type + income + pop + disaster + civilwar +
   dist + v2x_api + imports + exports + distance + fdi
-lm_robust(
-  update(form, asinh(counts_by_year) ~ .),
-  data = new_dt,
-  clusters = recipient,
-  se_type = 'stata',
-  fixed_effects = ~ year
-) -> ols_counts
-lm_robust(
-  update(form, total_visits ~ .),
-  data = new_dt,
-  clusters = recipient,
-  se_type = 'stata',
-  fixed_effects = ~ year
-) -> ols_visits
-
+cont_form <- update(type_form, ~ . - type + asinh(aid) + asinh(debt))
 
 library(glmmTMB)
 glmmTMB(
-  update(form, counts_by_year ~ . + as.factor(year) + (1 | recipient)),
+  update(type_form, counts_by_year ~ . + as.factor(year) + (1 | recipient)),
   data = new_dt,
   ziformula = ~1,
   family = nbinom1
-) -> znb_counts
+) -> znb_counts_type
 glmmTMB(
-  update(form, total_visits ~ . + as.factor(year) + (1 | recipient)),
+  update(type_form, total_visits ~ . + as.factor(year) + (1 | recipient)),
   data = new_dt,
   ziformula = ~1,
   family = nbinom2
-) -> znb_visits
-summary(znb_counts)
-summary(znb_visits)
+) -> znb_visits_type
+glmmTMB(
+  update(cont_form, counts_by_year ~ . + as.factor(year) + (1 | recipient)),
+  data = new_dt,
+  ziformula = ~1,
+  family = nbinom1
+) -> znb_counts_cont
+glmmTMB(
+  update(cont_form, total_visits ~ . + as.factor(year) + (1 | recipient)),
+  data = new_dt,
+  ziformula = ~1,
+  family = nbinom2
+) -> znb_visits_cont
+summary(znb_counts_type)
+summary(znb_visits_type)
+summary(znb_counts_cont)
+summary(znb_visits_cont)
 
 bind_rows(
   broom.mixed::tidy(
-    znb_counts
+    znb_counts_type
   ),
   broom.mixed::tidy(
-    znb_visits
+    znb_visits_type
+  ),
+  broom.mixed::tidy(
+    znb_counts_cont
+  ),
+  broom.mixed::tidy(
[…]

### 2022-08-05 03_analysis/01_new_analysis.R
latest analysis

@@ -452,38 +452,26 @@ ggplot(fixed_effs) +
     )
   )
 
-pred_dt <- new_dt %>%
-  filter(year == 2014) %>%
-  group_by(type, year) %>%
-  summarize(
-    across(
-      c(income, pop, disaster, civilwar, dist, v2x_api,
-        exports, imports, distance, fdi),
-      mean
-    ),
-    recipient = recipient[200]
-  ) %>%
-  ungroup %>%
-  mutate(
-    across(
-      c(income, pop, disaster, civilwar, dist, v2x_api,
-        exports, imports, distance, fdi),
-      mean
-    )
-  )
-
 tibble(
-  None = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='None']))),
-  Aid = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Aid']))),
-  Debt = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Debt']))),
-  Both = predict(znb_counts, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Both'])))
+  None = predict(znb_counts_type, type = 'response', 
+                 newdata = new_dt %>% mutate(type = unique(type[type=='None']))),
+  Aid = predict(znb_counts_type, type = 'response', 
+                newdata = new_dt %>% mutate(type = unique(type[type=='Aid']))),
+  Debt = predict(znb_counts_type, type = 'response', 
+                 newdata = new_dt %>% mutate(type = unique(type[type=='Debt']))),
+  Both = predict(znb_counts_type, type = 'response', 
+                 newdata = new_dt %>% mutate(type = unique(type[type=='Both'])))
 ) -> count_preds
 
 tibble(
-  None = predict(znb_visits, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='None']))),
-  Aid = predict(znb_visits, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Aid']))),
-  Debt = predict(znb_visits, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Debt']))),
-  Both = predict(znb_visits, type = 'response', newdata = new_dt %>% mutate(type = unique(type[type=='Both'])))
+  None = predict(znb_visits_type, type = 'response', 
+                 newdata = new_dt %>% mutate(type = unique(type[type=='None']))),
[…]

### 2022-08-05 04_paper/Draft4.Rmd
some minor edits to intro

@@
 China's overseas development financing now surpasses that of the United States, the World Bank, and several other multilateral development and lending institutions combined.
-But despite the mamoth proportions of Beijing's aid (and increasingly debt) that it issues world wide, the motives behind its overseas activities remain a mystery.
+But despite the mammoth proportions of Beijing's aid (and increasingly debt) that it issues world wide, the motives behind its overseas activities remain a mystery.
 China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*.
-@fuchsRudyak2019 cite this fact as a reason Western governments assume Beijing deliberately keeps its international development finance a secret.
+For this reason, many Western governments assume Beijing deliberately keeps its international development finance a secret[@fuchsRudyak2019].
 
@@
 
-We propose that despite the lack of formal reporting, Beijing can pursue recognition and diplomacy with its overseas financing with the help of other complementary foreign policy tools.
+We propose that despite the lack of formal reporting, Beijing can pursue recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
 Past research has shown that two specific instruments may play special roles in complementing these foreign policy objectives.
@@
 Until relatively recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
-However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD's official definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) has unmasked a considerable divergence in goals.
-The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreherEtAl2022.] Thus, as we test our hypotheses we also take care to distinguish between Beijing as donor from Beijing as lender.
+However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) has unmasked a considerable divergence in goals.
+The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreherEtAl2022.] Thus, as we test our hypotheses we also distinguish between Beijing-as-donor from Beijing-as-lender.
 

### 2022-08-09 03_analysis/Analysis_description.Rmd
Add files via upload

---
title: "Descriptive analysis 2"
author: "Lucie Lu"
date: "2022-08-05"
output: pdf_document
---

```{r}

rm(list = ls())
library(tidyverse)
library(dplyr)
#install.packages("censReg")
#library(censReg)
#library(AER)
#library(texreg)
library(estimatr)
library(mgcv)
library(here)
#install.packages("OneR")
library(OneR)
theme_set(theme_light())

```

```{r, eval=F}

dt <- read_csv(
  "https://raw.githubusercontent.com/milesdwilliams15/chinese_media_and_foreign_aid/main/01_data/final_data/final_data_imputed.csv"
)

```

## Which countries recevie the most aids on average?
```{r}
library("dplyr")
# aid only
filter(new_dt, type == "Aid")

aid_average <- new_dt %>% group_by(recipient) %>% summarise_at(vars(aid), list(mean_of_aid = mean))
od_aid_average <- aid_average[order(aid_average$mean_of_aid, decreasing = T), ]

od_aid_average$rank_aid <- rank(-od_aid_average$mean_of_aid, ties.method = "max")
od_aid_average
```
Iraq gets the most aids (aids from humanitarian aids)

## Which countries receive the most aids and debts?

```{r}

debt_average <- new_dt %>% group_by(recipient) %>% summarise_at(vars(debt), list(mean_of_debt = mean))

od_debt_average <- debt_average[order(debt_average$mean_of_debt, decreasing = T), ]

od_debt_average$rank_debt <- rank(-od_debt_average$mean_of_debt, ties.method = "max")
od_debt_average
```
```{r}
top_20_recipients <- cbind((od_debt_average %>% filter(rank_debt <= 20))[,1], 
      (od_aid_average %>% filter(rank_aid <= 20))[,1]) 
colnames(top_20_recipients) <- c("debt_top20", "aid_top20")
top_20_recipients

overlap0 <- calculate.overlap( x = list("debt" = top_20_recipients$debt_top20, 
                                        "aids" = top_20_recipients$aid_top20))
overlap0$a3
```

## Interesting patterns
Top 20 debt and aids countries are shown above. 8 countries have overlaps: Indonesia, Pakistan, Laos, Ethiopia, Cambodia, Sri Lanka, Kenya,Sudan are listed both.

```{r}
od_debt_average %>% filter(rank_debt == 142) #no debts
od_aid_average %>% filter(rank_aid == 142) #no aids

c_no_debt <- (od_debt_average %>% filter(rank_debt == 142))$recipient
c_no_aid <- (od_aid_average %>% filter(rank_aid == 142))$recipient

```

```{r}
#install.packages("VennDiagram")
library(VennDiagram)
overlap <- calculate.overlap( x = list( "aids" = top_20_recipients$aid_top20, 
                                        "debt" = c_no_debt))
overlap
```

Russia has most debts, but no aids; Iraq has most aids, but no debts at all.

## Which countries receive the most aid and debt? And their proportions?
```{r}

# calculate sum of aid and debt for each row
for (i in 1:nrow(new_dt)) {
   new_dt$aids_plus_debts[i] <- new_dt$aid[i] + new_dt$debt[i]
}

aid_debt_both <- new_dt %>% group_by(recipient) %>% 
  summarise_at(vars(aids_plus_debts), list(mean_of_both = mean))

##########

# combine aid average and aid debt both data
aid_prop <- merge(aid_average, aid_debt_both, by = "recipient")
aid_prop$mean_aid_prop <- round(aid_prop$mean_of_aid/aid_prop$mean_of_both, digits=2)

# combine debt average and aid debt both data

debt_prop <- merge(debt_average, aid_debt_both, by = "recipient")
debt_prop$mean_debt_prop <- round(debt_prop$mean_of_debt/debt_prop$mean_of_both, digits=2)

```

```{r informative combination of aid and debt data}
## merge with ordered aid debt both average data

m1 <- merge(aid_debt_both, aid_prop,  by = "recipient")
m2 <- merge(m1, debt_prop, by = "recipient")
m2 <- m2[,-c(2,4)]

m2 <- m2[order(m2$mean_of_both, decreasing = T), ]
m2$rank_both <- rank(-m2$mean_of_both, ties.method = "max")
m2

```

The proportion of debts is much higher than the aids for the top recipients.

## Which countries receive nothing?

```{r}
# 8 countries never receive anything
filter(m2, rank_both == 142)
```

8 countries never receive anything from China: Curacao, Dominican Republic, El Salvador, French Polynesia, Guam, Nicaragua, Panama and Praguay.

```{r combine media and diplomatic visits}
m2_figure <- m2

m3 <- cbind(new_dt %>% group_by(recipient) %>% summarise_at(vars(counts_by_year), list(coverage = mean)),
  new_dt %>% group_by(recipient) %>% summarise_at(vars(total_visits), list(diplomatic_visits = mean)))

m3 <- m3[,-3]

m2_figure <- merge(m2_figure, m3, by = 'recipient')

m2_figure <- m2_figure[order(m2_figure$coverage, decreasing = T), ]
m2_figure$rank_coverage <- rank(-m2_figure$coverage, ties.method = "max")
m2_figure
```

```{r}
top_20_coverage <- (m2_figure %>% filter(rank_coverage <= 20))[,1]
top_20_recipients$coverage_top20 <-  top_20_coverage
top_20_recipients
```

```{r overlaps}

overlap2 <- calculate.overlap( x = list( "aids" = top_20_recipients$aid_top20, 
                                        "coverage" = top_20_recipients$coverage_top20))
overlap2$a3

overlap3 <- calculate.overlap( x = list( "aids" = top_20_recipients$debt_top20, 
                                        "coverage" = top_20_recipients$coverage_top20))
overlap3$a3

```
- Countries that show up on the top 20 aid-recipients and Xinhua coverage are: Iraq, Indonesia, Pakistan, Cambodia, Kenya and Zambia.

- Countries that show up on the top 20 debt-recipients and Xinhua coverage are: Russia, Brazil, Indonesia, Pakistan, Vietnam, Malaysia, Iran, Cambodia, Kenya.

```{r}

lm1 <- lm(mean_of_debt ~ Coverage, data=m2_figure)
summary(lm1)
```

### 2022-08-12 04_paper/Draft4_812.Rmd
Add files via upload

--- 2022-08-05 04_paper/Draft4.Rmd
@@
 fontsize: 12pt
-bibliography: ref_Xinhua.bib
+#bibliography: ref_Xinhua.bib
 link-citations: yes
@@
 
-abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
+Abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
 We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
@@
 China's overseas development financing now surpasses that of the United States, the World Bank, and several other multilateral development and lending institutions combined.
-But despite the mammoth proportions of Beijing's aid (and increasingly debt) that it issues world wide, the motives behind its overseas activities remain a mystery.
+But despite the mammoth proportions of Beijing's aid (and increasingly debt) that it issues worldwide, the motives behind its overseas activities remain a mystery.
 China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*.
@@
 
+Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and behaving in global terms **[@nathan&scobell2012]**.
+Similarly, in terms of where China’s money goes and its economic influence concentrates, some countries are more important than others.
+However, no clear hierarchy or conclusive evidence has been drawn so far.
 The secrecy surrounding China's international development financing is puzzling.
 The painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
-Far from the rogue donor that many have feared, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors.
+**They find** that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors **(citation needed)**.
 Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
-These goals include international recognition and closer diplomatic ties with developing countries in what China calls "south-south" cooperation.
+These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.
 
 However, these goals are difficult to accomplish in secret.
-This therefore raises a natural question.
-*How does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*
+This, therefore, raises a natural question.
+*Do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts?
+If so, how?*
 
-We propose that despite the lack of formal reporting, Beijing can pursue recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
+We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
 Past research has shown that two specific instruments may play special roles in complementing these foreign policy objectives.
-First, international media are one way that countries can generate attention and promote a positive spin on their activities in foreign audiences.
-As Nye (2008) notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
-Perhaps in recognition of this, Beijing has expanded its outward facing state sponsored media activities and news reporting over the past two decades.
-This has been done in part through the English version of *Xinhua*, China's top state sponsored news agency.
+First, media presence is one way that countries can generate attention and promote a positive spin on their activities to foreign audiences.
+As Nye (2008) notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power **(citation needed)**.
+Perhaps in recognition of this, Beijing has expanded its outward-facing state-sponsored media activities and news reporting over the past two decades.
+This has been done in part through the English version of *Xinhua*, China's top state-sponsored news agency.
 
-Second, aside from news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
+Second, aside from expanding news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
 Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.
@@
 
-While public diplomacy and outward facing state sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes.
+While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes.
 In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance.
@@
 
-As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to type.
-Until relatively recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
-However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) has unmasked a considerable divergence in goals.
-The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreherEtAl2022.] Thus, as we test our hypotheses we also distinguish between Beijing-as-donor from Beijing-as-lender.
+As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to types of assistance China offers.
+Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
+However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals.
+The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreherEtAl2022.] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.
 
-The results from the analysis provide a novel perspective into the ways that China applies additional instruments to complement the goals it pursues via its overseas development financing.
+The results from the analysis provide a novel perspective on the ways that China applies additional instruments to complement the goals it pursues via its overseas development financing.
 However, while the findings overall are consistent with our hypotheses, they do so in ways that also problematize the neat distinction between China's use of aid and its use of debt.
-In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's ODA recipients while no significant relationship exists between aid and diplomatic visits.
-Conversely, we find that debt is significantly linked to greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage.
+In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's ODA recipients, while no significant relationship exists between aid and diplomatic visits.
+Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage.
 Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomacy with its debtors.
 
-The reason why these diverging patterns exist between China's aid and debt related activities poses a new puzzle for future research.
-It further reveals that China's supposed "split personality" when it comes to aid and debt may be more a matter of degree than of absolutes.
+Aid recipient countries disproportionately get more media attention from *Xinhua* to report their economy and needs for development projects and aid.
+Notably, *Xinhua* does not just promote China’s efforts to offer aid to those countries in need but also gives a rounded picture of those countries’ economic conditions that justify their bases of needs.
+Another implication of our finding is that Beijing is more likely to lend money to its “friends”: countries with more cordial diplomatic relations tend to have closer political interests and ties.
+While the previous study highlights that lending indicates Beijing’s economic interests, our finding suggests that lending is more closely related to its political interests.
+For instance, Russia, one of China’s closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017.
+In contrast, Iraq shows the opposite pattern: it receives the highest amount of aid from China during the period of our investigation, but it does not receive any loans.
 

### 2022-08-12 03_analysis/Analysis_description.Rmd
Add files via upload

@@
 
+# and load Miles' file: new_dt
+```
+
+```{r}
+unique(new_dt$recipient)
+#142
 ```
@@
 ```
-Iraq gets the most aids (aids from humanitarian aids)
+Iraq gets the most aids (aids from humanitarian aids), with a surge in 2010 and 2014.
 
@@
 
-Russia has most debts, but no aids; Iraq has most aids, but no debts at all.
+Russia has most debts, but no aids; Iraq has most aids, but no debts at all. (China-Iraq: https://www.mei.edu/publications/china-iraq-relations-poised-quantum-leap#_ftn39)
 

### 2022-09-05 04_paper/Draft4.Rmd
saving

@@
 China's overseas development financing now surpasses that of the United States, the World Bank, and several other multilateral development and lending institutions combined.
-But despite the mammoth proportions of Beijing's aid (and increasingly debt) that it issues world wide, the motives behind its overseas activities remain a mystery.
+As the reach and scope of its development activities has grown to mammoth proportions, the motives behind its overseas activities remain hotly contested, and the limited transparency surrounding Beijing's overseas financing only adds fuel to controversy.
 China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*.
-For this reason, many Western governments assume Beijing deliberately keeps its international development finance a secret[@fuchsRudyak2019].
+For this reason, many Western governments assume Beijing deliberately tries to keep its international development finance a secret [@fuchsRudyak2019].
 
-The secrecy surrounding China's international development financing is puzzling.
-The painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
+Thankfully, due to the painstaking work of researchers to document and analyze trends in China's development financing, both academics and policymakers have learned a great deal about Beijing's approach to giving and lending.
 Far from the rogue donor that many have feared, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors.
-Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
-These goals include international recognition and closer diplomatic ties with developing countries in what China calls "south-south" cooperation.
+Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish strategic and economic objectives in international politics, promote public goods in developing countries, and generate goodwill and stronger diplomatic relations with recipient countries.
 
-However, these goals are difficult to accomplish in secret.
+However, the discovery that China is little different from traditional Western donors makes the limited state-sanctioned transparency of its overseas development financing all the more puzzling.
+Many of the goals often attributed to Western donors (generating goodwill, strengthening diplomatic ties, etc.) are difficult to accomplish in secret.
+And, while Beijing has taken steps to improve the visible branding of its aid projects on the ground, there is limited evidence that this is sufficient for attributing credit to Beijing [see @dietrichEtAl2018].
 This therefore raises a natural question.
@@
 First, international media are one way that countries can generate attention and promote a positive spin on their activities in foreign audiences.
-As Nye (2008) notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
+As nye_public_2008-2 notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
 Perhaps in recognition of this, Beijing has expanded its outward facing state sponsored media activities and news reporting over the past two decades.
@@
 Second, aside from news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
-Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.
-These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.
+Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.^[See @aidData2021.] These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.
 
@@
 
+# Some Stylized Facts
+
+```{r, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
+library(knitr)
+library(here)
+include_graphics(
+  here('06_figures/aid_debt_trends.png')
+)
+```
+
+```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status.'}
+include_graphics(
+  here('06_figures/rate_coverage_visits_by_aid.png')
+)
+```
+
+```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country debtor status.'}
+include_graphics(
+  here('06_figures/rate_coverage_visits_by_debt.png')
+)
+```
+
+```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
+include_graphics(
+  here('06_figures/dev_countries_over_time_by_type.png')
+)
+```
+
+# Results
+
+```{r, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals. Controls and year fixed effects not shown. Models were estimated with random recipient intercepts.'}
+include_graphics(
+  here('06_figures/neg_binom_estimates.png')
+)
+```
+
+```{r, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
+include_graphics(
+  here('06_figures/predicted_differences.png')
+)
+```
+
 \clearpage

### 2022-09-05 04_paper/Draft4_812.Rmd
saving

@@
 fontsize: 12pt
-#bibliography: ref_Xinhua.bib
+bibliography: ref_Xinhua.bib
 link-citations: yes
@@
 China's overseas development financing now surpasses that of the United States, the World Bank, and several other multilateral development and lending institutions combined.
-But despite the mammoth proportions of Beijing's aid (and increasingly debt) that it issues worldwide, the motives behind its overseas activities remain a mystery.
+As the reach and scope of its development activities continue to grow, the motives behind its overseas activities remain hotly contested, and the limited transparency surrounding Beijing's overseas financing only fuels the controversy.
 China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*.
-For this reason, many Western governments assume Beijing deliberately keeps its international development finance a secret[@fuchsRudyak2019].
+For this reason, many Western governments assume Beijing deliberately tries to keep its international development finance a secret [@fuchsRudyak2019].
 
-Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and behaving in global terms **[@nathan&scobell2012]**.
-Similarly, in terms of where China’s money goes and its economic influence concentrates, some countries are more important than others.
-However, no clear hierarchy or conclusive evidence has been drawn so far.
-The secrecy surrounding China's international development financing is puzzling.
-The painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
-**They find** that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors **(citation needed)**.
-Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
-These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.
+Thankfully, due to the painstaking work of researchers to document and analyze trends in China's development financing, both academics and policymakers have learned a great deal about Beijing's approach to giving and lending.
+Although Beijing has primarily focused on its immediate surrounding neighbors in the Asia-Pacific region and Central Asia with respect to its geostrategic interests, it is increasingly thinking and behaving in global terms [@nathan&scobell2012].
+When it comes to Beijing's overseas giving and lending, far from the rogue donor that many have feared, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors [@dreherEtAl2022].
+Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish strategic and economic objectives in international politics, promote public goods in developing countries, and generate goodwill and support stronger diplomatic relations abroad.
 
-However, these goals are difficult to accomplish in secret.
-This, therefore, raises a natural question.
-*Do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts?
+However, the discovery that China is little different from traditional Western donors makes the limited state-sanctioned transparency of its overseas development financing all the more puzzling.
+Many of the goals often attributed to Western donors (generating goodwill, strengthening diplomatic ties, etc.) are difficult to accomplish in secret.
+And, while Beijing has taken steps to improve the visible branding of its aid projects on the ground, there is limited evidence that this is sufficient for attributing credit to Beijing [see @dietrichEtAl2018].
+This therefore raises a natural question.
+*Do China’s overseas aid and debt relate to public diplomacy and international recognition?
 If so, how?*
 
-We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
+We propose that despite the lack of formal reporting, Beijing can pursue recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
 Past research has shown that two specific instruments may play special roles in complementing these foreign policy objectives.
-First, media presence is one way that countries can generate attention and promote a positive spin on their activities to foreign audiences.
-As Nye (2008) notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power **(citation needed)**.
-Perhaps in recognition of this, Beijing has expanded its outward-facing state-sponsored media activities and news reporting over the past two decades.
-This has been done in part through the English version of *Xinhua*, China's top state-sponsored news agency.
+First, international media are one way that countries can generate attention and promote a positive spin on their activities in foreign audiences.
+As @nye_public_2008-2 notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
+Perhaps in recognition of this, Beijing has expanded its outward facing state sponsored media activities and news reporting over the past two decades.
+This has been done in part through the English version of *Xinhua*, China's top state sponsored news agency.
 
-Second, aside from expanding news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
-Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.
-These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.
+Second, aside from news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
+Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.^[See @aidData2021.] These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.
 
@@
 In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance.
-Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* (to support China's image and to build publicity around its development activities) and be more frequent hosts of diplomatic missions from Beijing (to support closer bilateral cooperation).
+Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* (to support China's image and to build publicity around its development activities) and be more frequent hosts of diplomatic missions from Beijing (to support closer bilateral diplomacy and cooperation).
 
@@
 
+# Some Stylized Facts
+
+```{r, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
+library(knitr)
+library(here)
+include_graphics(
+  here('06_figures/aid_debt_trends.png')
+)
+```
+
+```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status.'}
+include_graphics(
+  here('06_figures/rate_coverage_visits_by_aid.png')
+)
+```
+
+```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country debtor status.'}
+include_graphics(
+  here('06_figures/rate_coverage_visits_by_debt.png')
+)
+```
+
+```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
+include_graphics(
+  here('06_figures/dev_countries_over_time_by_type.png')
+)
+```
+
+\clearpage
+
+# Results
+
+```{r, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals. Controls and year fixed effects not shown. Models were estimated with random recipient intercepts.'}
+include_graphics(
+  here('06_figures/neg_binom_estimates.png')
+)
+```
+
+```{r, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
+include_graphics(
+  here('06_figures/predicted_differences.png')
+)
+```
+
+\clearpage
+
 # References

### 2022-09-05 03_analysis/01_new_analysis.R

@@ -6,13 +6,10 @@
 # setup -------------------------------------------------------------------
 
 rm(list = ls())
-library(tidyverse)
-library(censReg)
-library(AER)
-library(texreg)
-library(estimatr)
-library(mgcv)
-library(here)
+library(tidyverse) # syntax
+library(glmmTMB)   # mixed-effects neg. binom. models
+library(texreg)    # printing regression output
+library(here)      # reduce headaches navigating the working directory
 theme_set(theme_light())
 
 # data --------------------------------------------------------------------
@@ -70,6 +67,11 @@ dt %>%
   ) +
   theme(
     legend.position = 'top'
+  ) 
+  ggsave(
+    here('06_figures/aid_debt_trends.png'),
+    height = 4,
+    width = 6
   )
 
 # coverage and visits by aid and debt
@@ -98,7 +100,8 @@ dt %>%
     labels = scales::comma
   ) +
   scale_color_manual(
-    values = c('Recipient' = 'royalblue', 'Non-recipient' = 'indianred3')
+    values = c('Recipient' = 'royalblue', 
+               'Non-recipient' = 'indianred3')
   ) +
   facet_wrap(
     ~ name, scales = 'free'
@@ -110,6 +113,11 @@ dt %>%
   ) +
   theme(
     legend.position = 'top'
+  ) 
+  ggsave(
+    here('06_figures/total_coverage_visits_by_aid.png'),
+    height = 4,
+    width = 6
   )
 
 dt %>%
@@ -125,7 +133,7 @@ dt %>%
   aes(
     x = year,
     y = value,
-    color = ifelse(`debt > 0`, 'Recipient', 'Non-recipient')
+    color = ifelse(`debt > 0`, 'Debtor', 'Non-debtor')
   ) +
   geom_line(
     size = 0.75
@@ -134,7 +142,8 @@ dt %>%
     labels = scales::comma
   ) +
   scale_color_manual(
-    values = c('Recipient' = 'royalblue', 'Non-recipient' = 'indianred3')
+    values = c('Debtor' = 'royalblue', 
+               'Non-debtor' = 'indianred3')
   ) +
   facet_wrap(
     ~ name, scales = 'free'
@@ -146,6 +155,11 @@ dt %>%
   ) +
   theme(
     legend.position = 'top'
+  ) 
+  ggsave(
+    here('06_figures/total_coverage_visits_by_debt.png'),
[…]

### 2022-09-05 04_paper/Draft4_2_0826.Rmd

---
title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: yes
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

Abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

# Introduction

China's overseas development financing now surpasses that of the United States, the World Bank, and several other multilateral development and lending institutions combined. But despite the mammoth proportions of Beijing's aid (and increasingly debt) that it issues worldwide, the motives behind its overseas activities remain a mystery. China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*. For this reason, many Western governments assume Beijing deliberately keeps its international development finance a secret [@fuchsRudyak2019].

Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and behaving in global terms [@nathan_chinas_2012]. Similarly, in terms of where China’s money goes and its economic influence concentrates, some countries are more important than others. However, no clear hierarchy or conclusive evidence has been drawn so far. The secrecy surrounding China's international development financing is puzzling. The painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending. **They find** that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors **(citation needed)**. Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics. These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls ``South-South" cooperation.

However, the goals of facilitating cooperation and winning international recognition as a rising power are difficult to accomplish in secret. This, therefore, raises a natural question. *Do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts? If so, how?*

We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities. We look at the Chinese multidimensional public diplomacy efforts – foreign aid and debt operations, outward-facing news articles, and diplomatic visits. Past research has shown that two specific instruments may play special roles in complementing the foreign policy objectives of distributing money. First, media presence is one way that countries can generate attention and promote a positive spin on their activities to foreign audiences. As Nye [-@nye_public_2008-2] notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power. Perhaps in recognition of this, Beijing has expanded its outward-facing state-sponsored media activities and news reporting over the past two decades. This has been done in part through the English version of *Xinhua*, China's top state-sponsored news agency.

Second, aside from expanding news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions. Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages. These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.

While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes. In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance. Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* to support China's image and to build publicity around its development activities, and be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.

As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to types of assistance China offers. Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF). However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals. The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreher_banking_2022.] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.

The results from the analysis of Dreher and his coauthors [-@dreher_banking_2022] provide a novel perspective on the ways that China applies additional instruments to complement the goals it pursues via its overseas development financing. While the findings overall are consistent with our hypotheses, they do so in ways that also problematize the neat distinction between China's use of aid and debt. In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's ODA recipients, while no significant relationship exists between aid and diplomatic visits. Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage. Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomacy with its debtors.

Aid recipient countries disproportionately get more media attention from *Xinhua* to report their economy and needs for development projects and aid. Notably, *Xinhua* does not just promote China’s efforts to offer aid to those countries in need but also gives a rounded picture of those countries’ economic conditions that justify their bases of needs.

Another implication of our finding is that Beijing is more likely to lend money to its “friends”: countries with more cordial diplomatic relations tend to have closer political interests and ties. A 2018 Belt and Road Initiative foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing’s economic interests and strategic dominance – China tends to lend its loans to vulnerable states with debt distress in exchange for unfair deals and strategic concessions. Brautigam [-@brautigam_critical_2020] calls the Chinese ``debt-trap diplomacy" a meme based on collective fear of the Chinese threat rather than sound empirical evidence. Our finding suggests that China is more likely to provide loans to diplomatically aligned countries. For instance, Russia, one of China’s closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017. In contrast, Iraq shows the opposite pattern: it receives the highest amount of aid from China during the period of our investigation, but it does not receive any loans.

# Xinhua’s Global Horizons

*Xinhua* is firmly under the control of the CCP’s Central Propaganda Department. In 2013, President Xi Jinping exhorted the Propaganda Department to “tell Chinese stories well,” and *Xinhua* news agency is at the forefront [@xinhua_xi_2013].  It also has an increasingly global reach to produce millions of articles in the past decade with hundreds of bureaus worldwide. Yet, *Xinhua*’s news reports should not be dismissed as mere propaganda or empty slogans. *Xinhua* presents itself as a balanced and fact-based news agency, not a government mouthpiece [@brazys_chinas_2020]. This outward-facing Chinese official media, whose mission as a key disseminator of the Party’s narrative to foreign audiences, may inform us of the PRC government’s initiatives of presenting Chinese perspectives of real-time events to global audiences.

*Xinhua* is global, but also serves as the main domestic media outlet. International and domestic audiences are two separate audiences, as *Xinhua* will produce its news contents in English, French, Spanish, Korean and Japanese, as well as Chinese. Brazys and Dukalaskis [-@brazys_chinas_2020] analyze how different countries are talked about in *Xinhua*’s articles in Chinese and in languages other than Chinese. They find that domestic-facing articles about other countries or regions are neither negative nor neutral, while articles about China are slightly positive. In contrast, *Xinhua*’s outward-facing articles use overall positive tones to report other countries and regions, including the United States. When characterizing China to foreign audiences, the tone is much more positive than the tone it uses for Chinese readers, or stories about any other country to both audiences.

The Chinese government is acutely sensitive to China’s image in foreign media coverage. In addition to building *Xinhua* as a global news agency, China also invests in ownership stake in media companies in other developing countries. A working paper by Sundquist [-@sundquist_telling_2022] shows that the media outlets after the ownership change adopt a more friendly tone when reporting China. This finding is consistent with the conventional argument that media ownership exerts a homogenizing effect on the newspapers’ coverage of foreign policy [@baum_media_2019]. Sending constructive media messages and shaping stories about China to international audiences is critical to Beijing, and *Xinhua* is not alone in this initiative.

\clearpage

# References

### 2022-09-07 04_paper/Draft4_812.Rmd
trying

@@
 This therefore raises a natural question.
-*Do China’s overseas aid and debt relate to public diplomacy and international recognition?
+*Does China’s overseas development financing relate to public diplomacy and international recognition?
 If so, how?*
@@
 While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes.
-In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance.
-Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* (to support China's image and to build publicity around its development activities) and be more frequent hosts of diplomatic missions from Beijing (to support closer bilateral diplomacy and cooperation).
+In particular, diplomacy and coverage are critical *visible* activities that can compensate for the often opaque character of Beijing's development finance.
+Thus, to the extent that China's development finance is targeted at image-building and diplomatic activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in the English version of *Xinhua* (to support China's image and to build publicity around its development activities) and be more frequent hosts of diplomatic missions from Beijing (to support closer bilateral diplomacy and cooperation).
 
-As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to types of assistance China offers.
+As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to the types of assistance China offers.
 Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
@@
 # Some Stylized Facts
+
+Figure 1 shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017.
+Values are shown in millions of 2017 USD.
+Blue shows values for aid and red shows values for debt.
+The difference in China's application of debt relative to aid is stark, and the gulf only expands over time.
+The observed explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century, as others have documented.
+Burdened with vast foreign currency reserves due do years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreherEtAl2022].
+This focus spurred a radical change in China's development finance portfolio.
+As @dreherEtAl2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5).
+Figure 1 shows this transformation from donor to lender in the starkest of terms.
 

### 2022-09-07 04_paper/Draft4_2_0826.Rmd
some more writing for stylized facts

@@
 
+# Some Stylized Facts
+
+Figure 1 shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017.
+Values are shown in millions of 2017 USD.
+Blue shows values for aid and red shows values for debt.
+The difference in China's application of debt relative to aid is stark, and the gulf only expands over time.
+The observed explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century, as others have documented.
+Burdened with vast foreign currency reserves due do years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreherEtAl2022].
+This focus spurred a radical change in China's development finance portfolio.
+As @dreherEtAl2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5).
+Figure 1 shows this transformation from donor to lender in the starkest of terms.
+
+```{r, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
+library(knitr)
+library(here)
+include_graphics(
+  here('06_figures/aid_debt_trends.png')
+)
+```
+
+Alongside this change in Beijing's approach to international development finance, a consensus has evolved that aid and debt serve different functions for China.
+Aid is supposed to support China's foreign policy goals, while debt is supposed to support its market interests.
+In short, aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China.
+
+```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status (top) and debtor status (bottom).', out.width="100%",fig.show='hold'}
+include_graphics(
+  c(here('06_figures/rate_coverage_visits_by_aid.png'),
+    here('06_figures/rate_coverage_visits_by_debt.png'))
+)
+```
+
+Despite this perceived (proposed) division of goals between aid and debt, Figure 2 tells a different story.
+The figure has a lower and upper panel.
+The left frame of each panel shows the mean number of *Xinhua* mentions per developing country per year, and the right frame of each panel shows the mean number of diplomatic visits per developing country per year.
+In the top, the sample is divided by status as a Chinese aid recipient.
+Blue denotes the trend in yearly mentions in *Xinhua* and diplomatic visits per country among recipients of Chinese aid, whereas red denotes these trends among non-recipients.
+In the bottom panel, the sample is divided by status as a Chinese debtor.
+Blue denotes the same trends in the top panel, but in this case for Chinese debtors.
+Meanwhile, red denotes these trends among non-debtors.
+
+```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
+include_graphics(
+  here('06_figures/dev_countries_over_time_by_type.png')
+)
+```
+
+\clearpage
+
+# Results
+
+```{r, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals. Controls and year fixed effects not shown. Models were estimated with random recipient intercepts.'}
+include_graphics(
+  here('06_figures/neg_binom_estimates.png')
+)
+```
+
+```{r, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
+include_graphics(
+  here('06_figures/predicted_differences.png')
+)
+```
+
 \clearpage

### 2022-09-07 03_analysis/01_new_analysis.R

@@ -214,13 +214,13 @@ dt %>%
   aes(
     x = year,
     y = value,
-    color = ifelse(`debt > 0`, 'Recipient', 'Non-recipient')
+    color = ifelse(`debt > 0`, 'Debtor', 'Non-debtor')
   ) +
   geom_line(
     size = 0.75
   ) +
   scale_color_manual(
-    values = c('Recipient' = 'royalblue', 'Non-recipient' = 'indianred3')
+    values = c('Debtor' = 'royalblue', 'Non-debtor' = 'indianred3')
   ) +
   facet_wrap(
     ~ name, scales = 'free'

### 2022-09-08 04_paper/Draft4_2_0826.Rmd
more writing for stylized facts

@@
 The observed explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century, as others have documented.
-Burdened with vast foreign currency reserves due do years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreherEtAl2022].
+Burdened with vast foreign currency reserves due do years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreher_banking_2022].
 This focus spurred a radical change in China's development finance portfolio.
-As @dreherEtAl2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5).
+As @dreher_banking_2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5).
 Figure 1 shows this transformation from donor to lender in the starkest of terms.
@@
 
-Alongside this change in Beijing's approach to international development finance, a consensus has evolved that aid and debt serve different functions for China.
-Aid is supposed to support China's foreign policy goals, while debt is supposed to support its market interests.
+```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
+include_graphics(
+  here('06_figures/dev_countries_over_time_by_type.png')
+)
+```
+
+Not only has China's total international development financing changed over time, so has its concentration in developing countries.
+Figure 2 shows yearly trends in the number of developing countries in the data sample by whether they exclusively receive Chinese aid (blue), exclusively are Chinese debtors (red), are both (green), or are neither (grey).
+The most substantial change over time has been in the number of developing countries that are neither recipients nor debtors with respect to Chinese development financing.
+In 2002 more than 70 of the developing countries in the sample were neither recipients nor debtors of Beijing's.
+By 2017 the count declined to 24.
+
+This change appears to be the product of growth in Beijing's application of debt; though, an expansion in the delivery of aid also explains some of the change.
+While the number of developing countries that are exclusively recipients of Chinese aid has not followed any particular trend (save for a noticeable decline from 2010 to 2014 and a subsequent rebound), the number of debtors has grown considerably.
+In 2002 less than 10 countries exclusively were recipients of Chinese loans (debt), and another 15 were recipients of loans in addition to aid.
+In 2017, 14 developing countries exclusively were recipients of loans, and nearly 50 were recipients of both loans and aid.
+
+However, despite an expansion in the number of debtors over time and the now mammoth scope of total debt relative to aid, most of these loans are concentrated in a smaller set of countries relative to aid.
+Even at its lowest dip in 2013, the number of developing countries that exclusively are beneficiaries of Chinese aid remained greater than the number of developing countries that exclusively were recipients of loans and the number of countries that were recipients of both loans and aid.
+This suggests that has Beijing has shifted its strategy for development finance, its approach has been to cast a wider net with its aid while it takes a more targeted approach with debt.
+
+Alongside these shifts in the application of aid and debt in Beijing's approach to international development finance, a consensus has evolved that aid and debt serve different functions for China.
+Aid is supposed to support China's foreign policy goals, while debt is supposed to support its market interests [see @dreher_banking_2022].
 In short, aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China.
+However, an examination of patterns in the main variables of interest in this study that we argue capture different but related foreign policy activities problematizes this tidy distinction.
 
@@
 
-Despite this perceived (proposed) division of goals between aid and debt, Figure 2 tells a different story.
-The figure has a lower and upper panel.
+Figure 3 shows trends in the number yearly *Xinhua* mentions of developing countries in the sample and the number of yearly diplomatic visits these countries host.
 The left frame of each panel shows the mean number of *Xinhua* mentions per developing country per year, and the right frame of each panel shows the mean number of diplomatic visits per developing country per year.
@@
 
-```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
-include_graphics(
-  here('06_figures/dev_countries_over_time_by_type.png')
-)
-```
+With respect to aid, there is little observable difference in country coverage in *Xinhua* depending on recipient status.
+However, recipients host appreciably more diplomatic missions from Beijing than non-recipients.
+The difference narrows by 2013, but remains nonetheless across the entire sample period.
+Meanwhile, with respect to debt, there are notable differences in both *Xinhua* mentions and diplomatic missions between debtor and non-debtor developing countries.
+Debtor status corresponds with greater levels of both outcomes.
 

### 2022-09-13 04_paper/Draft4_2_0826.Rmd
stylized facts + edits to intro

@@
 
-Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and behaving in global terms [@nathan_chinas_2012].
-Similarly, in terms of where China’s money goes and its economic influence concentrates, some countries are more important than others.
-However, no clear hierarchy or conclusive evidence has been drawn so far.
+Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and acting globally [@nathan_chinas_2012].
+Similarly, in terms of where China’s money goes and its economic influence is concentrated, some countries clearly are more important than others.
+However, Beijing's leaders hold the reasons why close to the vest.
+
 The secrecy surrounding China's international development financing is puzzling.
-The painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
+But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
 **They find** that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors **(citation needed)**.
 Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
-These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls ``South-South" cooperation.
+These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.
 
@@
 We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
-We look at the Chinese multidimensional public diplomacy efforts – foreign aid and debt operations, outward-facing news articles, and diplomatic visits.
-Past research has shown that two specific instruments may play special roles in complementing the foreign policy objectives of distributing money.
-First, media presence is one way that countries can generate attention and promote a positive spin on their activities to foreign audiences.
+Specifically, we consider outward-facing state-sanctioned news coverage and bilateral diplomatic missions from Beijing.
+Past research suggests that these two activities play special roles in complementing the foreign policy objectives that drive China's giving and lending.
+
+Media coverage is one way that countries can generate attention and promote a positive spin on their activities to foreign audiences.
 As Nye [-@nye_public_2008-2] notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
@@
 
-Second, aside from expanding news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
+In addition to expanding the reach and scope of its externally facing news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
 Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.
@@
 In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance.
-Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* to support China's image and to build publicity around its development activities, and be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.
+Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* to support China's image abroad and to build publicity around its development activities, and they will be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.
 
-As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to types of assistance China offers.
+As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to the type of assistance China offers.
 Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
@@
 
-The results from the analysis of Dreher and his coauthors [-@dreher_banking_2022] provide a novel perspective on the ways that China applies additional instruments to complement the goals it pursues via its overseas development financing.
 While the findings overall are consistent with our hypotheses, they do so in ways that also problematize the neat distinction between China's use of aid and debt.
@@
 
-Aid recipient countries disproportionately get more media attention from *Xinhua* to report their economy and needs for development projects and aid.
-Notably, *Xinhua* does not just promote China’s efforts to offer aid to those countries in need but also gives a rounded picture of those countries’ economic conditions that justify their bases of needs.
+Aid recipient countries disproportionately get more media attention from *Xinhua* via stories that report both on the state of their economy and their development needs.
+Notably, *Xinhua* does not just promote China’s efforts to offer aid to those countries in need but also gives a rounded picture of those countries’ economic conditions justifying their legitimate need for aid.
 
-Another implication of our finding is that Beijing is more likely to lend money to its “friends”: countries with more cordial diplomatic relations tend to have closer political interests and ties.
-A 2018 Belt and Road Initiative foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing’s economic interests and strategic dominance – China tends to lend its loans to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
-Brautigam [-@brautigam_critical_2020] calls the Chinese ``debt-trap diplomacy" a meme based on collective fear of the Chinese threat rather than sound empirical evidence.
+Meanwhile, the finding that loans correspond with diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI).
+A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing’s economic interests and strategic dominance---China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
+Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" a meme based on collective fear of the Chinese threat rather than sound empirical evidence.
 Our finding suggests that China is more likely to provide loans to diplomatically aligned countries.
@@
 In contrast, Iraq shows the opposite pattern: it receives the highest amount of aid from China during the period of our investigation, but it does not receive any loans.
+Concern about Chinese debt nonetheless raises a natural question related to the function of diplomacy in debtor countries.
+Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins?
+More research is needed to answer this question.
 
@@
 *Xinhua* is firmly under the control of the CCP’s Central Propaganda Department.
-In 2013, President Xi Jinping exhorted the Propaganda Department to “tell Chinese stories well,” and *Xinhua* news agency is at the forefront [@xinhua_xi_2013].
+In 2013, President Xi Jinping exhorted the Propaganda Department to “tell Chinese stories well,” and the *Xinhua* news agency is at the forefront [@xinhua_xi_2013].
 It also has an increasingly global reach to produce millions of articles in the past decade with hundreds of bureaus worldwide.
@@
 The difference in China's application of debt relative to aid is stark, and the gulf only expands over time.
-The observed explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century, as others have documented.
-Burdened with vast foreign currency reserves due do years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreher_banking_2022].
+
+This explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century.
+Burdened with vast foreign currency reserves due to years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreher_banking_2022].
 This focus spurred a radical change in China's development finance portfolio.
@@
 
-Not only has China's total international development financing changed over time, so has its concentration in developing countries.
+Not only has the composition of China's total international development financing changed over time, so has its portfolio of developing countries.
 Figure 2 shows yearly trends in the number of developing countries in the data sample by whether they exclusively receive Chinese aid (blue), exclusively are Chinese debtors (red), are both (green), or are neither (grey).
@@
 This change appears to be the product of growth in Beijing's application of debt; though, an expansion in the delivery of aid also explains some of the change.
-While the number of developing countries that are exclusively recipients of Chinese aid has not followed any particular trend (save for a noticeable decline from 2010 to 2014 and a subsequent rebound), the number of debtors has grown considerably.
+While the number of developing countries that are exclusively recipients of Chinese aid has not followed any particular trend (save for a noticeable decline from 2010 to 2014 and subsequent rebound), the number of debtors has grown considerably.
 In 2002 less than 10 countries exclusively were recipients of Chinese loans (debt), and another 15 were recipients of loans in addition to aid.
@@
 
-However, despite an expansion in the number of debtors over time and the now mammoth scope of total debt relative to aid, most of these loans are concentrated in a smaller set of countries relative to aid.
+However, despite an expansion in the number of debtors over time and the now mammoth scope of total lending, most of this debt is concentrated in a smaller set of countries relative to aid.
 Even at its lowest dip in 2013, the number of developing countries that exclusively are beneficiaries of Chinese aid remained greater than the number of developing countries that exclusively were recipients of loans and the number of countries that were recipients of both loans and aid.
@@
 Aid is supposed to support China's foreign policy goals, while debt is supposed to support its market interests [see @dreher_banking_2022].
-In short, aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China.
-However, an examination of patterns in the main variables of interest in this study that we argue capture different but related foreign policy activities problematizes this tidy distinction.
+The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China.
+However, an examination of patterns in the main variables of interest in this study problematizes this tidy distinction.
 
@@
 
+Recall that hypothesis 1 holds that Beijing will concentrate more *Xinhua* coverage in development finance recipients, and that hypothesis 2 holds that it will send more diplomatic missions to recipients.
 With respect to aid, there is little observable difference in country coverage in *Xinhua* depending on recipient status.
 However, recipients host appreciably more diplomatic missions from Beijing than non-recipients.
-The difference narrows by 2013, but remains nonetheless across the entire sample period.
-Meanwhile, with respect to debt, there are notable differences in both *Xinhua* mentions and diplomatic missions between debtor and non-debtor developing countries.
-Debtor status corresponds with greater levels of both outcomes.
+The difference narrows by 2013, but remains across the entire sample period.
+With respect to debt, there are notable differences in both *Xinhua* mentions and diplomatic missions between debtor and non-debtor developing countries.
+Debtor status corresponds with more frequent yearly mentions in *Xinhua* and a greater number of hosted missions from Beijing.
+
+These patterns remain only suggestive.
+Many factors jointly determine Beijing's financing, *Xinhua* coverage, and diplomatic missions that likely confound straightforward identification of the relationships among these variables.
+The next section summarizes the results from more rigorous statistical tests of hypotheses 1 and 2.
 

### 2022-09-14 04_paper/0913_draft.Rmd
figures + descriptions
Also I change the way to referencing figures

--- 2022-09-13 04_paper/Draft4_2_0826.Rmd
@@
 output: 
-  pdf_document:
-    number_sections: yes
+  bookdown::pdf_document2: 
+    toc: false
 classoption: fleqn
@@
 
-Figure 1 shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017.
+Figure \@ref(fig:total-aid-debt) shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017.
 Values are shown in millions of 2017 USD.
@@
 As @dreher_banking_2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5).
-Figure 1 shows this transformation from donor to lender in the starkest of terms.
+Figure \@ref(fig:total-aid-debt) shows this transformation from donor to lender in the starkest of terms.
 
-```{r, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
+```{r total-aid-debt, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
 library(knitr)
@@
 
-```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
+```{r 4-types, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
 include_graphics(
@@
 Not only has the composition of China's total international development financing changed over time, so has its portfolio of developing countries.
-Figure 2 shows yearly trends in the number of developing countries in the data sample by whether they exclusively receive Chinese aid (blue), exclusively are Chinese debtors (red), are both (green), or are neither (grey).
+Figure \@ref(fig:4-types) shows yearly trends in the number of developing countries in the data sample by whether they exclusively receive Chinese aid (blue), exclusively are Chinese debtors (red), are both (green), or are neither (grey).
 The most substantial change over time has been in the number of developing countries that are neither recipients nor debtors with respect to Chinese development financing.
@@
 
+```{r aid-debt-country, fig.cap='Top 20 Chinese Aid Recipients (left) and Debt Recipients (right) on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
+include_graphics(
+  here('06_figures/aid_debt.jpg'))
+
+```
+
+Figure \@ref(fig:aid-debt-country) shows the top-20 Chinese aid and debts recipient countries on average between 2002 and 2017.
+Notably, on average, Iraq received 500 million in aid but borrows 0 dollars of loan from China.
+In contrast, Russia borrowed almost 8,000 million dollars from China but received no aid at all.
+There is little overlap between the top recipient countries that receive both aid and debt from China.
+There are stark variations in terms of the amounts China lends.
+Russia and Venezuela were the only countries that borrowed more than 5,000 million dollars debt on average, the sum of which accounted for about 30% of the total lending amounts of the top-20 debt recipients.
+Eight countries are shown on both the left and right frames: Indonesia, Pakistan, Laos, Ethiopia, Cambodia, Sri Lanka, Kenya, and Sudan.
+Geographically, five are in South or East Asia, whereas three are in Africa.
+
+In terms of the compositions of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that 14 out of 20 countries received over 80% of debt in their portfolio.
+The top 5 recipients, Russia, Venezuela, Angola, Kazakhstan and Brazil received support from China almost purely in the form of loans.
+Kazakhstan is the only exception among the five beneficiaries that received slightly 2\% of aid in its portfolio.
+We can infer that Beijing invests more heavily in its debt, comparing to its aid distribution.
+In consistent with the trends demonstrated in Figure \@ref(fig:4-types), China takes a targeted approach with debt.
+
+```{r compositions, fig.cap='The Aid-Debt Composition of the Top 20 Chinese Aid and Debt Recipients on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
+include_graphics(
+  here('06_figures/portfolio.jpg'))
+
+```
+
 Alongside these shifts in the application of aid and debt in Beijing's approach to international development finance, a consensus has evolved that aid and debt serve different functions for China.
@@
 
-```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status (top) and debtor status (bottom).', out.width="100%",fig.show='hold'}
+```{r aid-debt-cov, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status (top) and debtor status (bottom).', out.width="100%",fig.show='hold'}
 include_graphics(
@@
 
-Figure 3 shows trends in the number yearly *Xinhua* mentions of developing countries in the sample and the number of yearly diplomatic visits these countries host.
+Figure \@ref(fig:aid-debt-cov) shows trends in the number yearly *Xinhua* mentions of developing countries in the sample and the number of yearly diplomatic visits these countries host.
 The left frame of each panel shows the mean number of *Xinhua* mentions per developing country per year, and the right frame of each panel shows the mean number of diplomatic visits per developing country per year.
@@
 
-```{r, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals. Controls and year fixed effects not shown. Models were estimated with random recipient intercepts.'}
+```{r binom-est, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals.
+Controls and year fixed effects not shown.
+Models were estimated with random recipient intercepts.'}
 include_graphics(
@@
 
-```{r, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
+```{r predicted-diff, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
 include_graphics(

### 2022-09-14 04_paper/0913_draft.Rmd
minor edits

@@
 Figure \@ref(fig:aid-debt-country) shows the top-20 Chinese aid and debts recipient countries on average between 2002 and 2017.
-Notably, on average, Iraq received 500 million in aid but borrows 0 dollars of loan from China.
-In contrast, Russia borrowed almost 8,000 million dollars from China but received no aid at all.
+Notably, on average, Iraq received 500 million in aid but borrows 0 dollars in loans from China.
+In contrast, Russia borrowed almost 8 billion dollars from China but received no aid at all.
 There is little overlap between the top recipient countries that receive both aid and debt from China.
 There are stark variations in terms of the amounts China lends.
-Russia and Venezuela were the only countries that borrowed more than 5,000 million dollars debt on average, the sum of which accounted for about 30% of the total lending amounts of the top-20 debt recipients.
+Russia and Venezuela were the only countries that borrowed more than 5 billion dollars in debt on average, the sum of which accounted for about 30% of the total lending amounts of the top-20 debt recipients.
 Eight countries are shown on both the left and right frames: Indonesia, Pakistan, Laos, Ethiopia, Cambodia, Sri Lanka, Kenya, and Sudan.
@@
 
-In terms of the compositions of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that 14 out of 20 countries received over 80% of debt in their portfolio.
+In terms of the composition of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that financing received in 14 out of 20 countries was over 80% debt.
 The top 5 recipients, Russia, Venezuela, Angola, Kazakhstan and Brazil received support from China almost purely in the form of loans.
-Kazakhstan is the only exception among the five beneficiaries that received slightly 2\% of aid in its portfolio.
-We can infer that Beijing invests more heavily in its debt, comparing to its aid distribution.
-In consistent with the trends demonstrated in Figure \@ref(fig:4-types), China takes a targeted approach with debt.
+Kazakhstan is the only exception among the five beneficiaries with aid comprising a measly 2% of its portfolio.
+Clearly, we can infer that Beijing invests more heavily in its debt relative to aid.
+Consistent with the trends demonstrated in Figure \@ref(fig:4-types), China takes a targeted approach with debt.
 

### 2022-09-29 04_paper/0929_draft.Rmd
adding aid section

--- 2022-09-14 04_paper/0913_draft.Rmd
@@
 Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and acting globally [@nathan_chinas_2012].
-Similarly, in terms of where China’s money goes and its economic influence is concentrated, some countries clearly are more important than others.
+Similarly, in terms of where China's money goes and its economic influence is concentrated, some countries clearly are more important than others.
 However, Beijing's leaders hold the reasons why close to the vest.
@@
 This, therefore, raises a natural question.
-*Do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts?
+*Do China's foreign aid and debt allocation relate to public diplomacy and international recognition efforts?
 If so, how?*
@@
 However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals.
-The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreher_banking_2022.] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.
+The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.[^1] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.
+
+[^1]: See @dreher_banking_2022.
 
@@
 Aid recipient countries disproportionately get more media attention from *Xinhua* via stories that report both on the state of their economy and their development needs.
-Notably, *Xinhua* does not just promote China’s efforts to offer aid to those countries in need but also gives a rounded picture of those countries’ economic conditions justifying their legitimate need for aid.
+Notably, *Xinhua* does not just promote China's efforts to offer aid to those countries in need but also gives a rounded picture of those countries' economic conditions justifying their legitimate need for aid.
 
 Meanwhile, the finding that loans correspond with diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI).
-A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing’s economic interests and strategic dominance---China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
+A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance---China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
 Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" a meme based on collective fear of the Chinese threat rather than sound empirical evidence.
 Our finding suggests that China is more likely to provide loans to diplomatically aligned countries.
-For instance, Russia, one of China’s closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017.
+For instance, Russia, one of China's closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017.
 In contrast, Iraq shows the opposite pattern: it receives the highest amount of aid from China during the period of our investigation, but it does not receive any loans.
@@
 
-# Xinhua’s Global Horizons
+# Motivations behind Chinese Foreign Aid
 
-*Xinhua* is firmly under the control of the CCP’s Central Propaganda Department.
-In 2013, President Xi Jinping exhorted the Propaganda Department to “tell Chinese stories well,” and the *Xinhua* news agency is at the forefront [@xinhua_xi_2013].
+China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors.
+While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests.
+Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
+At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
+Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].
+
+Two waves of surveys of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.[^2] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries.
+It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.
+
+[^2]: Reported by AidData ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) on March 22, 2018.
+Accessed March 3, 2022
+
+If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing.
+Visual branding of aid has emerged as a growing concern among donors.
+The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.[^3] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US.
+Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."[^4]
+
+[^3]: See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).
+
+[^4]: ["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012.
+Accessed March 3, 2022.
+
+Given the diplomatic uses of foreign aid, the obscurity that surrounds Beijing's development finance is all the more puzzling.
+Unlike Western donors, China does not report its financing activities to an international organization or make its activities visible in an online database.
+To say transparency is out of character for Beijing is an understatement, but foreign aid is one issue area where transparency would arguably serve China's interests.
+So why the secrecy?
+
+As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret.
+But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.[^5] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing.
+Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA).
+However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.[^6]
+
+[^5]: See @fuchsRudyak2019 for several related citations.
+
+[^6]: See this excellent summary entitled ["The Logic Behind China's Foreign Aid Agency"](https://carnegieendowment.org/2019/05/21/logic-behind-china-s-foreign-aid-agency-pub-79154) by the Carnegie Endowment for International Peace published May 21, 2019.
+Accessed March 10, 2022.
+
+Absent transparency in reporting, there are other tools at Beijing's disposal that may complement the diplomatic objectives behind its foreign aid.
+In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives.
+We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences).
+We summarize these factors in greater detail in the following sections.
+
+# Xinhua's Global Horizons
+
+*Xinhua* is firmly under the control of the CCP's Central Propaganda Department.
+In 2013, President Xi Jinping exhorted the Propaganda Department to "tell Chinese stories well," and the *Xinhua* news agency is at the forefront [@xinhua_xi_2013].
 It also has an increasingly global reach to produce millions of articles in the past decade with hundreds of bureaus worldwide.
-Yet, *Xinhua*’s news reports should not be dismissed as mere propaganda or empty slogans.
+Yet, *Xinhua*'s news reports should not be dismissed as mere propaganda or empty slogans.
 *Xinhua* presents itself as a balanced and fact-based news agency, not a government mouthpiece [@brazys_chinas_2020].
-This outward-facing Chinese official media, whose mission as a key disseminator of the Party’s narrative to foreign audiences, may inform us of the PRC government’s initiatives of presenting Chinese perspectives of real-time events to global audiences.
+This outward-facing Chinese official media, whose mission as a key disseminator of the Party's narrative to foreign audiences, may inform us of the PRC government's initiatives of presenting Chinese perspectives of real-time events to global audiences.
 
@@
 International and domestic audiences are two separate audiences, as *Xinhua* will produce its news contents in English, French, Spanish, Korean and Japanese, as well as Chinese.
-Brazys and Dukalaskis [-@brazys_chinas_2020] analyze how different countries are talked about in *Xinhua*’s articles in Chinese and in languages other than Chinese.
+Brazys and Dukalaskis [-@brazys_chinas_2020] analyze how different countries are talked about in *Xinhua*'s articles in Chinese and in languages other than Chinese.
 They find that domestic-facing articles about other countries or regions are neither negative nor neutral, while articles about China are slightly positive.
-In contrast, *Xinhua*’s outward-facing articles use overall positive tones to report other countries and regions, including the United States.
+In contrast, *Xinhua*'s outward-facing articles use overall positive tones to report other countries and regions, including the United States.
 When characterizing China to foreign audiences, the tone is much more positive than the tone it uses for Chinese readers, or stories about any other country to both audiences.
 
-The Chinese government is acutely sensitive to China’s image in foreign media coverage.
+The Chinese government is acutely sensitive to China's image in foreign media coverage.
 In addition to building *Xinhua* as a global news agency, China also invests in ownership stake in media companies in other developing countries.
 A working paper by Sundquist [-@sundquist_telling_2022] shows that the media outlets after the ownership change adopt a more friendly tone when reporting China.
-This finding is consistent with the conventional argument that media ownership exerts a homogenizing effect on the newspapers’ coverage of foreign policy [@baum_media_2019].
+This finding is consistent with the conventional argument that media ownership exerts a homogenizing effect on the newspapers' coverage of foreign policy [@baum_media_2019].
 Sending constructive media messages and shaping stories about China to international audiences is critical to Beijing, and *Xinhua* is not alone in this initiative.

### 2022-09-29 04_paper/0929_draft.Rmd
media and diplomacy added

@@
 
-Abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
+abstract: "[*old abstract*] Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
 We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
@@
 To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
+To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) meta-data of millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
 We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
@@
 This, therefore, raises a natural question.
-*Do China's foreign aid and debt allocation relate to public diplomacy and international recognition efforts?
-If so, how?*
+*How do China's foreign aid and debt allocation relate to public diplomacy and international recognition efforts?*
 
@@
 
-# Xinhua's Global Horizons
+# Media’s Agenda-Setting Effects
 
+## First-level Agenda-setting
+
+Agenda-setting refers to the ability of media to signal to the public what is important.
+Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public.
+That is, the public learns the importance of objects based on the amount of coverage that those objects receive.
+Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues [@mccombs_agenda-setting_1972].
+More specifically, as Lang and Lang [-@berelson_mass_1966] observe, "The mass media force attention to certain issues.
+They build up public images of political figures.
+They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about" (p.
+468).
+Since their seminal work, hundreds of studies have examined this media effect on the public.
+
+Over decades of rich research in agenda-setting, empirical patterns support Cohen [-@cohen_press_1963] 's famous notation that the media is "stunningly successful in telling its readers what to think about" (p.
+13; *emphasis added*).
+That is, the salience of news media reports transfers to the perception of issue salience to the public [@mccombs_agenda-setting_1972].
+Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn, shapes individuals' perceptions of the relative importance and salience of the issues.
+
+To extend this logic, media salience indicates significance for foreign countries named in the media.
+Wanta et al.
+[-@wanta_agenda_2004-3] show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S.
+The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.
+
+With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention.
+From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air.
+News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.
+
+Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover.
+Not all countries in the world receive equal coverage.
+In fact, only a small portion of international events can get through the media gatekeepers and get media coverage.
+While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered.
+Golan and Wanta's [-@golan_international_2003-1] study examines how 138 elections held between 1998 and 2000 were covered by the U.S.
+network television newscasts (ABC, CBS, NBC and CNN).
+They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa.
+A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage [@sheafer_relative_2014-1].
+Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.
+
+## Second-level Agenda-setting and Xinhua's Global Horizons
+
+In addition to swaying people's attention, media agenda-setting is also critical in building states' image to international audiences.
+Nye [-@nye_public_2008-2] suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications, with an aim to improve the country's "soft power".
+Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press.
+China has expanded its Xinhua News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.
+
+Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others [@entman_theorizing_2008; @kiousis_international_2008].
+Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes.
+Improving one's image to foreign audiences is the core objective of mediated public diplomacy.
+
+As a state-sponsored media platform, Xinhua News Agency is often considered more than a news media agency.
 *Xinhua* is firmly under the control of the CCP's Central Propaganda Department.
 In 2013, President Xi Jinping exhorted the Propaganda Department to "tell Chinese stories well," and the *Xinhua* news agency is at the forefront [@xinhua_xi_2013].
-It also has an increasingly global reach to produce millions of articles in the past decade with hundreds of bureaus worldwide.
+It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy [@shambaugh_chinas_2015-1], with an increasingly global reach to produce millions of articles in the past decade with hundreds of bureaus worldwide.
 Yet, *Xinhua*'s news reports should not be dismissed as mere propaganda or empty slogans.
 *Xinhua* presents itself as a balanced and fact-based news agency, not a government mouthpiece [@brazys_chinas_2020].
+It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires.
+The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea.
+It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format.
 This outward-facing Chinese official media, whose mission as a key disseminator of the Party's narrative to foreign audiences, may inform us of the PRC government's initiatives of presenting Chinese perspectives of real-time events to global audiences.
+Governments use media to tell its story to the world and improve its public relations with other countries.
+As such, scholars often focus on Chinese mediated public diplomacy efforts through Xinhua.
+That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries [@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009].
 
@@
 
+This paper will focus on Xinhua outward-facing English branch whose audiences are primarily English-speaking readers.
+Simply providing more information will not improve their image in the Western world.
+Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack.
+As Druckman (2001) presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
+On the other hand, Xinhua needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.
+
+Hence, while Xinhua plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information.
+It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
+Taking into account the limited space of Xinhua to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.
+
 The Chinese government is acutely sensitive to China's image in foreign media coverage.
@@
 Sending constructive media messages and shaping stories about China to international audiences is critical to Beijing, and *Xinhua* is not alone in this initiative.
+
+# Public Diplomacy
+
+Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country.
+For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people – and listen to them" [@hoffman_introduction_1968, p.
+4].
+In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" [@deibel_culture_1976, p.
+15].
+
+An image that fits into a traditional mental image of public diplomacy is "diplomats engaged in traditional negotiations under the glare of publicity" [@deibel_culture_1976, p.
+13].
+In addition to negotiations behind closed doors, records of visits have symbolic evidence to show the bilateral relationships between countries.
+The elite-level diplomacy, government-to-government diplomatic visit, is the focus in this section.
+
+Government-to-government visits are important as leaders' resources are scarce.
+They often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005].
+Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and the states' security issues [@mcmanus_making_2018].
+In all, diplomatic visits send important an important positive signal that the visiting and hosting countries support each other and have closer relationships.
+
+Visiting leaders can increase the awareness of themselves and their country among citizens in the host country.
+Goldsmith and Horiuchi [-@goldsmith_spinning_2009] find that the impact of high-level government visits on foreign publics' opinions is contextual.
+U.S.
+visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq.
+Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy.
+The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect.
+The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries [@goldsmith_does_2021].
+In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.
+
+In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.
+From the perspective of communication, diplomatic visit is a signal of support and proximity of the countries.
+The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.
+
+# Hypotheses [just a start]
+
+We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion.
+News editors build the credibility of the news agency to transmit information around the globe.
+High-level officials spend time and resources to visit other countries for economic or security purposes – to strengthen the bilateral relationship.
+Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically.
+In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing.
+They are in the potential friend circle.
+While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic.
+Foreign aid, instead, provides tangible and materials support to the countries in need.
+Hence, we expect China to prioritize giving foreign aid to its “friends” -- countries where China has developed multi-facet relationships through public diplomacy efforts.
+This rationale leads to our hypotheses:
 

### 2022-10-06 04_paper/1006_draft.Rmd
building on aid section

--- 2022-09-29 04_paper/0929_draft.Rmd
@@
 But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
-**They find** that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors **(citation needed)**.
+In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors.
 Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
@@
 
-# Motivations behind Chinese Foreign Aid
+# Motivations behind Chinese Overseas Financing
 
@@
 
-# Media’s Agenda-Setting Effects
+In addition to considering how diplomatic missions and state-sponsored outward-facing media correspond with Beijing's development finance, we also distinguish between Beijing's ODA-like expenditures and its other official flows (OOF).
+The former we may call aid (or development assistance), and the latter we may call debt (or loans).
+As @dreher_banking_2022 note, Beijing uses aid and debt to accomplish different goals, and it further does not finance them in equal proportion, both in terms of total spending and in terms of how it targets funds across developing countries.
+@dreher_banking_2022 argue that aid tends to be most associated with China's foreign policy goals, while debt tends to correspond to its market interests.
+What do these differences imply for Beijing's bilateral diplomacy and state-sponsored foreign media?
+
+On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences.
+On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic.
+Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy.
+On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically.
+As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources.
+When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans[@dreher_banking_2022].
+
+# Media's Agenda-Setting Effects
 
@@
 It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
-Taking into account the limited space of Xinhua to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.
+Taking into account the limited space of Xinhua to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.
 
@@
 Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country.
-For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people – and listen to them" [@hoffman_introduction_1968, p.
+For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" [@hoffman_introduction_1968, p.
 4].
@@
 News editors build the credibility of the news agency to transmit information around the globe.
-High-level officials spend time and resources to visit other countries for economic or security purposes – to strengthen the bilateral relationship.
+High-level officials spend time and resources to visit other countries for economic or security purposes -- to strengthen the bilateral relationship.
 Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically.
@@
 They are in the potential friend circle.
-While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic.
+While public diplomacy is one way to increase a state's soft power, in the end, it is intangible power and symbolic.
 Foreign aid, instead, provides tangible and materials support to the countries in need.
-Hence, we expect China to prioritize giving foreign aid to its “friends” -- countries where China has developed multi-facet relationships through public diplomacy efforts.
+Hence, we expect China to prioritize giving foreign aid to its "friends" -- countries where China has developed multi-facet relationships through public diplomacy efforts.
 This rationale leads to our hypotheses:

### 2022-10-06 04_paper/10_06_draft_newabstract.Rmd
Add files via upload

--- 2022-10-06 04_paper/1006_draft.Rmd
@@
 
-abstract: "[*old abstract*] Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving?
+abstract: "Absent formal avenues of transparency, how do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts?
 We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
 These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.
-To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) meta-data of millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research.
-We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid.
-Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
+We also distinguish Beijing-as-donor and Beijing-as-lender.
+We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
+To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid and debt giving.
+To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and yearly counts of bilateral official diplomatic visits from China and (2) the meta-data of millions of English edition Xinhua news articles from 2000 to 2017 in the Cline Center for Advanced Social Research.
+We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors.
+Aid recipient countries disproportionately get more media attention from Xinhua via news stories that report both the state of their economy and their developmental needs.
+Notably, Xinhua does not just promote China’s efforts but also gives a round picture of the countries’ economic conditions in justifying their legitimate need for aid.
+Our results dispel the myths of China as a ’rouge donor’ and Chinese ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid presents a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
+Also, China is more likely to provide loans to diplomatically aligned countries."
 ---
@@
 ```
+\clearpage
 
@@
   here('06_figures/aid_debt.jpg'))
-
 ```
@@
   here('06_figures/portfolio.jpg'))
-
 ```

### 2022-10-13 04_paper/10_12_draft.Rmd
adding to hypothesis section

--- 2022-10-06 04_paper/10_06_draft_newabstract.Rmd
@@
 ```
+
 \clearpage
@@
 On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences.
-On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic.
+On the other hand, while aid and debt may have different goals, such a tidy distinction may be too simplistic.
 Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy.
@@
 
-We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion.
-News editors build the credibility of the news agency to transmit information around the globe.
-High-level officials spend time and resources to visit other countries for economic or security purposes -- to strengthen the bilateral relationship.
-Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically.
-In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing.
-They are in the potential friend circle.
-While public diplomacy is one way to increase a state's soft power, in the end, it is intangible power and symbolic.
-Foreign aid, instead, provides tangible and materials support to the countries in need.
-Hence, we expect China to prioritize giving foreign aid to its "friends" -- countries where China has developed multi-facet relationships through public diplomacy efforts.
-This rationale leads to our hypotheses:
+We have made the case that both foreign state-sponsored media and diplomatic visits can be used to sway foreign public opinion in favor of Beijing.
+By covering developing countries that receive Chinese development financing, *Xinhua* editors can paint a positive picture of Beijing's financing and, in so doing, take steps to promote China's international image.
+In addition, by sending regular diplomatic missions to developing countries, Beijing is able to strengthen its bilateral relationships with countries in the Global South.
+Since both approaches feature scarce time and resources, we expect that Beijing will choose on whom to cast the spotlight and to visit strategically.
+
+Most importantly for China's overseas development financing, coverage and diplomatic visits are immediate visible signals of Beijing's priorities.
+For this reason, Beijing may use both as a way to complement related political objectives it seeks to promote via its financing activities (e.g., its overseas aid and its overseas debt).
+
+To the extent that aid supports Beijing's foreign policy goals, we should expect that aid recipients will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.
+
+> H1: Developing countries that receive more foreign aid from China will receive more coverage in *Xinhua*.
+
+> H2: Developing countries that receive more foreign aid from China will host more diplomatic missions from China.
+
+The same logic applies to Beijing's use of debt.
+If loans function in service of political objectives, then countries that owe greater debt to Beijing also will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.
+
+> H3: Developing countries that owe more debt to China will receive more coverage in *Xinhua*.
+
+> H4: Developing countries that owe more debt to China will host more diplomatic missions from China.
+
+If we can reject the null hypothesis for H1 and H2, but cannot for H3 and H4, this will be consistent with the view that China uses aid---not debt---for political goals [@dreher_banking_2022].
 

### 2022-10-20 04_paper/10_20_draft_newabstract.Rmd
Changes
Update abstract, add placeholders for variables explanations, and polish section 6 stylized facts

--- 2022-10-13 04_paper/10_12_draft.Rmd
@@
 We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy.
-We also distinguish Beijing-as-donor and Beijing-as-lender.
 We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
-To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid and debt giving.
-To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and yearly counts of bilateral official diplomatic visits from China and (2) the meta-data of millions of English edition Xinhua news articles from 2000 to 2017 in the Cline Center for Advanced Social Research.
+We expect greater coverage of a developing country in a Chinese media outlet directed to aid giving, and greater bilateral diplomatic activity to correlate with greater debt allocation.
+To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of Xinhua news articles in the Cline Center for Advanced Social Research.
 We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors.
-Aid recipient countries disproportionately get more media attention from Xinhua via news stories that report both the state of their economy and their developmental needs.
-Notably, Xinhua does not just promote China’s efforts but also gives a round picture of the countries’ economic conditions in justifying their legitimate need for aid.
-Our results dispel the myths of China as a ’rouge donor’ and Chinese ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid presents a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
-Also, China is more likely to provide loans to diplomatically aligned countries."
+Aid-recipient countries disproportionately get more media coverage on the state of their economy and developmental needs.
+Also, China is more likely to provide loans to diplomatically aligned countries.
+Our results dispel the myths of China as a ’rouge donor’ and Chinese ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid presents a versatile foreign policy tool in international politics.
+"
 ---
@@
 ```
-
 \clearpage
@@
 On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences.
-On the other hand, while aid and debt may have different goals, such a tidy distinction may be too simplistic.
+On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic.
 Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy.
@@
 
+In this section, we will provide some figures to show the trends of Chinese aid and debt between 2002 and 2017 and the top 20 recipients in terms of their financial portfolios on average.
+Then we will present some visuals on the correlations between *Xinhua* news coverage, diplomatic visits, Chinese financial outflow destinations in yearly trends as well as in countries ranked the highest percentiles on each dimension.
+
+## Main variables
+
+*aid, debt, Xinhua mentions, diplomatic visits*
+
+## Trends in Aid and Debt
+
 Figure \@ref(fig:total-aid-debt) shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017.
@@
 The difference in China's application of debt relative to aid is stark, and the gulf only expands over time.
-
 This explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century.
@@
 This focus spurred a radical change in China's development finance portfolio.
-As @dreher_banking_2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5).
+As @dreher_banking_2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (p.
+5).
 Figure \@ref(fig:total-aid-debt) shows this transformation from donor to lender in the starkest of terms.
 
-```{r total-aid-debt, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
+```{r total-aid-debt, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.', out.width="80%", fig.align = 'center'}
 library(knitr)
@@
 
-```{r 4-types, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
+```{r 4-types, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.', out.width="80%", fig.align = 'center'}
 include_graphics(
@@
 
-Figure \@ref(fig:aid-debt-country) shows the top-20 Chinese aid and debts recipient countries on average between 2002 and 2017.
+Figure \@ref(fig:aid-debt-country) shows the top 20 Chinese aid and debts recipient countries on average between 2002 and 2017.
 Notably, on average, Iraq received 500 million in aid but borrows 0 dollars in loans from China.
@@
 
+## Interplay between Chinese Aid and Debt Outflows, News Mentions and Diplomatic Destinations
+
 Figure \@ref(fig:aid-debt-cov) shows trends in the number yearly *Xinhua* mentions of developing countries in the sample and the number of yearly diplomatic visits these countries host.
@@
 
-Recall that hypothesis 1 holds that Beijing will concentrate more *Xinhua* coverage in development finance recipients, and that hypothesis 2 holds that it will send more diplomatic missions to recipients.
+Recall that hypotheses 1 and 3 hold that Beijing will concentrate more *Xinhua* coverage in development finance recipients, and that hypotheses 2 and 4 hold that it will send more diplomatic missions to recipients.
 With respect to aid, there is little observable difference in country coverage in *Xinhua* depending on recipient status.
@@
 
+Finally, we examine the overlaps between top 20 *Xinhua* news coverage countries and the top 10 percent aid and debt recipients of the year in Figure \@ref(fig:coverage-combined).
+The y-axis is the list of top 20 *Xinhuan* news coverage countries ranked in order.
+The blud or red colors denote whether the countries are ranked as top 10 percent debt aid or recipients of the year.
+The bigger the dot is, the higher amount of yearly news coverage count it is.
+Russia received the highest number of news exposure between 2002 and 2017 on average.
+It also consistently stands as top 10 percent debt recipients of the year (shown as red dots in Figure \@ref(fig:coverage-combined) (bottom)).
+Take India as another example: in 2009, 2010, 2011 and 2012, it received over 400 times mentions in *Xinhua* and ranked as the top 10 percent debt recipients.
+Indonesia also consistently received over 200 yearly mentions in *Xinhua* reports and borrowed significantly amount of money from China.
+Overall, there is a significant overlap for countries receiving high media exposure and scoring high percentiles in Chinese debt and aid during the time of investigation.
+
+```{r coverage-combined, fig.cap='Distribution of top 20 Xinhua news coverage ocuntries and top 10 percent aid (top) and debt (bottom) recipients from 2002 to 2017.', out.width="100%",fig.show='hold'}
+
+include_graphics(
+  here('06_figures/coverages_combined.jpg'))
+
+```
+
+Similarly, Figure \@ref(fig:visits-combined) shows the overlaps between top 20 diplomatic visits countries and the top 10 percent aid and debt recipients of the year.
+Nine countries[^7] were listed as the top 20 diplomatic visits and *Xinhua* news coverage on average between 2002 and 2017.
+Countries such as Kazakhstan, India and Thailand often hosted Chinese high officials for more than 30 times a year.
+Overall, China seemed to visit the list of the top 10 countries over 10 times and reguarly except for four countries in 2016 and 2017.
+These countries were more likely to be countries where received the highest percentiles of financial inflows from China.
+
+[^7]: India, Indonesia, Thailand, Malaysia, Afghanistan, Pakistan, Philippines, Cambodia, Vietnam.
+
+```{r visits-combined, fig.cap='Distribution of top 20 diplomatic visits destinations and top 10 percent aid (top) and debt (bottom) recipients from 2002 to 2017.', out.width="100%", fig.show='hold'}
+
+include_graphics(
+  here('06_figures/visits_combined.jpg'))
+
+```
+
 These patterns remain only suggestive.
 Many factors jointly determine Beijing's financing, *Xinhua* coverage, and diplomatic missions that likely confound straightforward identification of the relationships among these variables.
-The next section summarizes the results from more rigorous statistical tests of hypotheses 1 and 2.
-
-\clearpage
+The next section summarizes the results from more rigorous statistical tests of hypotheses 1 to 4.
 
@@
 
+**Adding confounders here**
+
 ```{r binom-est, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals.
 Controls and year fixed effects not shown.
-Models were estimated with random recipient intercepts.'}
+Models were estimated with random recipient intercepts.', fig.show='hold'}
 include_graphics(
@@
 
-```{r predicted-diff, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
+```{r predicted-diff, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.', fig.show='hold'}
 include_graphics(

### 2022-10-20 04_paper/10_20_draft_newabstract.Rmd
started working on summary on methods

@@
 
+# Methods
+
+To test hypotheses 1-4 we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively.
+Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process.
+We opt for negative binomial regression rather than Poisson since the variance of the outcomes is not equivalent to their means.
+We further apply the zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values.
+Because of the panel nature of the data, we further include random recipient intercepts in model estimation to account for within-recipient dependence and additional unobserved recipient heterogeneity.
+
+The first two specifications below model the yearly count of *Xinhua* mentions and of diplomatic visits from Beijing given the identity of the recipient country as one of either an aid beneficiary, a debtor, or both.
+These variables are denoted by a vector called "Type" which contains binary indicators for whether country $i$ in year $t$ receives exclusively aid, exclusively debt, or both from Beijing.
+
+$$
+\text{coverage}_{it} = \exp\{\tau_t + \text{Type}_{it}^\top \beta + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}; \tag{1}
+$$
+
+$$
+\text{visits}_{it} = \exp\{\tau_t + \text{Type}_{it}^\top \beta + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}. \tag{2}
+$$
+
+These models are blunt tests of differences between coverage and visits for aid recipients and debtors relative to countries that receive neither from China.
+We additionally estimate the following two models to test whether changes in the amount of aid or debt received correspond to shifts in coverage and visits:
+
+$$
+\text{coverage}_{it} = \exp\{\tau_t + \beta_1 \text{ asinh}(\text{aid}_{it-1}) + \beta_2 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}; \tag{3}
+$$
+
+$$
+\text{visits}_{it} = \exp\{\tau_t + \beta_2 \text{ asinh}(\text{aid}_{it-1}) + \beta_4 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}. \tag{4}
+$$
+
+Hypotheses 1-4 are tested via the direction and statistical significance of $\beta$ parameters 1-4.
+H1 (that aid recipients receive more outward facing coverage in *Xinhua*) will be supported if $\beta_1 > 0$ and H2 (that aid recipients host more diplomatic missions from Beijing) will be supported if $\beta_2 > 0$.
+H3 and H4 (hypotheses that parallel H1 and H2, but which apply to Chinese debt) will be supported if $\beta_3>0$ and $\beta_4>0$, respectively.
+
+Models 1-4 each include year intercepts to adjust for yearly shocks and changes to Beijing's overall aid and debt portfolio, denoted by the term $\tau_t$.
+The parameter $\rho_i$ denotes random recipient intercepts.
+The vector $X_{it}$ denotes a set of control variables to improve precision and to adjust for possible confounders for Chinese bilateral financing, *Xinhua* coverage, and diplomatic visits.
+A summary of these variables, any transformations applied, and their sources is given in Table [x].
+
+[Table x goes here]
+
 # Some Stylized Facts

### 2022-10-31 04_paper/10_31_draft.Rmd
mw updates

--- 2022-10-20 04_paper/10_20_draft_newabstract.Rmd
@@
 We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences).
-We summarize these factors in greater detail in the following sections.
 
-In addition to considering how diplomatic missions and state-sponsored outward-facing media correspond with Beijing's development finance, we also distinguish between Beijing's ODA-like expenditures and its other official flows (OOF).
+We summarize these factors in greater detail in the following sections, but before considering them, it is necessary to first summarize the current landscape of China's overseas financing.
+In particular, it is important to draw a distinction between Beijing's ODA-like expenditures and its other official flows (OOF).
 The former we may call aid (or development assistance), and the latter we may call debt (or loans).
-As @dreher_banking_2022 note, Beijing uses aid and debt to accomplish different goals, and it further does not finance them in equal proportion, both in terms of total spending and in terms of how it targets funds across developing countries.
-@dreher_banking_2022 argue that aid tends to be most associated with China's foreign policy goals, while debt tends to correspond to its market interests.
+As @dreher_banking_2022 note in their groundbreaking and comprehensive book on Chinese aid and loans, Beijing uses aid and debt to accomplish different goals, and it further does not finance them in equal proportion, both in terms of total spending and in terms of how it targets funds across developing countries.
+@dreher_banking_2022 argue that aid tends to be most associated with China's foreign policy objectives, while debt tends to correspond to its market interests.
 What do these differences imply for Beijing's bilateral diplomacy and state-sponsored foreign media?
@@
 When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans[@dreher_banking_2022].
+
+What this implies in the aggregate is that aid from China tends to be most strongly determined by both development and political factors, while debt is most strongly determined by market-based factors.
+For the two outcomes discussed in the following sections, this suggests that Chinese ODA-like expenditures more so than OOF should be strong predictors of other complementary and visible foreign policy activities.
+Meanwhile, given the more market-oriented (and by extension more controversial) application of debt, we should expect a much weaker association to exist between OOF and the factors summarized below.
+While visibility may be a virtue for aid, the opposite may be true for debt.
+The next section summarizes these outcomes and their relevance as measures of foreign policy-related activities in the context of China's overseas financing.
 
@@
 By covering developing countries that receive Chinese development financing, *Xinhua* editors can paint a positive picture of Beijing's financing and, in so doing, take steps to promote China's international image.
-In addition, by sending regular diplomatic missions to developing countries, Beijing is able to strengthen its bilateral relationships with countries in the Global South.
+In addition, by sending regular diplomatic missions to developing countries, Beijing is able to strengthen its bilateral relationships with countries in the Global South helping to cement the close bilateral ties the offer of development assistance is, in part, indented to promote.
+
 Since both approaches feature scarce time and resources, we expect that Beijing will choose on whom to cast the spotlight and to visit strategically.
+Most importantly for China's overseas development financing, coverage and diplomatic visits are immediate visible signals of Beijing's priorities.
+For this reason, Beijing may use both as a way to complement related political objectives it seeks to promote via its financing activities.
 
-Most importantly for China's overseas development financing, coverage and diplomatic visits are immediate visible signals of Beijing's priorities.
-For this reason, Beijing may use both as a way to complement related political objectives it seeks to promote via its financing activities (e.g., its overseas aid and its overseas debt).
+However, as noted in the discussion of China's overseas financing, prior research points to the importance of distinguishing between Beijing's ODA-like (aid) activities and its OOF-like (debt) activities.
+Both coverage and visits are visible activities that help to complement the material resources provided in the form of aid.
+However, as noted previously, debt tends to be associated with more market-based goals, which have historically been controversial in the development community.
+This leads to the reasonable conclusion that aid, rather than debt, should have closer correspondence with coverage and visits than debt.
 
@@
 
-The same logic applies to Beijing's use of debt.
-If loans function in service of political objectives, then countries that owe greater debt to Beijing also will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.
+Conversely, to the extent that loans function in service of market-based objectives rather than political ones, then countries that owe greater debt to Beijing also will not necessarily be more likely targets of greater foreign-facing media coverage in *Xinhua* nor more likely hosts of a greater number of diplomatic missions from Beijing.
 
-> H3: Developing countries that owe more debt to China will receive more coverage in *Xinhua*.
+> H3: Developing countries that owe more debt to China will receive no more or less coverage in *Xinhua*.
 
-> H4: Developing countries that owe more debt to China will host more diplomatic missions from China.
+> H4: Developing countries that owe more debt to China will host no more or less diplomatic missions from China.
 
-If we can reject the null hypothesis for H1 and H2, but cannot for H3 and H4, this will be consistent with the view that China uses aid---not debt---for political goals [@dreher_banking_2022].
+If we can reject the null hypothesis for H1 and H2 this will be consistent with the view that China uses aid for political goals.
+Conversely, H3 and H4 are themselves null hypotheses.
+If these can be rejected, this will count as evidence that, in fact, debt is not independent of foreign policy objectives as the literature claims [@dreher_banking_2022].
+The next section describes our data and research design for testing these hypotheses.
 
@@
 
-The first two specifications below model the yearly count of *Xinhua* mentions and of diplomatic visits from Beijing given the identity of the recipient country as one of either an aid beneficiary, a debtor, or both.
-These variables are denoted by a vector called "Type" which contains binary indicators for whether country $i$ in year $t$ receives exclusively aid, exclusively debt, or both from Beijing.
+We estimate the following two models to test whether changes in the amount of aid or debt received correspond to shifts in coverage and visits:
 
 $$
-\text{coverage}_{it} = \exp\{\tau_t + \text{Type}_{it}^\top \beta + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}; \tag{1}
+\text{coverage}_{it} = \exp\{\tau_t + \beta_1 \text{ asinh}(\text{aid}_{it-1}) + \beta_2 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}; \tag{1}
 $$
@@
 $$
-\text{visits}_{it} = \exp\{\tau_t + \text{Type}_{it}^\top \beta + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}. \tag{2}
-$$
-
-These models are blunt tests of differences between coverage and visits for aid recipients and debtors relative to countries that receive neither from China.
-We additionally estimate the following two models to test whether changes in the amount of aid or debt received correspond to shifts in coverage and visits:
-
-$$
-\text{coverage}_{it} = \exp\{\tau_t + \beta_1 \text{ asinh}(\text{aid}_{it-1}) + \beta_2 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}; \tag{3}
-$$
-
-$$
-\text{visits}_{it} = \exp\{\tau_t + \beta_2 \text{ asinh}(\text{aid}_{it-1}) + \beta_4 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}. \tag{4}
+\text{visits}_{it} = \exp\{\tau_t + \beta_2 \text{ asinh}(\text{aid}_{it-1}) + \beta_4 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}. \tag{2}
 $$
@@
 H1 (that aid recipients receive more outward facing coverage in *Xinhua*) will be supported if $\beta_1 > 0$ and H2 (that aid recipients host more diplomatic missions from Beijing) will be supported if $\beta_2 > 0$.
-H3 and H4 (hypotheses that parallel H1 and H2, but which apply to Chinese debt) will be supported if $\beta_3>0$ and $\beta_4>0$, respectively.
+H3 and H4 (which recall are null hypotheses that apply to Chinese debt) will be rejected if $\beta_3>0$ and $\beta_4>0$, respectively.
 
-Models 1-4 each include year intercepts to adjust for yearly shocks and changes to Beijing's overall aid and debt portfolio, denoted by the term $\tau_t$.
+Models 1 and 2 each include year intercepts to adjust for yearly shocks and changes to Beijing's overall aid and debt portfolio, denoted by the term $\tau_t$.
 The parameter $\rho_i$ denotes random recipient intercepts.
@@
 
-include_graphics(
-  here('06_figures/coverages_combined.jpg'))
+# include_graphics(
+#   here('06_figures/coverages_combined.jpg'))
 
@@
 
-include_graphics(
-  here('06_figures/visits_combined.jpg'))
+# include_graphics(
+#   here('06_figures/visits_combined.jpg'))
 
@@
 
-**Adding confounders here**
+This section summarizes the results from the main statistical analysis.
+All results shown are for zero-inflated negative binomial models.
+The sample used to estimate these models included 2,480 country-year observations consisting of 142 unique countries with observations from 2002 to 2017.
+The Appendix includes summary statistics along with full regression tables.
+To save space, we limit our presentation of the results to the main predictors of interest.
 
@@
 
-```{r predicted-diff, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.', fig.show='hold'}
-include_graphics(
-  here('06_figures/predicted_differences.png')
-)
-```
+Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the four regression specifications enumerated in the methods discussion.
+The figure contains a left and right panel.
+On the right, results are shown for models 1 and 2 while on the left, results are shown for models 3 and 4.
+Recall that the first pair of models uses continuous measures of aid and debt as predictors while the second pair uses binary indicators of whether a developing country is an aid recipient, a debtor, or both of Beijing's.
+Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor).
+The x-axis in each panel denotes the value of the estimated coefficient, and the y-axis indicates the predictor that corresponds with the point estimate.
+Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits.
+Zero is indicated along the x-axis via a vertical dotted line.
+If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.
+
+The results paint a surprising picture of the relationship between Chinese development finance and the outcomes of interest.
+While H1 (that aid recipients are more likely to received more media coverage targeted at foreign audiences) finds support, H2 (that aid recipients are more likely to host diplomatic missions from Beijing) is not supported.
+Further, while we fail to reject the null that debtors do not receive any more or less foreign-facing coverage (H3), we unexpectedly reject the null that debtors do not host any more or less diplomatic missions (H4).
+In particular, the coefficient on aid when the response is *Xinhua* mentions is approximately 0.009 while the coefficient on debt when the response is diplomatic missions is approximately 0.007.
+
+\begin{table}
+\caption{Marginal Effects}
+\label{tab:mareff}
+\centering
+\begin{tabular}[t]{lcc}
+\hline
+ & \multicolumn{2}{c}{(\%) Change} \\
+ & \textit{Xinhua} Coverage & Diplomatic Visits \\
+\hline
+Aid & 0.76 & -0.002 \\
+Debt & 0.01 & 0.05 \\
+\hline
+\multicolumn{3}{l}{\rule{0pt}{1em}\textit{Note: }Estimates for Pakistan, 2017.}\\
+\end{tabular}
+\end{table}
+
+To put these estimates in more substantive terms, it will be helpful to show some computed marginal effects.
+Table \@ref(tab:mareff) shows the predicted change in each of the outcomes given a percent increase in either aid or debt in Pakistan in 2017.
+Cell entries in the first column denote the \% change in the number of times Pakistan appears in *Xinhua* in 2017 while entries in the second column denote the \% change in the number of times Pakistan hosts diplomatic missions from Beijing in 2017.
+The first row indicates what this change is per a hypothetical percent increase aid from China to Pakistan, and the second row indicates what this change is per a hypothetical percent increase in loans (debt) from China to Pakistan.
+The marginal effect for aid on coverage in this case is \%0.76 while the marginal effect for debt on visits is \%0.05.
 

### 2022-10-31 03_analysis/01_new_analysis.R

@@ -431,23 +431,19 @@ bind_rows(
       each = 2
     )),
     var_type = c(
-      rep('Country Classification',
+      rep('Models: (3) & (4)',
           len = 6),
-      rep('Financing Received',
+      rep('Models: (1) & (2)',
           len = 4)
     )
   ) -> fixed_effs
-ggplot(fixed_effs) +
+ggplot(fixed_effs %>% filter(var_type == "Models: (1) & (2)")) +
   aes(
     x = estimate,
     xmin = estimate - 1.96 * std.error,
     xmax = estimate + 1.96 * std.error,
     y = term,
     color = Outcome
-  ) +
-  facet_wrap(
-    ~ var_type,
-    scales = 'free'
   ) +
   geom_point(
     position = ggstance::position_dodgev(-.5)
@@ -490,99 +486,145 @@ ggplot(fixed_effs) +
     width = 6
   )
 
-tibble(
-  None = predict(znb_counts_type, type = 'response', 
-                 newdata = new_dt %>% mutate(type = unique(type[type=='None']))),
-  Aid = predict(znb_counts_type, type = 'response', 
-                newdata = new_dt %>% mutate(type = unique(type[type=='Aid']))),
-  Debt = predict(znb_counts_type, type = 'response', 
-                 newdata = new_dt %>% mutate(type = unique(type[type=='Debt']))),
-  Both = predict(znb_counts_type, type = 'response', 
-                 newdata = new_dt %>% mutate(type = unique(type[type=='Both'])))
-) -> count_preds
-
-tibble(
-  None = predict(znb_visits_type, type = 'response', 
-                 newdata = new_dt %>% mutate(type = unique(type[type=='None']))),
-  Aid = predict(znb_visits_type, type = 'response', 
-                newdata = new_dt %>% mutate(type = unique(type[type=='Aid']))),
-  Debt = predict(znb_visits_type, type = 'response', 
-                 newdata = new_dt %>% mutate(type = unique(type[type=='Debt']))),
-  Both = predict(znb_visits_type, type = 'response', 
-                 newdata = new_dt %>% mutate(type = unique(type[type=='Both'])))
[…]

### 2022-11-03 04_paper/1103_draft.Rmd
changes upfront

--- 2022-10-31 04_paper/10_31_draft.Rmd
@@
 ---
-title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
+title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
 author: ["Lucie Lu","Miles D. Williams"]
@@
 We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
-We expect greater coverage of a developing country in a Chinese media outlet directed to aid giving, and greater bilateral diplomatic activity to correlate with greater debt allocation.
+We expect greater coverage of a developing country in a Chinese outward-facing media outlet and bilateral diplomatic activity to correlate with greater aid giving and debt allocation.
 To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of Xinhua news articles in the Cline Center for Advanced Social Research.
@@
 Also, China is more likely to provide loans to diplomatically aligned countries.
-Our results dispel the myths of China as a ’rouge donor’ and Chinese ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid presents a versatile foreign policy tool in international politics.
+Our results dispel the myths of China as a ’rouge donor’ of desigining ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid and debt allocations present a versatile foreign policy tool in international politics.
 "
@@
 This, therefore, raises a natural question.
-*How do China's foreign aid and debt allocation relate to public diplomacy and international recognition efforts?*
+*How do China's foreign aid and debt allocation relate to its public diplomacy and international recognition efforts?*
 
 We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
-Specifically, we consider outward-facing state-sanctioned news coverage and bilateral diplomatic missions from Beijing.
+Specifically, we consider outward-facing state-sponsored news coverage and bilateral diplomatic missions from Beijing.
 Past research suggests that these two activities play special roles in complementing the foreign policy objectives that drive China's giving and lending.
-
-Media coverage is one way that countries can generate attention and promote a positive spin on their activities to foreign audiences.
-As Nye [-@nye_public_2008-2] notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
-Perhaps in recognition of this, Beijing has expanded its outward-facing state-sponsored media activities and news reporting over the past two decades.
-This has been done in part through the English version of *Xinhua*, China's top state-sponsored news agency.
-
-In addition to expanding the reach and scope of its externally facing news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
-Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.
-These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.
 
@@
 
-As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to the type of assistance China offers.
+As we test these hypotheses, in our research design we delineate China's development financing according to the type of assistance China offers.
 Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
@@
 
-While the findings overall are consistent with our hypotheses, they do so in ways that also problematize the neat distinction between China's use of aid and debt.
-In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's ODA recipients, while no significant relationship exists between aid and diplomatic visits.
+We find that there are a few overlaps between the top 20 countries that receive aid and loans from Beijing at the same time.
+In other words, China target its aid and debt to different sets of developing countries.
+However, the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercial oriented ones, as conventional view holds.
+In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's aid recipients, while no significant relationship exists between aid and diplomatic visits.
 Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage.
-Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomacy with its debtors.
+Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomatic visits with its debtors.
 
-Aid recipient countries disproportionately get more media attention from *Xinhua* via stories that report both on the state of their economy and their development needs.
+On the one hand, aid recipient countries disproportionately get more media coverage from *Xinhua* via stories that report both on the state of their economy and their development needs.
 Notably, *Xinhua* does not just promote China's efforts to offer aid to those countries in need but also gives a rounded picture of those countries' economic conditions justifying their legitimate need for aid.
+On the other hand, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions to cement closer bilateral ties with debtors.
 
-Meanwhile, the finding that loans correspond with diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI).
+These findings contradict with what conventional views hold that Beijing has tried to keep its giving secret.
+Instead, *Xinhua* devotes significant media attention and resources to Beijing's aid-recipients.
+It may help to promote Chinese roles and efforts in the developmental trajectories of these countries and improve Chinese image through visual branding of aid.
+Furthermore, China is not shy away from its ambition in building closer bilateral cooperation with its debt-recipients to align with their foreign policy goals.
+In addition to lending money, China engages in building and strengthening the friendships with these countries.
+Economic interests to motivate Beijing's debt allocations are suggestive to be secondary to its policy goals.
+
+Meanwhile, the finding that loans corresponding with diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI).
 A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance---China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
-Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" a meme based on collective fear of the Chinese threat rather than sound empirical evidence.
+Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" as a meme based on collective fear of the Chinese threat rather than sound empirical evidence.
 Our finding suggests that China is more likely to provide loans to diplomatically aligned countries.
@@
 Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins?
-More research is needed to answer this question.
+This study sheds some light on this pressing question, but further research is needed to fully answer it.
 
@@
 In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives.
-We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences).
+We focus in particular on two factors:  (1) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences) and (2) elite level diplomatic visits from China to developing countries.
+We propose that countries receiving disproportionately China’s bilateral development finance support also receive more concentrated media coverage and diplomatic visits from Beijing.
 
@@
 @dreher_banking_2022 argue that aid tends to be most associated with China's foreign policy objectives, while debt tends to correspond to its market interests.
-What do these differences imply for Beijing's bilateral diplomacy and state-sponsored foreign media?
+What do these differences imply for Beijing's bilateral diplomacy efforts and state-sponsored foreign media's reporting strategy?
 
@@
 As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources.
-When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans[@dreher_banking_2022].
+When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans [@dreher_banking_2022].
 
@@
 Meanwhile, given the more market-oriented (and by extension more controversial) application of debt, we should expect a much weaker association to exist between OOF and the factors summarized below.
-While visibility may be a virtue for aid, the opposite may be true for debt.
+While visibility may be a virtue for aid, the opposite may be true for debt, if the two indeed serve separate goals.
 The next section summarizes these outcomes and their relevance as measures of foreign policy-related activities in the context of China's overseas financing.
@@
 We have made the case that both foreign state-sponsored media and diplomatic visits can be used to sway foreign public opinion in favor of Beijing.
+Media coverage is one way that countries can generate attention and promote a positive spin on their activities to foreign audiences.
+As Nye [-@nye_public_2008-2] notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power.
+Perhaps in recognition of this, Beijing has expanded its outward-facing state-sponsored media activities and news reporting over the past two decades.
+This has been done in part through the English version of *Xinhua*, China's top state-sponsored news agency.
 By covering developing countries that receive Chinese development financing, *Xinhua* editors can paint a positive picture of Beijing's financing and, in so doing, take steps to promote China's international image.
-In addition, by sending regular diplomatic missions to developing countries, Beijing is able to strengthen its bilateral relationships with countries in the Global South helping to cement the close bilateral ties the offer of development assistance is, in part, indented to promote.
+
+In addition to expanding the reach and scope of its externally facing news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions.
+Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.
+These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.
+By sending regular diplomatic missions to developing countries, Beijing is able to strengthen its bilateral relationships with countries in the Global South helping to cement the close bilateral ties the offer of development assistance is, in part, indented to promote.
 
@@
 
-# include_graphics(
-#   here('06_figures/coverages_combined.jpg'))
+ include_graphics(
+   here('06_figures/coverages_combined.jpg'))
 
@@
 
-# include_graphics(
-#   here('06_figures/visits_combined.jpg'))
+ include_graphics(
+   here('06_figures/visits_combined.jpg'))
 
@@
 The first row indicates what this change is per a hypothetical percent increase aid from China to Pakistan, and the second row indicates what this change is per a hypothetical percent increase in loans (debt) from China to Pakistan.
-The marginal effect for aid on coverage in this case is \%0.76 while the marginal effect for debt on visits is \%0.05.
+The marginal effect for aid on coverage in this case is 0.76\% while the marginal effect for debt on visits is 0.05\%.
 

### 2022-11-10 04_paper/10_20_draft_newabstract.Rmd
old updates

@@
 
-```{r predicted-diff, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.', fig.show='hold'}
-include_graphics(
-  here('06_figures/predicted_differences.png')
-)
-```
+Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the four regression specifications enumerated in the methods discussion.
+The figure contains a left and right panel.
+On the right, results are shown for models 1 and 2 while on the left, results are shown for models 3 and 4.
+Recall that the first pair of models uses continuous measures of aid and debt as predictors while the second pair uses binary indicators of whether a developing country is an aid recipient, a debtor, or both of Beijing's.
+Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor).
+The x-axis in each panel denotes the value of the estimated coefficient, and the y-axis indicates the predictor that corresponds with the point estimate.
+Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits.
+Zero is indicated along the x-axis via a vertical dotted line.
+If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.
+
+The results paint a surprising picture of the relationship between Chinese development finance and the outcomes of interest.
+While H1 (that aid recipients are more likely to received more media coverage targeted at foreign audiences) finds support, H2 (that aid recipients are more likely to host diplomatic missions from Beijing) is not supported.
+Further, while we fail to reject the null that debtors do not receive any more or less foreign-facing coverage (H3), we unexpectedly reject the null that debtors do not host any more or less diplomatic missions (H4).
+
+In substantive terms, these estimates correspond with an approximately
+
+\begin{table}
+\caption{Marginal Effects}
+\centering
+\begin{tabular}[t]{lcc}
+\hline
+ & \multicolumn{2}{c}{(\%) Change} \\
+ & \textit{Xinhua} Coverage & Diplomatic Visits \\
+\hline
+Aid & 0.77 & 0.00 \\
+Debt & 0.02 & 0.15 \\
+\hline
+\multicolumn{3}{l}{\rule{0pt}{1em}\textit{Note: }Estimates for Pakistan, 2017.}\\
+\end{tabular}
+\end{table}
 

### 2022-11-10 04_paper/1110_draft.Rmd
updates to hypotheses, results, and conclusion

--- 2022-11-03 04_paper/1103_draft.Rmd
@@
 
-# Hypotheses [just a start]
+# Hypotheses
 
@@
 
-However, as noted in the discussion of China's overseas financing, prior research points to the importance of distinguishing between Beijing's ODA-like (aid) activities and its OOF-like (debt) activities.
-Both coverage and visits are visible activities that help to complement the material resources provided in the form of aid.
-However, as noted previously, debt tends to be associated with more market-based goals, which have historically been controversial in the development community.
-This leads to the reasonable conclusion that aid, rather than debt, should have closer correspondence with coverage and visits than debt.
+To test this logic, we examine the extent to which recipients of Chinese overseas development financing also receive disproportionate coverage in *Xinhua* and host a disproportionate number of diplomatic missions from Beijing.
+We further leverage data both on Chinese ODA (aid) and Chinese OOF (debt) in testing these relationships.
+As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its comercial goals.
+We therefore should expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.
 
-To the extent that aid supports Beijing's foreign policy goals, we should expect that aid recipients will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.
+In particular, to the extent that aid supports Beijing's foreign policy goals, we should expect that aid recipients will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.
 
@@
 
-Conversely, to the extent that loans function in service of market-based objectives rather than political ones, then countries that owe greater debt to Beijing also will not necessarily be more likely targets of greater foreign-facing media coverage in *Xinhua* nor more likely hosts of a greater number of diplomatic missions from Beijing.
+Conversely, to the extent that loans function in service of market-based objectives rather than political ones, countries that owe greater debt to Beijing also will not necessarily be more likely targets of greater foreign-facing media coverage in *Xinhua* nor more likely hosts of a greater number of diplomatic missions from Beijing.
 
@@
 
-Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the four regression specifications enumerated in the methods discussion.
-The figure contains a left and right panel.
-On the right, results are shown for models 1 and 2 while on the left, results are shown for models 3 and 4.
-Recall that the first pair of models uses continuous measures of aid and debt as predictors while the second pair uses binary indicators of whether a developing country is an aid recipient, a debtor, or both of Beijing's.
+Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the two regression specifications enumerated in the methods discussion.
+Recall that this pair of models uses continuous measures of aid and debt as predictors.
 Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor).
@@
 Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits.
-Zero is indicated along the x-axis via a vertical dotted line.
+Zero is indicated along the x-axis via a vertical dashed line.
 If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.
@@
 To put these estimates in more substantive terms, it will be helpful to show some computed marginal effects.
-Table \@ref(tab:mareff) shows the predicted change in each of the outcomes given a percent increase in either aid or debt in Pakistan in 2017.
+Table \@ref(tab:mareff) shows the predicted change in each of the outcomes given a percent increase in either aid or debt.
+The estimates were computed for Pakistan in 2017.
 Cell entries in the first column denote the \% change in the number of times Pakistan appears in *Xinhua* in 2017 while entries in the second column denote the \% change in the number of times Pakistan hosts diplomatic missions from Beijing in 2017.
@@
 
+# Discussion and Conclusion
+
+Our findings paint an interesting picture of how China's overseas financing relates to other kinds of foreign policy activities, speicifically its coverage of aid recipients targeted at foreign audiences and its bilateral diplomatic missions.
+To the extent that aid is associated with improving Beijing's image and fostering closer ties with recipients, we expect Beijing to complement its aid activities with both more coverage and more diplomatic visits.
+
+At the same time that we expected to observe these relationships for Chinese aid, we expected to find weaker relationships between these outcomes and Chinese loans.
+China's application of debt has become a point of controversy because of its proposed links to Beijing's comercial interests.
+We therefore hypothesized that loans from China would be independent of coverage and visits.
+
+Our finding only partially support our expectations.
+As expected, aid recipients receive disproportionate coverage in *Xinhua*.
+However, they are no more likely to receive more diplomatic missions from Beijing.
+Conversely, while debt owed to China does not lead to more coverage in *Xinhua*, it does correspond with more diplomatic visits.
+These more complicated findings warrant further explanation and research.
+At minimum, the links between debt and diplomatic activities suggests that Beijing's commercial interests cannot be divorced entirely from foreign policy.
+China appears to engage in efforts to build diplomatic ties disproportionately in debtor countries (rather than aid recipients).
+This finding deserves attention by future scholars to assess possible mechanisms that lead debt and diplomacy to complement each other.
+
 \clearpage

### 2022-11-15 04_paper/1114_draft_LL.Rmd
Ready to go!!!

--- 2022-11-10 04_paper/1110_draft.Rmd
@@
 ---
-title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
+title: "Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
 author: ["Lucie Lu","Miles D. Williams"]
@@
   - \usepackage{rotating}
+  - \usepackage{indentfirst}
   - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}
 
-abstract: "Absent formal avenues of transparency, how do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts?
-We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities.
-We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
-We expect greater coverage of a developing country in a Chinese outward-facing media outlet and bilateral diplomatic activity to correlate with greater aid giving and debt allocation.
-To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of Xinhua news articles in the Cline Center for Advanced Social Research.
+abstract: "Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts?
+We bring a novel perspective to this issue by considering its international recognition efforts through public diplomacy and news.
+Chinese.
+We propose that Beijing’s foreign policy tools, *Xinhua* media coverage of developing countries and bilateral diplomatic activities, are associated with its overseas financing allocation decisions.
+We expect greater media coverage and bilateral diplomatic activity of a developing country to correlate with more foreign aid giving, but not so much with its debt.
+It is generally believed that foreign aid is motivated by a country’s developmental needs, hence perceived to be conducive to constructing a positive image of being a donor than lending interest-based debts.
+To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of *Xinhua* news articles in the Cline Center for Advanced Social Research.
 We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors.
 Aid-recipient countries disproportionately get more media coverage on the state of their economy and developmental needs.
-Also, China is more likely to provide loans to diplomatically aligned countries.
-Our results dispel the myths of China as a ’rouge donor’ of desigining ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid and debt allocations present a versatile foreign policy tool in international politics.
-"
+Meanwhile, China is more likely to provide loans to diplomatically aligned countries.
+Our results dispel the myths that China is a “rouge donor” or a designer of “debt-trap diplomacy.” Instead, we provide suggestive evidence that, much like traditional donors, China’s foreign aid and debt allocations present a versatile foreign policy tool in international politics."
 ---
@@
 Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and acting globally [@nathan_chinas_2012].
-Similarly, in terms of where China's money goes and its economic influence is concentrated, some countries clearly are more important than others.
-However, Beijing's leaders hold the reasons why close to the vest.
+Similarly, in terms of where China's money goes and its economic influences concentrate, some countries clearly are more important than others.
+However, Beijing holds the reasons why close to the vest.
 
 The secrecy surrounding China's international development financing is puzzling.
-But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending.
-In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors.
-Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
+But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending [@dreherEtAl2018; @strange_tracking_2017].
+In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, much like these traditional donors, Like traditional Western donors, foreign aid provision is a foreign policy tool to boost the status of the donor country [@ferry_turning_2021].
+China's foreign aid can present as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
 These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.
+In contrast, while arguably China's economic interests seem to play a central role in its allocation of foreign financing activities, empirical evidence does not show associations between Chinese foreign aids and a country's natural resource endowments [@hendrix_confronting_2014; @dreherFuchs2015].
 
@@
 This, therefore, raises a natural question.
-*How do China's foreign aid and debt allocation relate to its public diplomacy and international recognition efforts?*
+*Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts?*
 
-We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities.
-Specifically, we consider outward-facing state-sponsored news coverage and bilateral diplomatic missions from Beijing.
-Past research suggests that these two activities play special roles in complementing the foreign policy objectives that drive China's giving and lending.
-
+We propose that despite the lack of formal reporting, Beijing's overseas financing allocations go hand in hand with its focus on building allies and shaping foreign public opinions.
+Specifically, we consider foreign policy tools such as outward-facing state-sponsored news coverage and bilateral diplomatic visits from Beijing.
 While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes.
-In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance.
-Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* to support China's image abroad and to build publicity around its development activities, and they will be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.
+In particular, diplomatic visits and media coverage are critical *visible* activities that can promote the often opaque character of Beijing's development finance.
+Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we expect that in general, recipients of China's overseas development assistance will also attract disproportionate attention of media coverage in *Xinhua* to support China's image abroad and to build publicity around its development activities, and they will be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.
 
@@
 Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF).
-However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals.
+However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals [@dreherEtAl2018].
 The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.[^1] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.
+We hypothesize that Beijing intends to be recognized as an altruistic donor but avoids being associated with its intention as a profit-seeking lender.
+Hence, we develop more fine-grained hypotheses: Aid recipient countries receive more media coverage and diplomatic visits from China, while debt recipient countries do not.
 
@@
 
-We find that there are a few overlaps between the top 20 countries that receive aid and loans from Beijing at the same time.
-In other words, China target its aid and debt to different sets of developing countries.
-However, the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercial oriented ones, as conventional view holds.
+To foreshadow our results, we find that there are very few overlaps between the top 20 countries that receive aid and loans from Beijing at the same time.
+In other words, China targets its aid and debt to different sets of developing countries.
+However, the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercial oriented ones, as the conventional view holds.
 In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's aid recipients, while no significant relationship exists between aid and diplomatic visits.
@@
 On the one hand, aid recipient countries disproportionately get more media coverage from *Xinhua* via stories that report both on the state of their economy and their development needs.
-Notably, *Xinhua* does not just promote China's efforts to offer aid to those countries in need but also gives a rounded picture of those countries' economic conditions justifying their legitimate need for aid.
+Notably, *Xinhua*'s new stories do not just promote China's efforts to offer aid to those countries in need but also give a rounded picture of those countries' economic conditions justifying their legitimate need for aid.
 On the other hand, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions to cement closer bilateral ties with debtors.
+These findings contradict with what conventional views hold that Beijing has tried to keep its financial assistance secret.
+Instead, *Xinhua* devotes significant media attention and resources to Beijing's aid recipients.
+It helps to promote Chinese roles and efforts in the developmental trajectories of these countries and improve Chinese image through visual branding of aid.
 
-These findings contradict with what conventional views hold that Beijing has tried to keep its giving secret.
-Instead, *Xinhua* devotes significant media attention and resources to Beijing's aid-recipients.
-It may help to promote Chinese roles and efforts in the developmental trajectories of these countries and improve Chinese image through visual branding of aid.
-Furthermore, China is not shy away from its ambition in building closer bilateral cooperation with its debt-recipients to align with their foreign policy goals.
-In addition to lending money, China engages in building and strengthening the friendships with these countries.
-Economic interests to motivate Beijing's debt allocations are suggestive to be secondary to its policy goals.
+Furthermore, in contrast to what conventional wisdom holds, China does not shy away from its ambition in building closer bilateral cooperation with its debt recipients to align with their foreign policy goals.
+In addition to lending money, China engages in building and strengthening long-term bilateral relationships with these countries.
+Foreign policy goals play a central role in motivating Beijing's debt allocations.
+Meanwhile, our finding that Chinese loans corresponding with its diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI).
+A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance  ---  China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
+Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" as a popularly constructed meme based on collective fear of the Chinese threat rather than sound empirical evidence.
+Our empirical finding suggests that China is more likely to provide loans to diplomatically aligned countries.
+For instance, Russia, one of China's closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017.
+In contrast, Iraq shows the opposite pattern: it receives the highest amount of need-based aid from China during the period of our investigation, but it does not receive any loans.
+Concerns about Chinese debt nonetheless raise a natural question related to the function of diplomacy in debtor countries.
+Our findings suggest that China's international development program is complex and multifaceted.
+Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins?
+Our study sheds some new light on this pressing question, but further research is needed to fully answer it.
 
-Meanwhile, the finding that loans corresponding with diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI).
-A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance---China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
-Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" as a meme based on collective fear of the Chinese threat rather than sound empirical evidence.
-Our finding suggests that China is more likely to provide loans to diplomatically aligned countries.
-For instance, Russia, one of China's closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017.
-In contrast, Iraq shows the opposite pattern: it receives the highest amount of aid from China during the period of our investigation, but it does not receive any loans.
-Concern about Chinese debt nonetheless raises a natural question related to the function of diplomacy in debtor countries.
-Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins?
-This study sheds some light on this pressing question, but further research is needed to fully answer it.
+This paper proceeds as follows.
+We start by outlining different motivations for China's state financing allocations, followed by discussions of possibly using state-sponsored media and diplomatic visits for Chinese international recognition.
+We then introduce the variables and model specification strategies in the methods section.
+Before we show the results from our models, we provide several figures to present our descriptive analysis.
+Finally, we present our results, with conditional support of our hypotheses, and end with discussions on the implications of our findings.
 
@@
 Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018].
-At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015].
-Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].
+At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015; @dreherEtAl2018].
+Further, China's aid disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].
 
@@
 It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.
+Like the major Western powers, donors of foreign aid is status-conferring: it demonstrates a dedication to helping the needed, improving the audiences' perception of the donor [@goldsmith_doing_2014; @ferry_turning_2021].
 
@@
 If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing.
-Visual branding of aid has emerged as a growing concern among donors.
+Visual branding of aid has emerged as a growing concern among donors [@goldsmith_doing_2014].
 The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.[^3] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US.
@@
 On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic.
-Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy.
+Perhaps more importantly, some of the market oriented objectives that drive China's global debt may not benefit from public displays of diplomacy.
 On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically.
@@
 Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack.
-As Druckman (2001) presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
+As Druckman [-@druckman_limits_2001] presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
 On the other hand, Xinhua needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.
@@
 
-Government-to-government visits are important as leaders' resources are scarce.
-They often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005].
+Government-to-government visits are an indicator of the importance the Chinese government places on developing relations with a country as leaders' resources are scarce [@kastner_is_2012].
+These visits have both symbolic and functional roles.
+Diplomatic visits often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005].
+In fact, studies show that diplomatic visits of Chinese leaders lead to stronger commercial ties and surge of investment [@stone_chinese_2022].
+For example, Chinese President Xi Jinping promised over 10 billion of investment during a state visit to South Africa.
+In a news conference hosted by President Cyril Ramaphosa, he demonstrated that “We have agreed that we must work as partners (with China) to improve the lives of our peoples by elevating our business, commercial and trade ties” [@reuter_chinas_2018].
+The high-profile leader visits are even used as a proxy for Chinese favor-giving and lobbying for votes in the UN [@wang_leader_2022].
 Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and the states' security issues [@mcmanus_making_2018].
-In all, diplomatic visits send important an important positive signal that the visiting and hosting countries support each other and have closer relationships.
+In all, diplomatic visits send an important positive signal that the visiting and hosting countries support each other and have close long-term relationships.
 
@@
 Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy.
-The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect.
+The most recent finding shows that high level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect [@goldsmith_does_2021].
 The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries [@goldsmith_does_2021].
@@
 Since both approaches feature scarce time and resources, we expect that Beijing will choose on whom to cast the spotlight and to visit strategically.
-Most importantly for China's overseas development financing, coverage and diplomatic visits are immediate visible signals of Beijing's priorities.
+Most importantly for China's overseas development financing, media coverage and diplomatic visits are immediate visible signals of Beijing's priorities.
 For this reason, Beijing may use both as a way to complement related political objectives it seeks to promote via its financing activities.
@@
 We further leverage data both on Chinese ODA (aid) and Chinese OOF (debt) in testing these relationships.
-As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its comercial goals.
-We therefore should expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.
+As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its commercial goals.
+The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China.
+However, an examination of patterns in the main variables of interest in this study questions this tidy distinction.
+We therefore expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.
 
@@
 
-If we can reject the null hypothesis for H1 and H2 this will be consistent with the view that China uses aid for political goals.
+If we can reject the null hypothesis for H1 and H2, this will be consistent with the view that China's aid givings are compatible with their policy goals.
 Conversely, H3 and H4 are themselves null hypotheses.
-If these can be rejected, this will count as evidence that, in fact, debt is not independent of foreign policy objectives as the literature claims [@dreher_banking_2022].
+If these can be rejected, this will count as evidence that, in fact, debt is neither independent of foreign policy objectives nor tracing commercial interests as the literature claims [@dreher_banking_2022].
 The next section describes our data and research design for testing these hypotheses.
@@
 
-To test hypotheses 1-4 we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively.
+To test hypotheses 1-4, we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively.
 Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process.
@@
 The vector $X_{it}$ denotes a set of control variables to improve precision and to adjust for possible confounders for Chinese bilateral financing, *Xinhua* coverage, and diplomatic visits.
-A summary of these variables, any transformations applied, and their sources is given in Table [x].
+A summary of these variables (four main variables and nine confounders), definitions and their sources is given in the table below.
 
-[Table x goes here]
+- Independent variables: `Xinhua's Economic News Articles`, `Diplomatic visits`
+- Dependent variables: `Aid`, `Debt`
+- Confounders: `UN Vote Agreement (distance)`, `GDP`, `Population`, `Disaster`, `Civil wars`, `Distance`, `Export/Import`, `FDI`, `Democracy Score`
+
+| Variables       | Definitions          | Sources           |
+|------------------|------------------------------------------------|--------------|
+| `Xinhua's Economic News Articles` | Keywords search[^7] from news headlines to identify relevant news articles and do yearly counts by country. | Global News Archive[^8]|
+| `Diplomatic visits`      | Total number of high-level and provincial-level visits by government officials between China and the receiving country each year.| China's Global Public Diplomacy[^9]|
+| `Aid`     | Sum of total amounts in dollars of Chinese Official Development Assistance (ODA) to receiving country each year. | Chinese Development Finance[^10]|
+| `Debt` | Sum of total amounts in dollars of Chinese Other Official Flows (OOF) to receiving country each year.         | Chinese Development Finance|
+| `UN Vote Agreement (distance)` | Aggregated distance of ideal points of UN General Assembly Voting by year        | UN General Assembly Voting Data[^11] |
+| `GDP` | PPP GDP of recipient countries is gross domestic product converted to international dollars using purchasing power parity rates (constant 2017 international \$)        | World Bank[^12]|
+| `Population` | Total population of recipient countries is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship.        | World Bank|
+| `Disaster` | Deaths as a result of natural disasters in recipient countries by year        | Global Burden of Disease Study [^13]|
+| `Civil wars` | State-based violent conflicts count of the recipient countries by year        | PRIO Conflict Recurrence Database[^14]|
+| `Distance` | Bilateral country distances between recipient countries and China        | CEPII[^15]|
+| `Export/Import` | Annual trade statistics between recipient countries and China        | Open Trade Statistics[^16]|
+| `FDI` | Foreign direct investment to the recipient countries, net (BoP, current US$) by year       | World Bank|
+| `Democracy Score` | Aggregated polyarchy index : To what extent is the electoral principle of democracy achieved?      | V-Dem[^17]|
+
+[^7]: Selecting news articles' headlines that mention one or more of these keywords: aid, donor, lend, development, investment, growth, support, business, help, construction, education, funds, projects, donate, assist
+[^8]: @cline_center_for_advanced_social_research_global_2022
+[^9]:  @aiddata_aiddata_2021
+[^10]: @custer_tracking_2021
+[^11]: @voeten_united_2009
+[^12]: @world_bank_world_2022
+[^13]: @health_metrics_and_evaluation_ihme_global_2019
+[^14]: @uppsala_conflict_data_program_ucdp_prio_2020
+[^15]: @mayer_notes_2011
+[^16]: @vargas_open_2022
+[^17]: @coppedge_v-dem_2020
 
@@
 Then we will present some visuals on the correlations between *Xinhua* news coverage, diplomatic visits, Chinese financial outflow destinations in yearly trends as well as in countries ranked the highest percentiles on each dimension.
-
-## Main variables
-
-*aid, debt, Xinhua mentions, diplomatic visits*
 
@@
 
-In terms of the composition of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that financing received in 14 out of 20 countries was over 80% debt.
+In terms of the composition of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that financing received in 14 out of 20 countries was over 80% of the total debt.
 The top 5 recipients, Russia, Venezuela, Angola, Kazakhstan and Brazil received support from China almost purely in the form of loans.
-Kazakhstan is the only exception among the five beneficiaries with aid comprising a measly 2% of its portfolio.
+Kazakhstan is the only exception among the five beneficiaries with aid comprising a merely 2% of its portfolio.
 Clearly, we can infer that Beijing invests more heavily in its debt relative to aid.
@@
 ```
-
-Alongside these shifts in the application of aid and debt in Beijing's approach to international development finance, a consensus has evolved that aid and debt serve different functions for China.
-Aid is supposed to support China's foreign policy goals, while debt is supposed to support its market interests [see @dreher_banking_2022].
-The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China.
-However, an examination of patterns in the main variables of interest in this study problematizes this tidy distinction.
 
@@
 
-Recall that hypotheses 1 and 3 hold that Beijing will concentrate more *Xinhua* coverage in development finance recipients, and that hypotheses 2 and 4 hold that it will send more diplomatic missions to recipients.
-With respect to aid, there is little observable difference in country coverage in *Xinhua* depending on recipient status.
+From the longitudinal presentations of the data, With respect to aid, there is little observable difference in country coverage in *Xinhua* depending on recipient status.
 However, recipients host appreciably more diplomatic missions from Beijing than non-recipients.
@@
 The y-axis is the list of top 20 *Xinhuan* news coverage countries ranked in order.
-The blud or red colors denote whether the countries are ranked as top 10 percent debt aid or recipients of the year.
+The blue or red colors denote whether the countries are ranked as top 10 percent debt aid or recipients of the year.
 The bigger the dot is, the higher amount of yearly news coverage count it is.
-Russia received the highest number of news exposure between 2002 and 2017 on average.
-It also consistently stands as top 10 percent debt recipients of the year (shown as red dots in Figure \@ref(fig:coverage-combined) (bottom)).
+Russia received the highest number of news exposure between 2002 and 2017 on average, and also consistently stood as top 10 percent debt recipients of the year (shown as red dots in Figure \@ref(fig:coverage-combined) (bottom)).
 Take India as another example: in 2009, 2010, 2011 and 2012, it received over 400 times mentions in *Xinhua* and ranked as the top 10 percent debt recipients.
@@
 
-Similarly, Figure \@ref(fig:visits-combined) shows the overlaps between top 20 diplomatic visits countries and the top 10 percent aid and debt recipients of the year.
-Nine countries[^7] were listed as the top 20 diplomatic visits and *Xinhua* news coverage on average between 2002 and 2017.
-Countries such as Kazakhstan, India and Thailand often hosted Chinese high officials for more than 30 times a year.
-Overall, China seemed to visit the list of the top 10 countries over 10 times and reguarly except for four countries in 2016 and 2017.
-These countries were more likely to be countries where received the highest percentiles of financial inflows from China.
-
-[^7]: India, Indonesia, Thailand, Malaysia, Afghanistan, Pakistan, Philippines, Cambodia, Vietnam.
-
 ```{r visits-combined, fig.cap='Distribution of top 20 diplomatic visits destinations and top 10 percent aid (top) and debt (bottom) recipients from 2002 to 2017.', out.width="100%", fig.show='hold'}
@@
 
+Similarly, Figure \@ref(fig:visits-combined) shows the overlaps between top 20 diplomatic visits countries and the top 10 percent aid and debt recipients of the year.
+Nine countries[^18] were listed as the top 20 diplomatic visits and *Xinhua* news coverage on average between 2002 and 2017.
+Countries such as Kazakhstan, India and Thailand often hosted Chinese high officials for more than 30 times a year.
+Overall, China seemed to visit the list of the top 10 countries over 10 times and regularly except for four countries in 2016 and 2017.
+These countries were more likely to receive the highest percentiles of financial inflows from China.
+
+[^18]: India, Indonesia, Thailand, Malaysia, Afghanistan, Pakistan, Philippines, Cambodia, Vietnam
+
 These patterns remain only suggestive.
 Many factors jointly determine Beijing's financing, *Xinhua* coverage, and diplomatic missions that likely confound straightforward identification of the relationships among these variables.
-The next section summarizes the results from more rigorous statistical tests of hypotheses 1 to 4.
+The next section summarizes the results from more rigorous statistical tests of hypotheses 1 to 4, leveraging on the model specifications explained in the Methods section.
 
@@
 
+Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the two regression specifications enumerated in the methods discussion.
+Recall that this pair of models uses continuous measures of aid and debt as predictors.
+Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor).
+The x-axis in each panel denotes the value of the estimated coefficient, and the y-axis indicates the predictor that corresponds with the point estimate.
+Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits.
+Zero is indicated along the x-axis via a vertical dashed line.
+If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.
+
 ```{r binom-est, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals.
@@
 ```
-
-Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the two regression specifications enumerated in the methods discussion.
-Recall that this pair of models uses continuous measures of aid and debt as predictors.
-Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor).
-The x-axis in each panel denotes the value of the estimated coefficient, and the y-axis indicates the predictor that corresponds with the point estimate.
-Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits.
-Zero is indicated along the x-axis via a vertical dashed line.
-If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.
 
@@
 
-Our findings paint an interesting picture of how China's overseas financing relates to other kinds of foreign policy activities, speicifically its coverage of aid recipients targeted at foreign audiences and its bilateral diplomatic missions.
-To the extent that aid is associated with improving Beijing's image and fostering closer ties with recipients, we expect Beijing to complement its aid activities with both more coverage and more diplomatic visits.
-
-At the same time that we expected to observe these relationships for Chinese aid, we expected to find weaker relationships between these outcomes and Chinese loans.
-China's application of debt has become a point of controversy because of its proposed links to Beijing's comercial interests.
+Our findings paint a new picture of how China's overseas financing relates to other kinds of foreign policy activities, specifically its coverage of aid recipients targeted at foreign audiences and its bilateral diplomatic missions.
+A consensus has evolved that aid and debt serve different functions for China.
+Aid is supposed to support China's foreign policy goals, while debt is supposed to support its market interests [@dreher_banking_2022].
+To the extent that aid is associated with improving Beijing's image and fostering closer ties with recipients, we expected Beijing to complement its aid activities with both more coverage and more diplomatic visits.
+At the same time that we expected to observe these positive relationships for Chinese aid, we expected to find weaker relationships between these outcomes and Chinese loans.
+China's application of debt has become a point of controversy because of its proposed links to Beijing's commercial interests.
 We therefore hypothesized that loans from China would be independent of coverage and visits.
 
-Our finding only partially support our expectations.
-As expected, aid recipients receive disproportionate coverage in *Xinhua*.
+Our empirical findings only partially support our expectations (and hence the consensus in the field).
+As expected, aid recipients receive disproportionately more coverage in *Xinhua*.
 However, they are no more likely to receive more diplomatic missions from Beijing.
 Conversely, while debt owed to China does not lead to more coverage in *Xinhua*, it does correspond with more diplomatic visits.
+Diplomatic visits play symbolic roles in reflecting Chinese leadership priorities in building long-term relationships with the host country, and often accompany material benefits such as investment and development plans.
+Hence, debt recipient countries with more diplomatic visits are considered strategic partners to Beijing.
 These more complicated findings warrant further explanation and research.
-At minimum, the links between debt and diplomatic activities suggests that Beijing's commercial interests cannot be divorced entirely from foreign policy.
-China appears to engage in efforts to build diplomatic ties disproportionately in debtor countries (rather than aid recipients).
-This finding deserves attention by future scholars to assess possible mechanisms that lead debt and diplomacy to complement each other.
+At a minimum, the correlations between debt and diplomatic activities suggest that Beijing's commercial interests cannot be divorced entirely from foreign policy.
+China appears to disproportionately engage in efforts to build diplomatic ties in debtor countries (rather than aid recipients).
+These findings deserve attention by future scholars to assess possible mechanisms that lead debt and diplomacy to complement each other.
 

### 2022-11-21 04_paper/1118_final.Rmd
hot off the press

--- 2022-11-15 04_paper/1114_draft_LL.Rmd
@@
 
-Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and acting globally [@nathan_chinas_2012].
-Similarly, in terms of where China's money goes and its economic influences concentrate, some countries clearly are more important than others.
-However, Beijing holds the reasons why close to the vest.
-
-The secrecy surrounding China's international development financing is puzzling.
-But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending [@dreherEtAl2018; @strange_tracking_2017].
-In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, much like these traditional donors, Like traditional Western donors, foreign aid provision is a foreign policy tool to boost the status of the donor country [@ferry_turning_2021].
-China's foreign aid can present as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics.
-These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.
-In contrast, while arguably China's economic interests seem to play a central role in its allocation of foreign financing activities, empirical evidence does not show associations between Chinese foreign aids and a country's natural resource endowments [@hendrix_confronting_2014; @dreherFuchs2015].
+Despite the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending [@dreherEtAl2018; @strange_tracking_2017].
+In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared.
+Instead, like traditional Western donors, Beijing uses foreign aid as a foreign policy tool to accomplish goals like boosting its international status and realizing diplomatic objectives in recipient countries [@ferry_turning_2021].
 
@@
 
-We propose that despite the lack of formal reporting, Beijing's overseas financing allocations go hand in hand with its focus on building allies and shaping foreign public opinions.
+We propose that Beijing's overseas financing goes hand in hand with other visible activities.
 Specifically, we consider foreign policy tools such as outward-facing state-sponsored news coverage and bilateral diplomatic visits from Beijing.
@@
 
+In our analysis we leverage the latest data on China's overseas development financing produced by AidData, in addition to two other relatively new databases.
+For *Xinhua* articles, we rely on the new Archer web portal from the Cline Center for Advanced Social Research at the University of Illinois at Urbana-Champaign, which makes accessible the vast Global News Index compiled by the Cline Center.
+For diplomatic visits, we take advantage China's Public Diplomacy Dashboard recently compiled by AidData.
+
 As we test these hypotheses, in our research design we delineate China's development financing according to the type of assistance China offers.
@@
 The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.[^1] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.
-We hypothesize that Beijing intends to be recognized as an altruistic donor but avoids being associated with its intention as a profit-seeking lender.
+We hypothesize that Beijing intends to be recognized as an altruistic donor but avoids being associated with its intentions as a profit-seeking lender.
 Hence, we develop more fine-grained hypotheses: Aid recipient countries receive more media coverage and diplomatic visits from China, while debt recipient countries do not.
@@
 In other words, China targets its aid and debt to different sets of developing countries.
-However, the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercial oriented ones, as the conventional view holds.
+However, statistical tests show that the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercially oriented ones, as the conventional view holds.
 In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's aid recipients, while no significant relationship exists between aid and diplomatic visits.
@@
 
-On the one hand, aid recipient countries disproportionately get more media coverage from *Xinhua* via stories that report both on the state of their economy and their development needs.
-Notably, *Xinhua*'s new stories do not just promote China's efforts to offer aid to those countries in need but also give a rounded picture of those countries' economic conditions justifying their legitimate need for aid.
-On the other hand, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions to cement closer bilateral ties with debtors.
-These findings contradict with what conventional views hold that Beijing has tried to keep its financial assistance secret.
-Instead, *Xinhua* devotes significant media attention and resources to Beijing's aid recipients.
-It helps to promote Chinese roles and efforts in the developmental trajectories of these countries and improve Chinese image through visual branding of aid.
-
-Furthermore, in contrast to what conventional wisdom holds, China does not shy away from its ambition in building closer bilateral cooperation with its debt recipients to align with their foreign policy goals.
-In addition to lending money, China engages in building and strengthening long-term bilateral relationships with these countries.
-Foreign policy goals play a central role in motivating Beijing's debt allocations.
-Meanwhile, our finding that Chinese loans corresponding with its diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI).
-A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance  ---  China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions.
-Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" as a popularly constructed meme based on collective fear of the Chinese threat rather than sound empirical evidence.
-Our empirical finding suggests that China is more likely to provide loans to diplomatically aligned countries.
-For instance, Russia, one of China's closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017.
-In contrast, Iraq shows the opposite pattern: it receives the highest amount of need-based aid from China during the period of our investigation, but it does not receive any loans.
-Concerns about Chinese debt nonetheless raise a natural question related to the function of diplomacy in debtor countries.
-Our findings suggest that China's international development program is complex and multifaceted.
-Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins?
-Our study sheds some new light on this pressing question, but further research is needed to fully answer it.
-
 This paper proceeds as follows.
-We start by outlining different motivations for China's state financing allocations, followed by discussions of possibly using state-sponsored media and diplomatic visits for Chinese international recognition.
+We start by outlining different motivations for China's overseas financing, followed by discussions of state-sponsored media and diplomatic visits.
 We then introduce the variables and model specification strategies in the methods section.
@@
 It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.
-Like the major Western powers, donors of foreign aid is status-conferring: it demonstrates a dedication to helping the needed, improving the audiences' perception of the donor [@goldsmith_doing_2014; @ferry_turning_2021].
+And, beyond generating goodwill, giving aid also has been shown to be related to status in the international system as well[@ferry_turning_2021]---another fact that is surely not lost on policymakers in Beijing.
 
@@
 We focus in particular on two factors: (1) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences) and (2) elite level diplomatic visits from China to developing countries.
-We propose that countries receiving disproportionately China’s bilateral development finance support also receive more concentrated media coverage and diplomatic visits from Beijing.
+We propose that countries receiving disproportionately China's bilateral development finance support also receive more concentrated media coverage and diplomatic visits from Beijing.
 
@@
 On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences.
-On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic.
-Perhaps more importantly, some of the market oriented objectives that drive China's global debt may not benefit from public displays of diplomacy.
+On the other hand, some of the market oriented objectives that drive China's global debt may not benefit from public displays of diplomacy.
 On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically.
@@
 Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public.
-That is, the public learns the importance of objects based on the amount of coverage that those objects receive.
+That is, the public learns the importance of issues based on the amount of coverage that those issues receive.
 Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues [@mccombs_agenda-setting_1972].
@@
 
-Over decades of rich research in agenda-setting, empirical patterns support Cohen [-@cohen_press_1963] 's famous notation that the media is "stunningly successful in telling its readers what to think about" (p.
-13; *emphasis added*).
+Over decades of rich research in agenda-setting, empirical patterns support Cohen's [-@cohen_press_1963] famous line that the media is "stunningly successful in telling its readers what to think about" (p.
+13).
 That is, the salience of news media reports transfers to the perception of issue salience to the public [@mccombs_agenda-setting_1972].
@@
 [-@wanta_agenda_2004-3] show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S.
-The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.
+Media coverage of certain countries will lead to these countries becoming more salient among the public.
 
-With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention.
+The news editor is a key source of gatekeeping power since they can tell us where to focus our attention.
 From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air.
@@
 
-Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover.
+Also, previous findings show the strategic consideration of news editors in considering what international news gets media coverage.
 Not all countries in the world receive equal coverage.
@@
 Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press.
-China has expanded its Xinhua News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.
+China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.
 
-Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others [@entman_theorizing_2008; @kiousis_international_2008].
-Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes.
+Recent research on second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes over others [@entman_theorizing_2008; @kiousis_international_2008].
+Compared to first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes.
 Improving one's image to foreign audiences is the core objective of mediated public diplomacy.
 
-As a state-sponsored media platform, Xinhua News Agency is often considered more than a news media agency.
+As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency.
 *Xinhua* is firmly under the control of the CCP's Central Propaganda Department.
 In 2013, President Xi Jinping exhorted the Propaganda Department to "tell Chinese stories well," and the *Xinhua* news agency is at the forefront [@xinhua_xi_2013].
-It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy [@shambaugh_chinas_2015-1], with an increasingly global reach to produce millions of articles in the past decade with hundreds of bureaus worldwide.
+It has had a dual role: reporting news and building up China's image as part of Beijing's "going out" strategy [@shambaugh_chinas_2015-1], with an increasingly global reach and ability to produce millions of articles in the past decade with hundreds of bureaus worldwide.
 Yet, *Xinhua*'s news reports should not be dismissed as mere propaganda or empty slogans.
@@
 It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires.
-The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea.
-It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format.
+The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence overseas.
+It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more viewer-friendly format.
+
 This outward-facing Chinese official media, whose mission as a key disseminator of the Party's narrative to foreign audiences, may inform us of the PRC government's initiatives of presenting Chinese perspectives of real-time events to global audiences.
 Governments use media to tell its story to the world and improve its public relations with other countries.
-As such, scholars often focus on Chinese mediated public diplomacy efforts through Xinhua.
+As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*.
 That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries [@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009].
@@
 
-This paper will focus on Xinhua outward-facing English branch whose audiences are primarily English-speaking readers.
+This paper will focus on *Xinhua*'s outward-facing English branch whose audiences are primarily English-speaking readers.
 Simply providing more information will not improve their image in the Western world.
@@
 As Druckman [-@druckman_limits_2001] presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations.
-On the other hand, Xinhua needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.
+On the other hand, *Xinhua* needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.
 
-Hence, while Xinhua plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information.
+Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information.
 It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.
-Taking into account the limited space of Xinhua to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.
+Taking into account the limited space of *Xinhua* to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.
 
@@
 
-Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country.
+Previous sections illustrate media agenda-setting as an essential step in Beijing's efforts to influence the public's opinion in a second country.
 For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" [@hoffman_introduction_1968, p.
@@
 These visits have both symbolic and functional roles.
-Diplomatic visits often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005].
+Diplomatic visits often mark further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005].
 In fact, studies show that diplomatic visits of Chinese leaders lead to stronger commercial ties and surge of investment [@stone_chinese_2022].
-For example, Chinese President Xi Jinping promised over 10 billion of investment during a state visit to South Africa.
-In a news conference hosted by President Cyril Ramaphosa, he demonstrated that “We have agreed that we must work as partners (with China) to improve the lives of our peoples by elevating our business, commercial and trade ties” [@reuter_chinas_2018].
+For example, Chinese President Xi Jinping promised over \$10 billion of investment during a state visit to South Africa.
+In a news conference hosted by President Cyril Ramaphosa, he demonstrated that "We have agreed that we must work as partners (with China) to improve the lives of our peoples by elevating our business, commercial and trade ties" [@reuter_chinas_2018].
 The high-profile leader visits are even used as a proxy for Chinese favor-giving and lobbying for votes in the UN [@wang_leader_2022].
@@
 The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China.
-However, an examination of patterns in the main variables of interest in this study questions this tidy distinction.
 We therefore expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.
@@
 Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process.
-We opt for negative binomial regression rather than Poisson since the variance of the outcomes is not equivalent to their means.
-We further apply the zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values.
+We opt for negative binomial regression rather than Poisson since we do not wish to impose assumptions about whether the variance of the outcomes is equivalent to their means.
+We further apply a zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values.
 Because of the panel nature of the data, we further include random recipient intercepts in model estimation to account for within-recipient dependence and additional unobserved recipient heterogeneity.
@@
 | Variables                         | Definitions                                                                                                                                                      | Sources                                |
-|------------------|------------------------------------------------|--------------|
-| `Xinhua's Economic News Articles` | Keywords search[^7] from news headlines to identify relevant news articles and do yearly counts by country. | Global News Archive[^8]|
-| `Diplomatic visits`      | Total number of high-level and provincial-level visits by government officials between China and the receiving country each year.| China's Global Public Diplomacy[^9]|
-| `Aid`     | Sum of total amounts in dollars of Chinese Official Development Assistance (ODA) to receiving country each year. | Chinese Development Finance[^10]|
-| `Debt` | Sum of total amounts in dollars of Chinese Other Official Flows (OOF) to receiving country each year.         | Chinese Development Finance|
+|----------------|----------------------------------------|----------------|
+| `Xinhua's Economic News Articles` | Keywords search[^7] from news headlines to identify relevant news articles and do yearly counts by country.
+| Global News Archive[^8]                |
+| `Diplomatic visits`               | Total number of high-level and provincial-level visits by government officials between China and the receiving country each year.
+| China's Global Public Diplomacy[^9]    |
+| `Aid`                             | Sum of total amounts in dollars of Chinese Official Development Assistance (ODA) to receiving country each year.
+| Chinese Development Finance[^10]       |
+| `Debt`                            | Sum of total amounts in dollars of Chinese Other Official Flows (OOF) to receiving country each year.
+| Chinese Development Finance            |
 | `UN Vote Agreement (distance)`    | Aggregated distance of ideal points of UN General Assembly Voting by year                                                                                        | UN General Assembly Voting Data[^11]   |
-| `GDP` | PPP GDP of recipient countries is gross domestic product converted to international dollars using purchasing power parity rates (constant 2017 international \$)        | World Bank[^12]|
-| `Population` | Total population of recipient countries is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship.        | World Bank|
-| `Disaster` | Deaths as a result of natural disasters in recipient countries by year        | Global Burden of Disease Study [^13]|
-| `Civil wars` | State-based violent conflicts count of the recipient countries by year        | PRIO Conflict Recurrence Database[^14]|
-| `Distance` | Bilateral country distances between recipient countries and China        | CEPII[^15]|
-| `Export/Import` | Annual trade statistics between recipient countries and China        | Open Trade Statistics[^16]|
-| `FDI` | Foreign direct investment to the recipient countries, net (BoP, current US$) by year       | World Bank|
-| `Democracy Score` | Aggregated polyarchy index : To what extent is the electoral principle of democracy achieved?      | V-Dem[^17]|
+| `GDP`                             | PPP GDP of recipient countries is gross domestic product converted to international dollars using purchasing power parity rates (constant 2017 international \$) | World Bank[^12]                        |
+| `Population`                      | Total population of recipient countries is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship.
+| World Bank                             |
+| `Disaster`                        | Deaths as a result of natural disasters in recipient countries by year                                                                                           | Global Burden of Disease Study [^13]   |
+| `Civil wars`                      | State-based violent conflicts count of the recipient countries by year                                                                                           | PRIO Conflict Recurrence Database[^14] |
+| `Distance`                        | Bilateral country distances between recipient countries and China                                                                                                | CEPII[^15]                             |
+| `Export/Import`                   | Annual trade statistics between recipient countries and China                                                                                                    | Open Trade Statistics[^16]             |
+| `FDI`                             | Foreign direct investment to the recipient countries, net (BoP, current US\$) by year                                                                            | World Bank                             |
+| `Democracy Score`                 | Aggregated polyarchy index : To what extent is the electoral principle of democracy achieved?
+| V-Dem[^17]                             |
 
 [^7]: Selecting news articles' headlines that mention one or more of these keywords: aid, donor, lend, development, investment, growth, support, business, help, construction, education, funds, projects, donate, assist
+
 [^8]: @cline_center_for_advanced_social_research_global_2022
+
 [^9]: @aiddata_aiddata_2021
+
 [^10]: @custer_tracking_2021
+
 [^11]: @voeten_united_2009
+
 [^12]: @world_bank_world_2022
+
 [^13]: @health_metrics_and_evaluation_ihme_global_2019
+
 [^14]: @uppsala_conflict_data_program_ucdp_prio_2020
+
 [^15]: @mayer_notes_2011
+
 [^16]: @vargas_open_2022
+
 [^17]: @coppedge_v-dem_2020
@@
 
-In this section, we will provide some figures to show the trends of Chinese aid and debt between 2002 and 2017 and the top 20 recipients in terms of their financial portfolios on average.
-Then we will present some visuals on the correlations between *Xinhua* news coverage, diplomatic visits, Chinese financial outflow destinations in yearly trends as well as in countries ranked the highest percentiles on each dimension.
+Before discussing the main statistical results, it may be helpful to summarize some trends of Chinese aid and debt and to consider the top recipients in terms of their financial portfolios on average.
+These stylized facts provide some helpful context and intuition for the data.
 
@@
 include_graphics(
-   here('06_figures/coverages_combined.jpg'))
-
+   here('06_figures/coverages_aid_fig.jpg'))
+include_graphics(
+   here('06_figures/coverages_debt_fig.jpg'))
 ```
@@
 include_graphics(
-   here('06_figures/visits_combined.jpg'))
-
+   here('06_figures/visits_aid_fig.jpg'))
+include_graphics(
+   here('06_figures/visits_debt_fig.jpg'))
 ```
@@
 \end{table}
-
+```
 To put these estimates in more substantive terms, it will be helpful to show some computed marginal effects.
@@
 The estimates were computed for Pakistan in 2017.
-Cell entries in the first column denote the \% change in the number of times Pakistan appears in *Xinhua* in 2017 while entries in the second column denote the \% change in the number of times Pakistan hosts diplomatic missions from Beijing in 2017.
+Cell entries in the first column denote the % change in the number of times Pakistan appears in *Xinhua* in 2017 while entries in the second column denote the % change in the number of times Pakistan hosts diplomatic missions from Beijing in 2017.
 The first row indicates what this change is per a hypothetical percent increase aid from China to Pakistan, and the second row indicates what this change is per a hypothetical percent increase in loans (debt) from China to Pakistan.
-The marginal effect for aid on coverage in this case is 0.76\% while the marginal effect for debt on visits is 0.05\%.
+The marginal effect for aid on coverage in this case is 0.76% while the marginal effect for debt on visits is 0.05%.
 
@@
 
+# Appendix
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
+```{r}
+library(tidyverse) # syntax
+library(here)      # reduce headaches navigating the working directory
+theme_set(theme_light())
+
+# data --------------------------------------------------------------------
+
+dt <- read_csv(
+  here('01_data/final_data/final_data_imputed.csv')
+)
+
+# descriptives ------------------------------------------------------------
+
+# summary stats
+df <- as.data.frame(dt %>% 
+                  select(-year,-aid_econ,-aid_socgov,-aid_human) %>%
+                  mutate(aid = aid/1000000,
+                         debt = debt/1000000,
+                         gdp = gdp/1000000,
+                         pop = pop/1000000,
+                         imports = imports/1000000,
+                         exports = exports/1000000,
+                         fdi = fdi/1000000))
+# stargazer::stargazer(
+#   df,
+#   #type = 'latex',
+#   title = "Summary Statistics"
+# )
+```
+
+\begin{table}[!htbp] \centering 
+  \caption{Summary Statistics} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
+\hline \\[-1.8ex] 
+Aid (mil.) & 2,480 & 40.396 & 215.303 & 0.000 & 8,097.842 \\ 
+Debt (mil.) & 2,480 & 284.140 & 1,544.402 & 0.000 & 36,037.020 \\ 
+\textit{Xinhua} Frequencies & 2,480 & 0.579 & 0.924 & 0.000 & 12.040 \\ 
+\textit{Xinhua} Counts & 2,480 & 38.105 & 65.470 & 0 & 643 \\ 
+Gov't Visits & 2,480 & 1.453 & 3.520 & 0 & 29 \\ 
+V-Dem (API) & 2,480 & 0.666 & 0.198 & 0.134 & 0.965 \\ 
+GDP (mil.) & 2,480 & 222,546.600 & 618,242.300 & 45.184 & 8,276,934.000 \\ 
+Population (mil.) & 2,480 & 29.566 & 103.636 & 0.010 & 1,338.677 \\ 
+Disaster Deaths & 2,480 & 338.449 & 6,483.236 & 0.000 & 222,658.300 \\ 
+Civil War & 2,480 & 0.133 & 0.340 & 0 & 1 \\ 
+Distance (km) & 2,480 & 9,518.719 & 3,948.601 & 809.538 & 19,297.470 \\ 
+Imports (mil.) & 2,480 & 2,459.284 & 7,219.887 & 0.000 & 62,136.640 \\ 
+Exports (mil.) & 2,480 & 2,870.717 & 7,621.028 & 0.000 & 71,617.250 \\ 
+Ally (ATOP) & 2,480 & 0.142 & 0.349 & 0 & 1 \\ 
+UN Policy Distance & 2,480 & 0.548 & 0.519 & 0.0001 & 3.348 \\ 
+FDI (mil.) & 2,480 & $-$1,612.817 & 5,331.112 & $-$90,485.120 & 35,050.840 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+```{r}
+# load(here("03_analysis", "model_fits.R"))
+# library(texreg)
+# coef_map <- list(
+#   "Count model: asinh(aid)" = "Aid (ODA)",
+#   "Count model: asinh(debt)" = "Debt (OOF)",
+#   "Count model: income" = "Income",
+#   "Count model: pop" = "Population",
+#   "Count model: disaster" = "Disaster Deaths",
+#   "Count model: civilwar" = "Civil War",
+#   "Count model: dist" = "Distance",
+#   "Count model: v2x_api" = "V-Dem",
+#   "Count model: imports" = "Imports",
+#   "Count model: exports" = "Exports",
+#   "Count model: distance" = "UN Policy Distance",
+#   "Count model: fdi" = "FDI"
+# )
+# texreg(fits_to_save, 
+#           custom.coef.map = coef_map,
+#           caption = "Zero-inflated Negative Binomial Estimates",
+#           caption.above = T,
+#           custom.model.names = c("Xinhua Mentions", "Diplomatic Visits"))
+```
+
+\begin{table}[!htbp] \centering 
+\caption{Zero-inflated Negative Binomial Estimates}
+\label{}
+\begin{tabular}{l c c}
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex]
+ & \textit{Xinhua} Mentions & Diplomatic Visits \\
+\hline \\[-1.8ex] 
+Aid (ODA)                                & $0.01^{***}$  & $-0.00$       \\
+                                         & $(0.00)$      & $(0.00)$      \\
+Debt (OOF)                               & $0.00$        & $0.01^{**}$   \\
+                                         & $(0.00)$      & $(0.00)$      \\
+Income                                   & $-0.03$       & $0.31^{*}$    \\
+                                         & $(0.07)$      & $(0.14)$      \\
+Population                               & $0.28^{***}$  & $-0.11$       \\
+                                         & $(0.07)$      & $(0.29)$      \\
+Disaster Deaths                          & $0.02^{*}$    & $-0.02$       \\
+                                         & $(0.01)$      & $(0.01)$      \\
+Civil War                                & $0.14^{**}$   & $-0.00$       \\
+                                         & $(0.05)$      & $(0.08)$      \\
+Distance                                 & $-0.59^{*}$   & $-8.33^{***}$ \\
+                                         & $(0.26)$      & $(1.43)$      \\
+V-Dem                                    & $-0.45^{*}$   & $0.05$        \\
+                                         & $(0.18)$      & $(0.23)$      \\
+Imports                                  & $-0.03^{**}$  & $-0.01$       \\
+                                         & $(0.01)$      & $(0.02)$      \\
+Exports                                  & $-0.10^{***}$ & $0.14^{**}$   \\
+                                         & $(0.03)$      & $(0.05)$      \\
+UN Policy Distance                       & $-0.00$       & $0.02$        \\
+                                         & $(0.05)$      & $(0.09)$      \\
+FDI                                      & $0.00$        & $-0.00$       \\
+                                         & $(0.00)$      & $(0.00)$      \\
+\hline
+AIC                                      & $18,303.17$    & $3,034.49$     \\
+Log Likelihood                           & $-9,120.59$    & $-1,486.24$    \\
+Num. obs.                                & $2,480$        & $2,480$        \\
+Num. groups: recipient                   & $142$         & $142$         \\
+\hline \\[-1.8ex] 
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+\end{tabular}
+\label{table:coefficients}
+\end{table}
+
+\clearpage
+
 # References

### 2022-11-21 04_paper/isq_manuscript.Rmd
hot off the press

--- 2022-11-21 04_paper/1118_final.Rmd
@@
 ---
-title: "Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
-author: ["Lucie Lu","Miles D. Williams"]
-date: "`r format(Sys.time(), '%d %B, %Y')`"
+#title: "Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
+#author: ["Lucie Lu","Miles D. Williams"]
+#date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: 
@@
 
-abstract: "Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts?
+#abstract: "Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts?
 We bring a novel perspective to this issue by considering its international recognition efforts through public diplomacy and news.
@@
 ```
-
-\clearpage
 

### 2022-11-21 04_paper/isq_title_page.Rmd
hot off the press

---
#title: "Untitled"
#author: "Miles D. Williams"
#date: '2022-11-21'
output: pdf_document
fontfamily: mathpazo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Title**: Who Gets More Money, Attention and Handshakes? Chinese Overseas Developing Financing, *Xinhua*, and Diplomacy

**Authors**: Lucie Lu^[University of Illinois at Urbana-Champaign], Miles D. Williams^[Denison University - williamsmd@denison.edu]

**Abstract**: How does China support the ostensible diplomatic and image-boosting goals of its overseas development financing? We leverage two new datasets that have recently been made available to answer this question---one, a database of millions of English edition *Xinhua* articles; the other, a database of Beijing's bilateral diplomatic missions in developing countries since the turn of the century. We propose that Beijing wields the English version of *Xinhua* as a tool to promote its image abroad, and that it engages in diplomatic missions to foster closer ties with developing countries in parallel with its allocation of foreign aid. We expect, all else equal, that greater media coverage in *Xinhua* and bilateral diplomatic activity will concentrate in developing countries that receive more foreign aid from China. At the same time, because of the greater controversy surrounding its use, we expect China's growing portfolio of debt allocation to have weaker or null correspondence with coverage and visits. Surprisingly, we show that this expectation only partially holds. Aid recipients receive more coverage in *Xinhua*, and debtors host a greater number of diplomatic missions from Beijing. While China likes to talk about its aid recipients, it prioritizes diplomacy with its debtors.

**Key Words**: foreign aid, China, media, diplomacy

### 2022-11-21 03_analysis/01_new_analysis.R

@@ -22,8 +22,9 @@ dt <- read_csv(
 
 # summary stats
 stargazer::stargazer(
-  as.data.frame(dt),
-  type = 'text'
+  as.data.frame(dt %>% mutate(fdi = fdi/1000000)),
+  type = 'latex',
+  title = "Summary Statistics"
 )
 
 # aid and debt over time
@@ -391,6 +392,14 @@ summary(znb_counts_type)
 summary(znb_visits_type)
 summary(znb_counts_cont)
 summary(znb_visits_cont)
+fits_to_save <- list(
+  znb_counts_cont = znb_counts_cont,
+  znb_visits_cont = znb_visits_cont
+)
+save(
+  fits_to_save,
+  file = here("03_analysis", "model_fits.R")
+)
 
 bind_rows(
   broom.mixed::tidy(

### 2022-11-21 04_paper/merge_manuscript.R

@@ -1,0 +1,6 @@
+# Full ISQ submission (title page + manuscript)
+pdftools::pdf_combine(
+  c(here::here("04_paper", "isq_title_page.pdf"),
+    here::here("04_paper", "isq_manuscript.pdf")),
+  here::here("04_paper", "isq_full_manuscript.pdf")
+)

### 2023-09-06 03_analysis/02_results_summary.Rmd
updates

--- 2021-12-15 03_analysis/02_results_summary.Rmd
@@
 knitr::opts_chunk$set(echo = F, warning = F, message = F)
+library(texreg)
+library(estimatr)
 ```
 
-**Note**: Table 1 shows results with the imputed dataset. Table 2 shows results with the non-imputed dataset.
+**Note**: Table 1 shows full panel results with the imputed dataset.
+Table 2 shows full panel results with the non-imputed dataset.
+Tables 3-5 show OLS, IV, and Lewbel IV estimates by region, respectively, for the imputed dataset.
+Tables 6-8 show the same with the non-imputed dataset.
 
@@
 load(
-  paste0(getwd(), "/tab1.R")
+  paste0(getwd(), "/model_list1.R")
 )
-reg.tab1 <- reg.tab
-cat(reg.tab1)
+screenreg(model_list[7:10],
+          include.ci = F,
+          custom.coef.map = list(
+            "aid" = "ODA",
+            "debt" = "OOF",
+            "lead_aid" = "ODA",
+            "lead_debt" = "OOF"
+          ))
 ```
@@
 reg.tab2 <- reg.tab
-cat(reg.tab2)
+reg.tab2
 ```

### 2023-09-06 03_analysis/01_new_analysis.R

@@ -10,12 +10,14 @@ library(tidyverse) # syntax
 library(glmmTMB)   # mixed-effects neg. binom. models
 library(texreg)    # printing regression output
 library(here)      # reduce headaches navigating the working directory
-theme_set(theme_light())
+library(coolorrr)  # plotting theme and palette
+set_palette()
+set_theme()
 
 # data --------------------------------------------------------------------
 
 dt <- read_csv(
-  here('01_data/final_data/final_data_imputed.csv')
+  here('01_data','final_data', 'final_data_imputed.csv')
 )
 
 # descriptives ------------------------------------------------------------
@@ -31,11 +33,11 @@ stargazer::stargazer(
 dt %>%
   group_by(year) %>%
   summarize(
-    Aid = sum(aid),
-    Debt = sum(debt)
+    ODA = sum(aid),
+    OOF = sum(debt)
   ) %>%
   pivot_longer(
-    Aid:Debt
+    ODA:OOF
   ) %>%
   mutate(
     value = value / 1000000
@@ -55,12 +57,7 @@ dt %>%
   scale_y_continuous(
     labels = scales::comma
   ) +
-  scale_color_manual(
-    values = c(
-      'Aid' = 'royalblue',
-      'Debt' = 'indianred3'
-    )
-  ) +
+  ggpal() +
   labs(
     x = NULL,
     y = 'Yearly Total\n(millions $)',
@@ -100,20 +97,14 @@ dt %>%
   scale_y_continuous(
     labels = scales::comma
   ) +
-  scale_color_manual(
-    values = c('Recipient' = 'royalblue', 
-               'Non-recipient' = 'indianred3')
-  ) +
+  ggpal() +
   facet_wrap(
     ~ name, scales = 'free'
   ) +
   labs(
     x = NULL,
     y = 'Yearly Total',
-    color = NULL
-  ) +
-  theme(
-    legend.position = 'top'
+    color = "ODA"
   ) 
   ggsave(
     here('06_figures/total_coverage_visits_by_aid.png'),
@@ -142,20 +133,14 @@ dt %>%
   scale_y_continuous(
     labels = scales::comma
   ) +
-  scale_color_manual(
-    values = c('Debtor' = 'royalblue', 
-               'Non-debtor' = 'indianred3')
-  ) +
+  ggpal() +
[…]

### 2023-09-06 03_analysis/01_primary_analysis.R

@@ -17,106 +17,173 @@ trans_dt <-
   mutate(
     income = gdp / pop
   ) %>%
+  rename(
+    count = counts_by_year
+  ) %>%
   mutate_at(
-    c("aid", "count", "govt_visits", "gdp", "income", "pop", "unemp",
+    c("aid", "debt", "count", "govt_visits", "income", "pop",
       "disaster", "dist", "distw", 
-      "distwces", "trade", "china_gdp"),
+      "distwces", "imports", "exports", "fdi"),
     asinh # use inverse hyperbolic sine rather than log(1 + x)
   ) %>%
-  group_by(recipient_iso3) %>%
+  group_by(recipient) %>%
   mutate(
-    aid = lead(aid, by = "year"),
-    lead_count = lead(count, by = "year"),
-    lead_visits = lead(govt_visits, by = "year")
+    lead_aid = lead(aid, order_by = year),
+    lead_debt = lead(debt, order_by = year),
+    lead_count = lead(count, order_by = year),
+    lead_visits = lead(govt_visits, order_by = year)
   ) %>%
   ungroup %>%
-  na.omit
+  na.omit %>%
+  distinct(recipient, year, .keep_all = T)
 
 
 # setup panel -------------------------------------------------------------
 
 pdata <- # for estimating random recipient effects with censReg
-  plm::pdata.frame(trans_dt, c(id = "recipient_iso3", time = "year"))
+  plm::pdata.frame(trans_dt, c(id = "recipient", time = "year"))
 
 
 # estimate main models ----------------------------------------------------
 
-spec <- # specification without predictors of interest 
-  aid ~ pmm_fh + gdp + pop + unemp + disaster + civilwar +
-  dist + trade + atopally + as.factor(year)
+spec_1 <- # specifications without predictors of interest 
+  lead_count ~ aid + debt + income + pop + disaster + civilwar +
+  dist + v2x_api + imports + exports + distance + fdi
+spec_2 <-
+  lead_visits ~ aid + debt + income + pop + disaster + civilwar +
+  dist + v2x_api + imports + exports + distance + fdi
+  
 
 # models to estimate:
-# 1. OLS
-# 2. multilevel Tobit with lag of dv
[…]
